### 2024-09-09 template.tex
Adjusting the template

%  LaTeX support: latex@mdpi.com 
%  For support, please attach all files needed for compiling as well as the log file, and specify your operating system, LaTeX version, and LaTeX editor.

%=================================================================
\documentclass[futureinternet,article,submit,pdftex,moreauthors]{Definitions/mdpi}

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis 
% For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by: 
% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. Remove "pdftex" for (1) compiling with LaTeX & dvi2pdf (if eps figures are used) or for (2) compiling with XeLaTeX.

%=================================================================
% MDPI internal commands - do not modify
\firstpage{1} 
\makeatletter 
\setcounter{page}{\@firstpage} 
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2024}
\copyrightyear{2024}
%\externaleditor{Academic Editor: Firstname Lastname}
\datereceived{ } 
\daterevised{ } % Comment out if no revised date
\dateaccepted{ } 
\datepublished{ } 
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org
%\CorrStatement{yes}  % For updates

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, inputenc, calc, indentfirst, fancyhdr, graphicx, epstopdf, lastpage, ifthen, float, amsmath, amssymb, lineno, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, tabto, xcolor, colortbl, soul, multirow, microtype, tikz, totcount, changepage, attrib, upgreek, array, tabularx, pbox, ragged2e, tocloft, marginnote, marginfix, enotez, amsthm, natbib, hyperref, cleveref, scrextend, url, geometry, newfloat, caption, draftwatermark, seqsplit
% cleveref: load \crefname definitions after \begin{document}

%=================================================================
% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition, Notation, Assumption
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{AI-Based Detection of Jamming Attacks in 6G Drone Networks}

% MDPI internal command: Title for citation in the left column
\TitleCitation{AI-Based Detection of Jamming Attacks in 6G Drone Networks}

% Author Orchid ID: enter ID or remove command
\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name

% Authors, for the paper (add full first names)
\Author{Sergio Cibecchini $^{1,\dagger,\ddagger}$\orcidA{}, Francesco Chiti $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}

%\longauthorlist{yes}

% MDPI internal command: Authors, for metadata in PDF
\AuthorNames{Sergio Cibecchini, Francesco Chiti and Firstname Lastname}

% MDPI internal command: Authors, for citation in the left column
\AuthorCitation{Cibecchini, S.; Chiti, F.; Lastname, F.}
% If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

% Contact information of the corresponding author
\corres{Correspondence: sergio.cibecchini@gmail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}

% Current address and/or shared authorship
\firstnote{Current address: Affiliation.}  % Current address should not be the same as any items in the Affiliation section.
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

%\simplesumm{} % Simple summary

%\conference{} % An extended version of a conference paper

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setcounter{section}{-1} %% Remove this when starting to work on the template.
\section{How to Use this Template}

The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).

% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.

\section{Introduction}

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper \cite{ref-journal}. Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Materials and Methods}

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
\begin{quote}
This is an example of a quote.
\end{quote}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
\subsection{Subsection}
\subsubsection{Subsubsection}

Bulleted lists look like this:
\begin{itemize}
\item	First bullet;
\item	Second bullet;
\item	Third bullet.
\end{itemize}

Numbered lists can be added as follows:
\begin{enumerate}
\item	First item; 
\item	Second item;
\item	Third item.
\end{enumerate}

The text continues here.

\subsection{Figures, Tables and Schemes}

All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.

\begin{figure}[H]
\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
\caption{This is a figure. Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.\label{fig1}}
\end{figure}   
\unskip

\begin{table}[H] 
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data \textsuperscript{1}\\
\bottomrule
\end{tabularx}
\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
\end{table}

The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).

% Example of a figure that spans the whole page width. The same concept works for tables, too.
\begin{figure}[H]
\begin{adjustwidth}{-\extralength}{0cm}
\centering
\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
\end{adjustwidth}
\caption{This is a wide figure.\label{fig2}}
\end{figure}

\begin{table}[H]
\caption{This is a wide table.\label{tab2}}
	\begin{adjustwidth}{-\extralength}{0cm}
		\newcolumntype{C}{>{\centering\arraybackslash}X}
		\begin{tabularx}{\fulllength}{CCCC}
			\toprule
			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
			\midrule
\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
			  	                   & Data			& Data			& Data\\
			             	      & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
			  	                  & Data			& Data			& Data\\
			             	     & Data			& Data			& Data\\
                   \midrule
\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
                  \midrule
\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
			  	                 & Data			& Data			& Data\\
			             	    & Data			& Data			& Data\\
			\bottomrule
		\end{tabularx}
	\end{adjustwidth}
	\noindent{\footnotesize{* Tables may have a footer.}}
\end{table}

%\begin{listing}[H]
%\caption{Title of the listing}
%\rule{\columnwidth}{1pt}
%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
%\rule{\columnwidth}{1pt}
%\end{listing}

Text.

Text.

\subsection{Formatting of Mathematical Components}

This is the example 1 of equation:
\begin{linenomath}
\begin{equation}
a = 1,
\end{equation}
\end{linenomath}
the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.

This is the example 2 of equation:
\begin{adjustwidth}{-\extralength}{0cm}
\begin{equation}
a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
\end{equation}
\end{adjustwidth}

% Example of a page in landscape format (with table and table footnote).
%\startlandscape
%\begin{table}[H] %% Table in wide page
%\caption{This is a very wide table.\label{tab3}}
%	\begin{tabularx}{\textwidth}{CCCC}
%		\toprule
%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
%		\midrule
%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
%		\bottomrule
%	\end{tabularx}
%	\begin{adjustwidth}{+\extralength}{0cm}
%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
%	\end{adjustwidth}
%\end{table}
%\finishlandscape

Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
%% Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

%% Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Discussion}

Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Patents}

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}

% Only for journal Methods and Protocols:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title. A supporting video article is available at doi: link.}

% Only for journal Hardware:
% If you wish to submit a video article, please do so with any other supplementary material.
% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
%\begin{tabularx}{\textwidth}{lll}
%\toprule
%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
%\midrule
%S1 & Python script (.py) & Script of python source code used in XX \\
%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
%S3 & Text (.txt) & Raw data from experiment X \\
%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
%... & ... & ... \\
%\bottomrule
%\end{tabularx}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work~reported.}

\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''. Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}

\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study. You might choose to exclude this statement if the study did not require ethical approval. Please note that the Editorial Office might ask you for further information. Please add “The study was conducted in accordance with the Declaration of Helsinki, and approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving humans. OR “The animal study protocol was approved by the Institutional Review Board (or Ethics Committee) of NAME OF INSTITUTE (protocol code XXX and date of approval).” for studies involving animals. OR “Ethical review and approval were waived for this study due to REASON (please provide a detailed justification).” OR “Not applicable” for studies not involving humans or animals.}

\informedconsent{Any research article describing a study involving humans should contain this statement. Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans. You might also choose to exclude this statement if the study did not involve humans.

Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves). Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}

\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data. In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study. Where no new data were created, or where data is unavailable due to privacy or ethical restrictions, a statement is still required. Suggested Data Availability Statements are available in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.}

% Only for journal Nursing Reports
%\publicinvolvement{Please describe how the public (patients, consumers, carers) were involved in the research. Consider reporting against the GRIPP2 (Guidance for Reporting Involvement of Patients and the Public) checklist. If the public were not involved in any aspect of the research add: ``No public involvement in any aspect of this research''.}

% Only for journal Nursing Reports
%\guidelinesstandards{Please add a statement indicating which reporting guideline was used when drafting the report. For example, ``This manuscript was drafted against the XXX (the full name of reporting guidelines and citation) for XXX (type of research) research''. A complete list of reporting guidelines can be accessed via the equator network: \url{https://www.equator-network.org/}.}

% Only for journal Nursing Reports
%\useofartificialintelligence{Please describe in detail any and all uses of artificial intelligence (AI) or AI-assisted tools used in the preparation of the manuscript. This may include, but is not limited to, language translation, language editing and grammar, or generating text. Alternatively, please state that “AI or AI-assisted tools were not used in drafting any aspect of this manuscript”.}

\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections. This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}

\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflicts of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results. Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section. If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional

%% Only for journal Encyclopedia
%\entrylink{The Link to this entry published on the encyclopedia platform.}

\abbreviations{Abbreviations}{
The following abbreviations are used in this manuscript:\\

\noindent 
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute\\
DOAJ & Directory of open access journals\\
TLA & Three letter acronym\\
LD & Linear dichroism
\end{tabular}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional
\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
\appendixstart
\appendix
\section[\appendixname~\thesection]{}
\subsection[\appendixname~\thesubsection]{}
The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data. Mathematical proofs of results not central to the paper can be added as an appendix.

\begin{table}[H] 
\caption{This is a table caption.\label{tab5}}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{CCC}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
Entry 1		& Data			& Data\\
Entry 2		& Data			& Data\\
\bottomrule
\end{tabularx}
\end{table}

\section[\appendixname~\thesection]{}
All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{adjustwidth}{-\extralength}{0cm}
%\printendnotes[custom] % Un-comment to print a list of endnotes

\reftitle{References}

% Please provide either the correct journal abbreviation (e.g. according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: external bibliography
%=====================================
%\bibliography{your_external_BibTeX_file}

%=====================================
% References, variant B: internal bibliography
%=====================================
\begin{thebibliography}{999}
% Reference 1
\bibitem[Author1(year)]{ref-journal}
Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
\bibitem[Author2(year)]{ref-book1}
Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
% Reference 3
\bibitem[Author3(year)]{ref-book2}
Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
% Reference 4
\bibitem[Author4(year)]{ref-unpublish}
Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
% Reference 5
\bibitem[Author5(year)]{ref-communication}
Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
% Reference 6
\bibitem[Author6(year)]{ref-proceeding}
Author 1, A.B.; Author 2, C.D.; Author 3, E.F. Title of presentation. In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
% Reference 7
\bibitem[Author7(year)]{ref-thesis}
Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
% Reference 8
\bibitem[Author8(year)]{ref-url}
Title of Site. Available online: URL (accessed on Day Month Year).
\end{thebibliography}

% If authors have biography, please use the format below
%\section*{Short Biography of Authors}
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author1.pdf}}}
%{\textbf{Firstname Lastname} Biography of first author}
%
%\bio
%{\raisebox{-0.35cm}{\includegraphics[width=3.5cm,height=5.3cm,clip,keepaspectratio]{Definitions/author2.jpg}}}
%{\textbf{Firstname Lastname} Biography of second author}

% For the MDPI journals use author-date citation, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\PublishersNote{}
\end{adjustwidth}
\end{document}

### 2024-09-13 article.tex
Created article file as a copy of the template
Started work on the introduction

--- 2024-09-09 template.tex
@@
 % Choose between the following MDPI journals:
-% acoustics, actuators, addictions, admsci, adolescents, aerobiology, aerospace, agriculture, agriengineering, agrochemicals, agronomy, ai, air, algorithms, allergies, alloys, analytica, analytics, anatomia, animals, antibiotics, antibodies, antioxidants, applbiosci, appliedchem, appliedmath, applmech, applmicrobiol, applnano, applsci, aquacj, architecture, arm, arthropoda, arts, asc, asi, astronomy, atmosphere, atoms, audiolres, automation, axioms, bacteria, batteries, bdcc, behavsci, beverages, biochem, bioengineering, biologics, biology, biomass, biomechanics, biomed, biomedicines, biomedinformatics, biomimetics, biomolecules, biophysica, biosensors, biotech, birds, bloods, blsf, brainsci, breath, buildings, businesses, cancers, carbon, cardiogenetics, catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, chemproc, children, chips, cimb, civileng, cleantechnol, climate, clinpract, clockssleep, cmd, coasts, coatings, colloids, colorants, commodities, compounds, computation, computers, condensedmatter, conservation, constrmater, cosmetics, covid, crops, cryptography, crystals, csmf, ctn, curroncol, cyber, dairy, data, ddc, dentistry, dermato, dermatopathology, designs, devices, diabetology, diagnostics, dietetics, digital, disabilities, diseases, diversity, dna, drones, dynamics, earth, ebj, ecologies, econometrics, economies, education, ejihpe, electricity, electrochem, electronicmat, electronics, encyclopedia, endocrines, energies, eng, engproc, entomology, entropy, environments, environsciproc, epidemiologia, epigenomes, est, fermentation, fibers, fintech, fire, fishes, fluids, foods, forecasting, forensicsci, forests, foundations, fractalfract, fuels, future, futureinternet, futurepharmacol, futurephys, futuretransp, galaxies, games, gases, gastroent, gastrointestdisord, gels, genealogy, genes, geographies, geohazards, geomatics, geosciences, geotechnics, geriatrics, grasses, gucdd, hazardousmatters, healthcare, hearts, hemato, hematolrep, heritage, higheredu, highthroughput, histories, horticulturae, hospitals, humanities, humans, hydrobiology, hydrogen, hydrology, hygiene, idr, ijerph, ijfs, ijgi, ijms, ijns, ijpb, ijtm, ijtpp, ime, immuno, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jal, jcdd, jcm, jcp, jcs, jcto, jdb, jeta, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmp, jmse, jne, jnt, jof, joitmc, jor, journalmedia, jox, jpm, jrfm, jsan, jtaer, jvd, jzbg, kidneydial, kinasesphosphatases, knowledge, land, languages, laws, life, liquids, literature, livers, logics, logistics, lubricants, lymphatics, machines, macromol, magnetism, magnetochemistry, make, marinedrugs, materials, materproc, mathematics, mca, measurements, medicina, medicines, medsci, membranes, merits, metabolites, metals, meteorology, methane, metrology, micro, microarrays, microbiolres, micromachines, microorganisms, microplastics, minerals, mining, modelling, molbank, molecules, mps, msf, mti, muscles, nanoenergyadv, nanomanufacturing,\gdef\@continuouspages{yes}} nanomaterials, ncrna, ndt, network, neuroglia, neurolint, neurosci, nitrogen, notspecified, %%nri, nursrep, nutraceuticals, nutrients, obesities, oceans, ohbm, onco, %oncopathology, optics, oral, organics, organoids, osteology, oxygen, parasites, parasitologia, particles, pathogens, pathophysiology, pediatrrep, pharmaceuticals, pharmaceutics, pharmacoepidemiology,\gdef\@ISSN{2813-0618}\gdef\@continuous pharmacy, philosophies, photochem, photonics, phycology, physchem, physics, physiologia, plants, plasma, platforms, pollutants, polymers, polysaccharides, poultry, powders, preprints, proceedings, processes, prosthesis, proteomes, psf, psych, psychiatryint, psychoactives, publications, quantumrep, quaternary, qubs, radiation, reactions, receptors, recycling, regeneration, religions, remotesensing, reports, reprodmed, resources, rheumato, risks, robotics, ruminants, safety, sci, scipharm, sclerosis, seeds, sensors, separations, sexes, signals, sinusitis, skins, smartcities, sna, societies, socsci, software, soilsystems, solar, solids, spectroscj, sports, standards, stats, std, stresses, surfaces, surgeries, suschem, sustainability, symmetry, synbio, systems, targets, taxonomy, technologies, telecom, test, textiles, thalassrep, thermo, tomography, tourismhosp, toxics, toxins, transplantology, transportation, traumacare, traumas, tropicalmed, universe, urbansci, uro, vaccines, vehicles, venereology, vetsci, vibration, virtualworlds, viruses, vision, waste, water, wem, wevj, wind, women, world, youth, zoonoticdis
 % For posting an early version of this manuscript as a preprint, you may use "preprints" as the journal. Changing "submit" to "accept" before posting will remove line numbers.
@@
 %---------
-% The default type of manuscript is "article", but can be replaced by: 
-% abstract, addendum, article, book, bookreview, briefreport, casereport, comment, commentary, communication, conferenceproceedings, correction, conferencereport, entry, expressionofconcern, extendedabstract, datadescriptor, editorial, essay, erratum, hypothesis, interestingimage, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, studyprotocol, systematicreview, supfile, technicalnote, viewpoint, guidelines, registeredreport, tutorial
-% supfile = supplementary materials
 
@@
 
+%PLACE TO ADD COMMANDS
+
 %=================================================================
@@
 % Full title of the paper (Capitalized)
-\Title{AI-Based Detection of Jamming Attacks in 6G Drone Networks}
+\Title{AI-Based Detection of Jamming Attacks In 6G Drone Networks}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\setcounter{section}{-1} %% Remove this when starting to work on the template.
-\section{How to Use this Template}
-
-The template details the sections that can be used in a manuscript.
-Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section).
-Please check the instructions on the authors' page of the journal to verify the correct order and names.
-For any questions, please contact the editorial office of the journal or support@mdpi.com.
-For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References).
-
-% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.
-
+%\setcounter{section}{-1} %% Remove this when starting to work on the template.
 \section{Introduction}
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper \cite{ref-journal}.
-Now citing a book reference \cite{ref-book1,ref-book2} or other reference types \cite{ref-unpublish,ref-communication,ref-proceeding}.
+The shift from 4G to 5G has been a generational leap has revolutionized connectivity around the world. 
+Despite 5G being still in its early adoption rate at the time of writing\cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
+6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency but this in turn 
+will also bring forth new security challenges, specific to those applications.
+
+One of the main differences between 5G and 6G technology will be the focus of the 6G standard in regards to 
+AI integration. While Software Defined Networks (SDN) have played a key role in improving the efficiency and security 
+of 5G networks, 6G is expected to take this a step further, by integrating artificial
+intelligence and machine learning directly into the network. This is what the authors of \cite{6GRoadmapLetaief} define as 
+the shift from \textit{Softwarization} to \textit{Intelligentization}.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \vspace{6pt} 
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% optional
-%\supplementary{The following supporting information can be downloaded at:  \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.}
-
-% Only for journal Methods and Protocols:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.
-A supporting video article is available at doi: link.}
-
-% Only for journal Hardware:
-% If you wish to submit a video article, please do so with any other supplementary material.
-% \supplementary{The following supporting information can be downloaded at: \linksupplementary{s1}, Figure S1: title; Table S1: title; Video S1: title.\vspace{6pt}\\
-%\begin{tabularx}{\textwidth}{lll}
-%\toprule
-%\textbf{Name} & \textbf{Type} & \textbf{Description} \\
-%\midrule
-%S1 & Python script (.py) & Script of python source code used in XX \\
-%S2 & Text (.txt) & Script of modelling code used to make Figure X \\
-%S3 & Text (.txt) & Raw data from experiment X \\
-%S4 & Video (.mp4) & Video demonstrating the hardware in use \\
-%... & ... & ... \\
-%\bottomrule
-%\end{tabularx}
-%}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-
-%% Only for journal Encyclopedia
-%\entrylink{The Link to this entry published on the encyclopedia platform.}
 
@@
 \begin{thebibliography}{999}
+
+\bibitem[Taylor(2024)]{5GStatisticsTaylor}
+5G - statistics \& facts. Available online: https://www.statista.com/topics/3447/5g/\#topicOverview (accessed on 13 September 2024).
+
+\bibitem[Letaief et al.(2019)]{6GRoadmapLetaief}
+Letaief, K.B.; Chen, W.; Shi, Y.; Zhang, J.; AI, B.
+The Roadmap to 6G: AI Empowered Wireless Networks.
+{\em IEEE Communications Magazine} {\bf 2019}, {\em 57}, 84--90.
+https://doi.org/10.1109/MCOM.2019.1900271.
+
 % Reference 1
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% for journal Sci
-%\reviewreports{\\
-%Reviewer 1 comments and authors’ response\\
-%Reviewer 2 comments and authors’ response\\
-%Reviewer 3 comments and authors’ response
-%}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \PublishersNote{}

### 2024-09-13 article.tex
Continued introduction

@@
 the shift from \textit{Softwarization} to \textit{Intelligentization}.
+
+AI integration in 6G networks will greatly strengthen the security of the network against security threats. 
+By leveraging Diagnostic Analytics, a collection of insights into the status of the networks, security teams 
+will be able to train specific AI models to detect and respond to security threats in real-time.
+
+In this paper we will focus on a specific aspect of the security of 6G networks, namely the detection of 
+jamming attacks in drone networks.
 

### 2024-09-13 article.tex
Started topic overview

@@
 The shift from 4G to 5G has been a generational leap has revolutionized connectivity around the world. 
-Despite 5G being still in its early adoption rate at the time of writing\cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
+Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
 6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency but this in turn 
@@
 
-In this paper we will focus on a specific aspect of the security of 6G networks, namely the detection of 
-jamming attacks in drone networks.
+In this paper we will focus on a specific aspect of the security of 6G networks, namely we will provide a machine learning based approach 
+for the detection of jamming attacks in networks of drones.
+
+The paper is divided in 5 sections: 
+\begin{enumerate}
+	\item \textbf{Topic overview:} In this section we will discuss how drones can benefit from integration in 6G network, analyze jamming attacks, their types, mitigation and detection.
+Finally we will discuss the advantages of an edge AI approach for jamming detection.
+	\item \textbf{Materials and methods:} In this section we will define the scenario that we decided to analyze as well as the dataset, algorithm and evaluation metrics we chose for our tests. 
+	\item \textbf{Numerical Results:} In this section we will present the testing methodology as well as the numerical results that we obtained. 
+	\item \textbf{Discussion:} In this section we will discuss the results obtained in the previous section and highlight notable trends.
+	\item \textbf{Conclusions:} In this section we will summarize the results and discuss possible future research directions.
+\end{enumerate}
+
+\section{Topic Overview}
+
+\subsection{Drones in 6G Networks}
+
+Drones, also known as Unmanned Aerial Vehicles (UAVs) are defined as \textit{all aircraft designed to fly
+without a pilot on board} \cite{DronesEC}. This technology has experienced rapid growth in recent years and is expected to 
+keep growing in both the consumer sector as well as the commercial and military sectors \cite{DronesStatisticsLaricchia}.
 
@@
 \begin{tabular}{@{}ll}
+SDN & Software Defined Networks\\
+UAVs & Unmanned Aerial Vehicles \\
+
 MDPI & Multidisciplinary Digital Publishing Institute\\
@@
 \bibitem[Taylor(2024)]{5GStatisticsTaylor}
-5G - statistics \& facts. Available online: https://www.statista.com/topics/3447/5g/\#topicOverview (accessed on 13 September 2024).
+5G - statistics \& facts. Available online: \url{https://www.statista.com/topics/3447/5g/topicOverview} (accessed on 13 September 2024).
 
@@
 {\em IEEE Communications Magazine} {\bf 2019}, {\em 57}, 84--90.
-https://doi.org/10.1109/MCOM.2019.1900271.
+\url{https://doi.org/10.1109/MCOM.2019.1900271}.
+
+\bibitem[EuropeanCommission(2024)]{DronesEC}
+Unmanned aircraft (drones). Available online: \url{https://transport.ec.europa.eu/transport-modes/air/aviation-safety/unmanned-aircraft-drones_en} (accessed on 13 May 2024).
+
+\bibitem[Laricchia(2024)]{DronesStatisticsLaricchia}
+Laricchia, F. Consumer and commercial drones - statistics and facts. Available online: \url{https://www.statista.com/topics/7939/drones/\#topicOverview} (accessed on 13 September 2024).
 

### 2024-09-13 article.tex
Finished the Topic Overview on Drones

@@
 keep growing in both the consumer sector as well as the commercial and military sectors \cite{DronesStatisticsLaricchia}.
+
+In report 22.886 \cite{5GV2XSultan} 3GPP, the organ responsible for the development and maintenance of the 5G standard, identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
+Everything) communication services. Among these use cases, the report identifies vehicle platooning, advanced and remote driving end extended situational awareness as some of the main benefits
+of V2V communication. All these use cases can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence 
+would allow the drones to act autonomously in a coordinated manner.
+
+This would prove useful in a variety of fields: from autonomous soil and crop health assessment as well as irrigation in agriculture, 
+delivery of life saving supplies and locating of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
+delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation.
+
+The effectiveness of drones in the military sector is widely recognized, both for high and low end models. For example, in the Ukraine war even cheap FPV drones 
+mounted with explosives were successfully used to destroy much more expensive equipment \cite{DroneCombatUkraine}.
+
+Security against Jamming attacks is crucial in all these applications, especially in a safety critical environment.
 
@@
 UAVs & Unmanned Aerial Vehicles \\
+3GPP & 3rd Generation Partnership Project \\
+V2X & Vehicle to Everything \\
+FPV & First Person View \\
 
@@
 
+\bibitem[Sultan(2018)]{5GV2XSultan}
+Sultan, A. Study on enhancement of 3GPP support for 5G V2X services. Tech. Rep. {\em 3GPP}, 2018.
+
+\bibitem[Rao et al.(2024)]{DroneCombatUkraine}
+Rao, A.; Zafra, M.; Hunder, M.; Kiyada, S.
+How drone combat in Ukraine is changing warfare.
+Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 May 2024).
+
 % Reference 1

### 2024-09-13 article.tex
Updated citation

@@
 delivery of life saving supplies and locating of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
-delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation.
+delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.
 
@@
 
+\bibitem[Hassija et al.(2021)]{DroneCommHassija}
+Hassija, V.; Kumar, R.; Gupta, H.; Singh, S.; Sharma, P.
+Fast, Reliable, and Secure Drone Communication: A Comprehensive Survey.
+{\em IEEE Communications Surveys and Tutorials} {\bf 2021}, {\em 23}, 2802--2832.
+https://doi.org/10.1109/COMST.2021.3097916.
+
 % Reference 1

### 2024-09-13 article.tex
finished section on jamming attacks

@@
 
+\section{Related Works}
+
+%TODO Add related works
+
 \section{Topic Overview}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Understanding Jamming Attacks}
+
+Jamming attacks are a type of Denial of Service (DoS) attack that aims at disrupting the communication between two or more devices. 
+This is achieved by transmitting a powerful signal on the same frequency as the one used by the devices to communicate. If the jamming signal is strong enough, 
+it is able to overwhelm the legitimate signal, effectively blocking the communication between the devices \cite{DroneCommHassija}. 
+Since the ability to communicate is affected, Jamming attacks falls under the umbrella of attacks that target the \textit{Availability} of the service in the CIA triad classification \cite{DataIntegrityCawthra}.
+Jamming attacks can be classified into 5 main categories, based on the attack pattern of the jammer:
+
+\begin{itemize}
+    \item \textbf{Constant Jamming:} Constant jamming is the simplest form of jamming attack. In constant jamming, the jammer is active all the time. 
+    \item \textbf{Periodic Jamming:} The jammer simply transmits a strong signal on the same frequency as the devices it wants to disrupt 
+    for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\). This type of jamming attack is particularly effective against devices 
+    that are not able to change their frequency and has the ability to disrupt the transmission of a sequence of consecutive packets. \cite{VANETsAI-Lyamin}
+    \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, giving each transmitted packet a probability 
+    \(p\) of being jammed \cite{VANETsAI-Lyamin}. 
+    \item \textbf{Reactive Jamming:} A reactive jammer starts transmitting its jamming signal only when it senses energy in the communication channel, 
+    indicating that a legitimate transmission is taking place. This type of jamming attack is more power efficient compared to other 
+    operation types, as it only transmits its signal when it is needed\cite{MLMisbehavior5GBoualouache}.
+    \item \textbf{Smart Jamming:} A smart jammer is a more sophisticated type of jammer that is able to adapt its jamming signal to 
+    maximize the disruption of the communication between the devices. Smart jammers are able to modify their attack pattern based on the 
+    transmission specifics of the devices they are targeting and are able to adapt to changes in the communication channel\cite{AntiJammingV2V-Feng}.
+\end{itemize}
+
+An effective Jamming detection AI model should achieve a high detection score against all the different types of jamming attacks.
+
 \section{Materials and Methods}
@@
 \subsubsection{Subsubsection}
-
-Bulleted lists look like this:
-\begin{itemize}
-\item	First bullet;
-\item	Second bullet;
-\item	Third bullet.
-\end{itemize}
-
-Numbered lists can be added as follows:
-\begin{enumerate}
-\item	First item; 
-\item	Second item;
-\item	Third item.
-\end{enumerate}
 
@@
 FPV & First Person View \\
+DOS & Denial Of Service \\
 
@@
 
-\bibitem[Rao et al.(2024)]{DroneCombatUkraine}
-Rao, A.; Zafra, M.; Hunder, M.; Kiyada, S.
-How drone combat in Ukraine is changing warfare.
-Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 May 2024).
-
 \bibitem[Hassija et al.(2021)]{DroneCommHassija}
@@
 
-% Reference 1
-\bibitem[Author1(year)]{ref-journal}
-Author~1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
-% Reference 2
-\bibitem[Author2(year)]{ref-book1}
-Author~2, L. The title of the cited contribution. In {\em The Book Title}; Editor 1, F., Editor 2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
-% Reference 3
-\bibitem[Author3(year)]{ref-book2}
-Author 1, A.; Author 2, B. \textit{Book Title}, 3rd ed.; Publisher: Publisher Location, Country, 2008; pp. 154--196.
-% Reference 4
-\bibitem[Author4(year)]{ref-unpublish}
-Author 1, A.B.; Author 2, C. Title of Unpublished Work. \textit{Abbreviated Journal Name} year, \textit{phrase indicating stage of publication (submitted; accepted; in press)}.
-% Reference 5
-\bibitem[Author5(year)]{ref-communication}
-Author 1, A.B. (University, City, State, Country); Author 2, C. (Institute, City, State, Country). Personal communication, 2012.
-% Reference 6
-\bibitem[Author6(year)]{ref-proceeding}
-Author 1, A.B.; Author 2, C.D.; Author 3, E.F.
-Title of presentation.
-In Proceedings of the Name of the Conference, Location of Conference, Country, Date of Conference (Day Month Year); Abstract Number (optional), Pagination (optional).
-% Reference 7
-\bibitem[Author7(year)]{ref-thesis}
-Author 1, A.B. Title of Thesis. Level of Thesis, Degree-Granting University, Location of University, Date of Completion.
-% Reference 8
-\bibitem[Author8(year)]{ref-url}
-Title of Site. Available online: URL (accessed on Day Month Year).
+\bibitem[Rao et al.(2024)]{DroneCombatUkraine}
+Rao, A.; Zafra, M.; Hunder, M.; Kiyada, S.
+How drone combat in Ukraine is changing warfare.
+Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 May 2024).
+
+\bibitem[Cawthra(2020)]{DataIntegrityCawthra}
+Cawthra, J. Data Integrity: Detecting and Responding to Ransomware and Other Destructive Events. {\em NIST Special Publication} {\bf 2020}, {\em 1800-26A}.
+
+\bibitem[Lyamin et al.(2018)]{VANETsAI-Lyamin}
+Lyamin, N.; Samuylov, A.; Gaidamaka, Y.; Vinel, A.; Koucheryavy, Y.
+AI-Based Malicious Network Traffic Detection in VANETs.
+{\em IEEE Network} {\bf 2018}, {\em 32}, 15--21.
+https://doi.org/10.1109/MNET.2018.1800074.
+
+\bibitem[Boualouache and Engel(2023)]{MLMisbehavior5GBoualouache}
+Boualouache, A.; Engel, T.
+A Survey on Machine Learning-Based Misbehavior Detection Systems for 5G and Beyond Vehicular Networks.
+{\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
+https://doi.org/10.1109/COMST.2023.3236448.
+
+\bibitem[Feng and Haykin(2019)]{AntiJammingV2V-Feng}
+Feng, S.; Haykin, S.
+Cognitive Risk Control for Anti-Jamming V2V Communications in Autonomous Vehicle Networks.
+{\em IEEE Transactions on Vehicular Technology} {\bf 2019}, {\em 68}, 9920--9934.
+https://doi.org/10.1109/TVT.2019.2935999.
+
 \end{thebibliography}

### 2024-09-14 article.tex
Started Jamming against drones section
Finished the paragraph on jamming attacks against drones

@@
 
+\subsection{Jamming attacks against drone networks}
+
+Jamming attacks are particularly effective against drone networks, as drones usually rely on external input to navigate and operate correctly.
+If a jammer were able to completely block the communication between the drone and the base station, the drone would be left without any indication on how to behave and would need to activate an internal failsafe mechanism.
+This usually comes in the form of either a return to base procedure, a landing procedure or a hover in place procedure.
+All of these procedures leave the drone in a vulnerable position, as a bad actor could potentially capture the drone and use it for malicious purposes.
+This is especially true when jamming attacks are used in combination with other types of attacks, such as spoofing attacks.
+
+One real world example of this is the capture of an American drone by Iran in 2011. 
+In December 2011 a Lockheed Martin RQ-170 Sentinel drone operated by the United States Air Force was flying over Iran when its operators lost control of the vehicle.
+The US government initially claimed that the drone had crashed due to a technical malfunction, but later reports revealed that the drone had been captured by the Iranian military.
+Iranian electronic warfare specialists claimed to have brought it down using a Jamming attack, that forced the drone into a return to base procedure, in combination with a  GPS spoofing attack, that made the drone land into a designated area \cite{RQ170DroneOwano}.
+After successfully capturing the drone, the Iranian government managed to reverse-engineer the drone and produce a working replica, which was then used in their military operations \cite{IranianUAVGross}.
+
+\subsection{Centralized vs Edge approach for Jamming detection}
+
 \section{Materials and Methods}
@@
 %% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
+This ensures correct line numbering.
 The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
@@
 \bibitem[EuropeanCommission(2024)]{DronesEC}
-Unmanned aircraft (drones). Available online: \url{https://transport.ec.europa.eu/transport-modes/air/aviation-safety/unmanned-aircraft-drones_en} (accessed on 13 May 2024).
+Unmanned aircraft (drones). Available online: \url{https://transport.ec.europa.eu/transport-modes/air/aviation-safety/unmanned-aircraft-drones_en} (accessed on 13 September 2024).
 
@@
 {\em IEEE Communications Surveys and Tutorials} {\bf 2021}, {\em 23}, 2802--2832.
-https://doi.org/10.1109/COMST.2021.3097916.
+\url{https://doi.org/10.1109/COMST.2021.3097916}.
 
@@
 How drone combat in Ukraine is changing warfare.
-Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 May 2024).
+Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 September 2024).
 
@@
 {\em IEEE Network} {\bf 2018}, {\em 32}, 15--21.
-https://doi.org/10.1109/MNET.2018.1800074.
+\url{https://doi.org/10.1109/MNET.2018.1800074}.
 
@@
 {\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
-https://doi.org/10.1109/COMST.2023.3236448.
+\url{https://doi.org/10.1109/COMST.2023.3236448}.
 
@@
 {\em IEEE Transactions on Vehicular Technology} {\bf 2019}, {\em 68}, 9920--9934.
-https://doi.org/10.1109/TVT.2019.2935999.
+\url{https://doi.org/10.1109/TVT.2019.2935999}.
+
+\bibitem[Owano(2024)]{RQ170DroneOwano}
+Owano, N. RQ-170 drone's ambush facts spilled by Iranian engineer. Available online: \url{https://phys.org/news/2011-12-rq-drone-ambush-facts-iranian.html} (accessed on 14 September 2024).
+
+\bibitem[Gross and TOI Staff(2024)]{IranianUAVGross}
+Gross, J.A.; TOI Staff.
+Iranian UAV that entered Israeli airspace seems to be American stealth knock-off.
+Available online: \url{https://www.timesofisrael.com/iranian-uav-that-enteredisraeli-airspace-seems-to-be-american-stealth-knock-off} (accessed on 16 May 2024).
 

### 2024-09-26 article.tex
Wrote related works

@@
 %PLACE TO ADD COMMANDS
+\usepackage{lipsum}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{subcaption}
 
@@
 % Authors, for the paper (add full first names)
-\Author{Sergio Cibecchini $^{1,\dagger,\ddagger}$\orcidA{}, Francesco Chiti $^{2,\ddagger}$ and Firstname Lastname $^{2,}$*}
+\Author{Sergio Cibecchini $^{1,\dagger}$\orcidA{}, Francesco Chiti $^{2}$ and Laura Pierucci$^{2,}$*}
 
@@
 % MDPI internal command: Authors, for metadata in PDF
-\AuthorNames{Sergio Cibecchini, Francesco Chiti and Firstname Lastname}
+\AuthorNames{Sergio Cibecchini, Francesco Chiti and Laura Pierucci}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{A single paragraph of about 200 words maximum.
-For research articles, abstracts should give a pertinent overview of the work.
-We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations.
-The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}
+\abstract{}
 
@@
 Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
+
 6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency but this in turn 
@@
 
-One of the main differences between 5G and 6G technology will be the focus of the 6G standard in regards to 
-AI integration. While Software Defined Networks (SDN) have played a key role in improving the efficiency and security 
-of 5G networks, 6G is expected to take this a step further, by integrating artificial
-intelligence and machine learning directly into the network. This is what the authors of \cite{6GRoadmapLetaief} define as 
+One of the main differences between 5G and 6G technology will be a much deeper integration with AI.
+While Software Defined Networks (SDN) have played a key role in improving the efficiency and security
+of 5G networks, 6G is expected to take this a step further, by designing the networks to be integrated with artificial intelligence from the ground up.
+This is what the authors of \cite{6GRoadmapLetaief} define as
 the shift from \textit{Softwarization} to \textit{Intelligentization}.
 
-AI integration in 6G networks will greatly strengthen the security of the network against security threats. 
+AI integration in 6G networks will greatly strengthen the security of the network against potential threats. 
 By leveraging Diagnostic Analytics, a collection of insights into the status of the networks, security teams 
@@
 \begin{enumerate}
-	\item \textbf{Topic overview:} In this section we will discuss how drones can benefit from integration in 6G network, analyze jamming attacks, their types, mitigation and detection.
+	\item \textbf{Topic overview:} In this section we will make a general overview of how drones can benefit from integration in 6G network, analyze jamming attacks, their types, mitigation and detection.
 Finally we will discuss the advantages of an edge AI approach for jamming detection.
 	\item \textbf{Materials and methods:} In this section we will define the scenario that we decided to analyze as well as the dataset, algorithm and evaluation metrics we chose for our tests. 
-	\item \textbf{Numerical Results:} In this section we will present the testing methodology as well as the numerical results that we obtained. 
-	\item \textbf{Discussion:} In this section we will discuss the results obtained in the previous section and highlight notable trends.
-	\item \textbf{Conclusions:} In this section we will summarize the results and discuss possible future research directions.
+	\item \textbf{Numerical Results:} In this section we will present the testing methodology, describe model tuning and testing phases and present the results obtained. 
+	\item \textbf{Discussion:} In this section we will comment the results obtained in the previous section and highlight the advantages of the proposed approach. 
+	\item \textbf{Conclusions:} In this section we will show how the proposed solution fits into a real world scenario and discuss possible future research directions.
 \end{enumerate}
@@
 
-%TODO Add related works
+Detection of jamming attacks in wireless networks has been a topic of interest for the research community for many years.
+A wide variety of approaches have been proposed for the detection of jamming attacks
+in different types of networks, with most of the work focusing on the detection of jamming attacks in Vehicular Ad-Hoc Networks (VANETs)\cite{VANETsAI-Lyamin}.
+
+This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors propose a machine learning based approach for the detection of jamming attacks in IoT networks. 
+The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in a IoT drone scenario.
+The authors show that the CNN model is able to achieve a high detection rate against constant jamming attacks, but it
+struggles in the classification of periodic jamming and normal traffic.
+
+The authors of \cite{GPSSpoofingDetection-Zuo} propose an Isolation Forest based approach for the detection of GPS spoofing attacks, while the authors of \cite{HybridJammingDetection-Hong} successfully applied a combination of decision trees and Isolation forest to classify
+and detect jamming attacks in a mobile scenario.
+
+We apply a similar solution to the one proposed in \cite{HybridJammingDetection-Hong} to the scenario of a 6G drone network, testing the model against the dataset proposed in \cite{JammingDetectionIoT-Hussain}.
+Our approach reached a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
+We also focused on the tuning of the model's hyperparameters to fit our specific scenario and compared it
+against the default model. In the tuning phase, the resource constrained nature of the scenario was taken into a count for the selection of the more appropriate hyperparameters.
 
@@
 Everything) communication services. Among these use cases, the report identifies vehicle platooning, advanced and remote driving end extended situational awareness as some of the main benefits
-of V2V communication. All these use cases can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence 
+of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence 
 would allow the drones to act autonomously in a coordinated manner.
 
-This would prove useful in a variety of fields: from autonomous soil and crop health assessment as well as irrigation in agriculture, 
-delivery of life saving supplies and locating of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
+This would prove useful in a variety of fields: from autonomous irrigation as well as soil and crop health assessment in agriculture, 
+delivery of life saving supplies and identification of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
 delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.
 
-The effectiveness of drones in the military sector is widely recognized, both for high and low end models. For example, in the Ukraine war even cheap FPV drones 
+In the military sector, the effectiveness of drones is widely recognized, both for high and low end models. For example, in the Ukraine war even cheap FPV drones 
 mounted with explosives were successfully used to destroy much more expensive equipment \cite{DroneCombatUkraine}.
@@
 \begin{itemize}
-    \item \textbf{Constant Jamming:} Constant jamming is the simplest form of jamming attack. In constant jamming, the jammer is active all the time. 
-    \item \textbf{Periodic Jamming:} The jammer simply transmits a strong signal on the same frequency as the devices it wants to disrupt 
-    for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\). This type of jamming attack is particularly effective against devices 
-    that are not able to change their frequency and has the ability to disrupt the transmission of a sequence of consecutive packets. \cite{VANETsAI-Lyamin}
-    \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, giving each transmitted packet a probability 
-    \(p\) of being jammed \cite{VANETsAI-Lyamin}. 
+    \item \textbf{Constant Jamming:} The jammer continuously transmits a strong signal on the same frequency used by the devices it wants to disrupt to communicate. 
+    \item \textbf{Periodic Jamming:} The jammer transmits a strong signal for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\).
+This pattern is repeated until the attack is stopped.
+    \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, jamming each transmitted packet with a probability 
+    \(p\) based on the attack pattern\cite{VANETsAI-Lyamin}. 
     \item \textbf{Reactive Jamming:} A reactive jammer starts transmitting its jamming signal only when it senses energy in the communication channel, 
     indicating that a legitimate transmission is taking place. This type of jamming attack is more power efficient compared to other 
-    operation types, as it only transmits its signal when it is needed\cite{MLMisbehavior5GBoualouache}.
+    attack patterns, as it only transmits its signal when it know that it can actually disrupt the communication\cite{MLMisbehavior5GBoualouache}.
     \item \textbf{Smart Jamming:} A smart jammer is a more sophisticated type of jammer that is able to adapt its jamming signal to 
@@
 
-\subsection{Jamming attacks against drone networks}
+\subsection{Jamming attacks against drone networks}\label{JammingDroneNetworks}
 
@@
 
-One real world example of this is the capture of an American drone by Iran in 2011. 
-In December 2011 a Lockheed Martin RQ-170 Sentinel drone operated by the United States Air Force was flying over Iran when its operators lost control of the vehicle.
+One real world example is the capture of an American drone by Iran in 2011. 
+In December 2011 a Lockheed Martin \textit{RQ-170} Sentinel drone operated by the United States Air Force was flying over Iran when its operators lost control of the vehicle.
 The US government initially claimed that the drone had crashed due to a technical malfunction, but later reports revealed that the drone had been captured by the Iranian military.
@@
 
+When presenting a machine learning based approach in an IoT setting, the question of where the AI model should be placed often arises.
+By their nature, IoT devices, and in turn drones, are usually resource constrained,
+both in terms of computational power but also in terms of internal storage and battery capacity \cite{6GSecurity-Chorti}.
+This means that complex AI models and algorithms are usually not feasible to be run on the device itself.
+A centralized approach
+offloads the computational burden to a central server, that returns the results of the AI model to the device.
+While this approach might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
+communication with the central server means less time to react to the attack.
+Also, as jamming attacks degrade or sometimes completely block the communication between the device and the base station, a centralized approach might not be feasible in this case.
+An lightweight edge approach on the other hand, while not as powerful as a centralized approach, would to provide real-time results to the device and would be able to operate even when the communication is disrupted, which is crucial in a jamming situation.
+
+\subsection{Detection and Mitigation of Jamming Attacks}\label{sec:DetectionMitigation}
+
+When attempting to mitigate jamming attacks, the first step is always to detect that an attack is taking place. This can be done by monitoring the communication channel for signs of jamming. 
+The state of the art approaches involve the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The simplest approach when
+developing a method to detect jamming attacks is to set a static threshold for these metrics and trigger an alarm when the threshold is crossed.
+While this approach is easy to implement and might be effective in some cases, it is not able to adapt to changes in the communication channel and might be prone to false positives.
+Implementing a machine learning based approach for jamming detection would allow the system to adapt to the changes in the communication channel and would be able to provide a more accurate detection of jamming attacks \cite{VANETsAI-Lyamin}.
+This is especially useful in mobile scenarios like
+drone networks, where the environment is constantly changing and the signal strength can vary greatly.
+
+Once an attack is successfully detected, state of the art jamming mitigation techniques, like Direct Sequence Spread Spectrum (DSSS), Frequency Hopping (FHSS) and advanced signal processing techniques can be put in place to mitigate the
+effects of the attack.
+
+The use of an AI model for jamming detection is particularly suitable for a 6G network, as the improved sensing capabilities would allow the model to train on a wide variety of diagnostic data, improving the detection rate and accuracy of the model.
+Furthermore, as the network is expected to be integrated with AI from the ground up, its highly likely that in the future drones will be integrated with AI-specific chips for a more efficient execution of AI models.
+
 \section{Materials and Methods}
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+\subsection{Scenario Definition and Attacker Classification}
 
-Research manuscripts reporting large datasets that are deposited in a publicly avail-able database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+In the proposed scenario we have a flying drone that is subject to a jamming attack.
+The drone communicates with a ground station and periodically samples the Received Signal Strength (RSS) of the signal it receives.
+The drone implements a simple unsupervised machine learning algorithm module, trained on nominal traffic RSS values.
+The module takes the sampled RSS values and classifies them as either normal or anomalous.
+Thanks to this classification module, the drone is able to determine wether or not a jamming attack is taking place.
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
-\begin{quote}
-This is an example of a quote.
-\end{quote}
+We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain point in time by transmitting a strong signal on the same frequency as the one used by the drone to communicate with the ground station.
+We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning the drone has to rely on its internal classification algorithm to determine if a jamming attack is taking place and react accordingly.
+We assume that the jammer type is unknown to the drone.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
-\subsection{Subsection}
-\subsubsection{Subsubsection}
-
-The text continues here.
-
-\subsection{Figures, Tables and Schemes}
-
-All figures and tables should be cited in the main text as Figure~\ref{fig1}, Table~\ref{tab1}, etc.
+Figure \ref{fig:CombinedJammingscenariosDiagram} shows a diagram of the proposed scenario.
 
 \begin{figure}[H]
-\includegraphics[width=10.5 cm]{Definitions/logo-mdpi}
-\caption{This is a figure.
-Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.\label{fig1}}
+	\includegraphics[width=10.5 cm]{img/CombinedJammingscenariosDiagram.jpg}
+	\caption{Proposed jamming scenario.
+The Drone communicates with the 6G base station and receives information about how to behave.
+The fixed jammer \textbf{(1)} and the mobile jammer \textbf{(2)} target the communication between the drone and the base station.
+The drone has an internal classification module that is able to detect jamming attacks.}
+	\label{fig:CombinedJammingscenariosDiagram}
 	\end{figure}   
@@
 
+In our scenario, the drone will be subject to two types of jamming attacks, a constant jamming attack and a periodic jamming attack.
+These types of attacks can be attributed to different types of jammers.
+The constant jamming attack could be caused by a ground jammer, as maintaining a constant jamming signal requires a large power source, while
+the periodic jamming attack could be caused by a drone jammer, as drones are usually battery powered and can only jam for a limited amount of time. 
+Employing a periodic jamming attack could help the malicious drone conserve energy and reduce the chances of being detected.
+
+Table \ref{tab:attacker_classification} shows the attacker classification in the proposed scenario \cite{MLMisbehavior5GBoualouache}:
+
 \begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are~cited.\label{tab1}}
+	\caption{Attacker classification details.\label{tab:attacker_classification}}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{Classification} & \textbf{Description} \\
+	\midrule
+	Active   & The attacker is actively trying to disrupt network operation by transmitting a jamming signal\\
+	External & The attack takes place at level 1 of the OSI model, meaning that the attacker is not part of the network\\
+	Local    & The attack is local, as it is targeted at a specific drone or drone cluster and not at the entire network\\
+	Malicious & Jamming attacks are considered malicious as their main goal is to disrupt correct network operation\\
+	\bottomrule
+\end{tabularx}
+\end{table}
+
+\subsection{Dataset Choice}\label{sec:DatasetChoice}
+
+As 6G network traffic is not yet available, we chose an open-source dataset \cite{JammingDetectionIoT-Hussain} that analyses the RSS values 
+received by a Raspberry Pi 3 that is subject to periodic and constant jamming attacks.
+
+The dataset was created using a software-defined radio (SDR) connected to a laptop that was programmed to transmit a jamming signal using the 
+open source software \textit{GNU Radio}.
+A second SDR radio was connected to a Raspberry Pi 3 and was chosen to receive the jamming signal.
+The jamming radio operates at a frequency of $2.412 GHz$ with a Bandwidth of $40MHz$, while the Raspberry Pi 3 was programmed to sample the RSS values with a frequency of $32K$ samples per second.
+
+The dataset contains 3 different \textit{.txt} files that store the RSS values sampled by the Raspberry Pi 3.
+The first file contains the RSS values sampled during a constant jamming attack, the second file contains the RSS values sampled during a periodic jamming attack and the third file contains the RSS values sampled during normal network operation.
+The samples are stored in a single column, with each row representing a single sample.
+The samples us the \textit{dBm (decibel-milliwatts)} unit of measurement, a logarithmic scale that measures the power of a signal in relation to 1 milliwatt.
+Conversion can be done using the formula \cite{WirelessCommSobot} shown in equation \ref{eq:dbm_to_mw}:
+
+\begin{linenomath}
+	\begin{equation}
+		P_{dBm} = 10 \cdot \log_{10} \left( \frac{P_{mW}}{1mW} \right)
+		\label{eq:dbm_to_mw}
+	\end{equation}
+\end{linenomath}
+
+Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5 cm]{img/ConstantJammingSignal.png}
+	\caption{Constant jamming attack RSS values}
+	\label{fig:ConstantJammingSignal}
+\end{figure}   
+\unskip
+\begin{figure}[H]
+	\includegraphics[width=10.5 cm]{img/PeriodicJammingSignal.png}
+	\caption{Periodic jamming attack RSS values}
+	\label{fig:PeriodicJammingSignal}
+\end{figure}   
+\unskip
+
+\subsection {Algorithm Choice}
+
+When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm had to meet.
+The algorithm has to be able to classify anomalous samples with a high detection rate (Recall), while at the same time
+being lightweight enough to be run on a resource constrained device like a drone.
+The training phase should also be fast, as this would allow the drone to redetermine the normal transmission RSS values in a constantly changing environment.
+If the model didn't periodically redefine normal RSS values,
+it would be prone to false positives caused by the mobile nature of drones. 
+The model should be also required a small amount of storage to run effectively, as drones are usually very limited in internal memory.
+
+The algorithm that best fit these requirements was the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
+The Isolation Forest algorithm is a state-of-the-art unsupervised machine learning algorithm for anomaly detection, introduced by Liu et al.
+in 2008.
+Unlike traditional anomaly detection algorithms, which require the definition of a normal class, Isolation Forest is able to detect anomalies without explicitly defining its characteristics.
+This is achieved by leveraging the properties of anomalies themselves, i.e being few and separated from the majority of the data points.
+
+The algorithm works by building a forest of isolation trees.
+Each tree is built by randomly selecting one of the features and then splitting the data points based on a value randomly selected between the minimum and maximum value of the feature.
+This partitions the data into the
+left and right branches of the tree.
+The process is repeated recursively until all the data points are isolated.
+The height of a node, meaning the number of splits that were required to isolate it, is used to determine the anomaly score of the data point.
+The higher the number of splits, the more likely the data point is to be an anomaly.
+Isolation Forest is an \textit{ensamble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
+More trees mean more accuracy but also more computational power required.
+
+\begin{figure}[H]
+	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
+	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal datapoint \textbf{x1}\cite{IsolationForestLiu}.}
+	\label{fig:IsolationForest}
+\end{figure}   
+\unskip
+
+The chosen implementation for isolation forest is the one provided by the \textit{Scikit-learn} library \cite{IsolationForestScikitLearn} for Python 3. 
+The algorithm was tested on a Desktop PC with an Intel i7-6700 CPU and 16GB of RAM as well as on a Raspberry Pi 3 with a Quad Core 1.2GHz CPU and 1GB of RAM \cite{RaspberryPi3ModelB}.
+The graphs shown are the ones obtained on the Desktop PC for convenience.
+The ability of the algorithm to run effectively on a resource constrained device like the Raspberry Pi 3, that has hardware comparable to the one found in high-end commercial drones, was confirmed.
+
+\subsection{Evaluation Metrics}\label{EvaluationMetrics}
+
+The performance of the model was evaluated using the state-of-the-art evaluation metrics for machine learning classification algorithms.
+The metrics are all based on the number of true positives, false positives, true negatives and false negatives.
+A true positive is an anomalous data point that is correctly classified as such, while a false positive is a normal data point that is incorrectly classified as an anomaly.
+A true negative on the other hand is a normal data point that is correctly classified as a normal data point, while a false negative is an anomalous data point which is incorrectly classified as a normal data point.
+The evaluation metrics that we chose to use are the following:
+
+\begin{itemize}
+	\item \textbf{Accuracy:} The accuracy is the ratio of correctly classified data points to the total number of data points (equation \ref{eq:accuracy}).
+	\begin{equation}
+		\label{eq:accuracy}
+	  Accuracy = \frac{TP + TN}{TP + TN + FP + FN}
+	\end{equation}
+	\item \textbf{Precision:} The precision is the ratio of correctly classified anomalies to the total number of data points classified as anomalies (equation \ref{eq:precision}).
+	\begin{equation}
+		\label{eq:precision}
+	  Precision = \frac{TP}{TP + FP}
+	\end{equation}
+	\item \textbf{Recall:} The recall is the ratio of correctly classified anomalies to the total number of anomalies (equation \ref{eq:recall}).
+	\begin{equation}
+		\label{eq:recall}
+	  Recall = \frac{TP}{TP + FN}
+	\end{equation}
+	\item \textbf{F1 Score:} The F1 score is the harmonic mean of the precision and recall (equation \ref{eq:f1}).
+	\begin{equation}
+		\label{eq:f1}
+	  F1 = 2 \times \frac{Precision \times Recall}{Precision + Recall}
+	\end{equation}
+\end{itemize}
+
+The combination of these metrics gives us an important insight into the model's performance.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Results}
+
+\subsection{Parameters Tuning Phase}
+
+The first phase in our testing methodology was the tuning of the model's hyperparameters.
+The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in section \ref{EvaluationMetrics}) and then choosing the best performing parameter value.
+From the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, the parameters we decided to tune were the following:
+
+\begin{itemize}
+	\item \textbf{n\_estimators:} The number of base estimators in the ensamble, i.e the number of isolation trees used to compute the anomaly score of each datapoint. 
+	\item \textbf{max\_samples:} The max number of samples to draw from the dataset to train each tree.
+	\item \textbf{contamination:} The amount of outliers present in the training dataset.  
+\end{itemize}
+
+During the tuning phase, the untested hyperparameters were set to their default values of the \textit{Scikit-learn} implementation of the Isolation Forest (\ref{tab:isolation_forest_parameters}).
+
+\begin{table}[H]
+	\caption{Scikit-Learn Isolation Forest hyperparameters default values.\label{tab:isolation_forest_parameters}}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{Parameter} & \textbf{Default Value} \\
+	\midrule
+	n\_estimators & 100 \\
+	max\_samples & 'auto' \\
+	contamination & 0.1 \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+The model was evaluated using as input normal traffic samples concatenated with jamming attack samples (see code snippet \ref{alg:dataset_concatenation}). 
+This was done to simulate a real-world scenario where the model has to be able to classify correctly anomalous samples but also reduce the number of false positives during normal operation.
+
+\begin{algorithm}
+	\caption{Test input definition}\label{alg:dataset_concatenation}
+	\begin{algorithmic}[1]
+	\State normalTraffic $\gets$ ReadAndParseFile(NORMAL\_TRAFFIC\_FILE, normal\_traffic\_size)
+	\State jamming $\gets$ ReadAndParseFile(JAMMING\_FILE, jamming\_size)
+
+	\State testInput $\gets$ Concatenate(normalTraffic, jamming)
+	\end{algorithmic}
+\end{algorithm}
+
+The values whe chose for \textit{normal\_traffic\_size} and \textit{jamming\_size} are shown in table \ref{tab:dataset_sizes}.
+
+\begin{table}[H]
+	\caption{Dataset sizes used for the tuning and testing phases.}\label{tab:dataset_sizes}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{Dataset} & \textbf{Size} \\
+	\midrule
+	normal\_traffic\_size & 20000 \\
+	jamming\_size & 2000 \\
+	\bottomrule
+\end{tabularx}
+\end{table}
+
+The dataset is purposefully unbalanced between normal data points and anomalous points, as jamming attacks are usually rare events compared to normal network operation.
+
+In figure \ref{fig:InputSignal} we can see a representation of the input signal in the case of a constant jamming attack.
+The proposed results, unless otherwise specified, are based on the input signal shown in figure \ref{fig:InputSignal}, which employs constant jamming.
+Periodic jamming always showed comparable trends as constant jamming in all the tests performed.
+
+\begin{figure}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+	\centering
+	\includegraphics[width=19.5cm]{img/InputSignal.png}
+	\caption{Input signal in the case of Constant Jamming. The normal traffic signal is concatenated with the jamming signal.}\label{fig:InputSignal}
+\end{adjustwidth}
+\end{figure}
+
+\subsubsection{n\_estimators tuning}
+
+The first parameter that we decided to tune was the \textit{n\_estimators} parameter. The tuning values are shown in table \ref{tab:n_estimators_tuning}.
+
+\begin{table}[H]
+	\caption{n\_estimators tuning values.}\label{tab:n_estimators_tuning}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{n\_estimators} & \textbf{Values} \\
+	\midrule
+	Minimum & 1 \\
+	Maximum & 50 \\
+	Step & 1 \\
+	\bottomrule
+\end{tabularx}
+\end{table}
+
+The effect on the evaluation metrics of the model is shown in figure \ref{fig:n_estimators_tuning}.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5cm]{img/nEstimatorsTuning.png}
+	\caption{n\_estimators tuning results.}\label{fig:n_estimators_tuning}
+\end{figure}
+\unskip
+
+As we can see from the graph, a growing number of estimators initially correlates with a better model performance, but after a certain point the performance stabilizes. 
+In graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} is shown that the time required both for training and classification increases linearly with the number of estimators.
+This means that choosing an appropriate number of estimators is crucial, as it can greatly affect the model performance.
+
+\begin{figure}[H]
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{img/nEstimatorsTrainingTime.png}
+        \caption{n\_estimators training time.}
+        \label{fig:n_estimators_training_time}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{img/nEstimatorsClassificationTime.png}
+        \caption{n\_estimators classification time.}
+        \label{fig:n_estimators_classification_time}
+    \end{subfigure}
+    \caption{Comparison of n\_estimators training and classification times.}
+    \label{fig:estimators_time_comparison}
+\end{figure}
+
+We decided to choose \textbf{n\_estimators = 15}, as it provided a good balance between model performance and computational resources required.
+The model metrics keep slowly improving up until 45 estimators, but the minimal performance increase was not worth such a large increase in training and classification time, especially considering the resource-constrained nature of the scenario.
+
+\subsubsection{max\_samples tuning}
+
+The second parameter that we decided to tune was the \textit{max\_samples} parameter. The tuning values are shown in table \ref{tab:max_samples_tuning}.
+
+\begin{table}[H]
+	\caption{max\_samples tuning values.}\label{tab:max_samples_tuning}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{max\_samples} & \textbf{Values} \\
+	\midrule
+	Minimum & 1 \\
+	Maximum & 100 \\
+	Step & 1 \\
+	\bottomrule
+\end{tabularx}
+\end{table}
+
+From figure \ref{fig:max_samples_tuning} we can see that the model performance is not greatly affected by the \textit{max\_samples} parameter.
+This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a small training set.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5cm]{img/maxSamplesTuning.png}
+	\caption{max\_samples tuning results.}\label{fig:max_samples_tuning}
+\end{figure}
+\unskip
+
+Still, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in figure \ref{fig:max_samples_time_comparison}.
+Given the minimal performance differences but the impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/maxSamplesTrainingTime.png}
+		\caption{max\_samples training time.}
+		\label{fig:max_samples_training_time}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/maxSamplesClassificationTime.png}
+		\caption{max\_samples classification time.}
+		\label{fig:max_samples_classification_time}
+	\end{subfigure}
+	\caption{Comparison of max\_samples training and classification times.}
+	\label{fig:max_samples_time_comparison}
+\end{figure}
+
+\subsubsection{contamination tuning}
+
+The final parameter we focused on is the \textit{contamination} parameter. The tuning values are shown in table \ref{tab:contamination_tuning}.
+
+\begin{table}[H]
+	\caption{contamination tuning values.}\label{tab:contamination_tuning}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{contamination} & \textbf{Values} \\
+	\midrule
+	Minimum & 0.01 \\
+	Maximum & 0.5 \\
+	Step & 0.01 \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+The contamination parameter was by far the one that had the most impact on the model performance, as shown in figure \ref{fig:contamination_tuning}.
+As recall was the metric that we wanted to prioritize as it highlights the number of detections, we chose the value of \textbf{contamination = 0.09}.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5cm]{img/contaminationTuning.png}
+	\caption{contamination tuning results.}\label{fig:contamination_tuning}
+\end{figure}
+\unskip
+
+Our testing showed that, as expected, tuning of the contamination parameter had minimal impact on the training and classification time.
+
+\subsection{Model Testing Phase}
+
+\subsubsection{Standard model testing}\label{sec:standardModelTesting}
+
+After the tuning phase, we tested the model using the best performing hyperparameters, recapped in table \ref{tab:best_hyperparameters} and compared against the default parameters.
+
+\begin{table}[H]
+	\caption{Tuned hyperparameters and default values} \label{tab:best_hyperparameters}
 	\newcolumntype{C}{>{\centering\arraybackslash}X}
@@
 	\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
+	\textbf{Parameter} & \textbf{Tuned Value} & \textbf{Default Value} \\
 	\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data \textsuperscript{1}\\
+	n\_estimators & 15 & 100 \\
+	max\_samples & 10 & 'auto' \\
+	contamination & 0.09 & 0.1 \\
 	\bottomrule
 	\end{tabularx}
-\noindent{\footnotesize{\textsuperscript{1} Tables may have a footer.}}
 \end{table}
 
-The text continues here (Figure~\ref{fig2} and Table~\ref{tab2}).
+The model was tested against the input signal shown in figure \ref{fig:InputSignal}.
+In figure \ref{fig:standardIsolationResults} we can see the results of the model classification of the input signal with the tuned hyperparameters.
 
-% Example of a figure that spans the whole page width. The same concept works for tables, too.
 \begin{figure}[H]
@@
 	\centering
-\includegraphics[width=15.5cm]{Definitions/logo-mdpi}
+	\includegraphics[width=19.5cm]{img/StandardIsolationForestClassification.png}
+	\caption{Classification results from the tuned Isolation Forest model}\label{fig:standardIsolationResults}
 \end{adjustwidth}
-\caption{This is a wide figure.\label{fig2}}
 \end{figure}
 
+Table \ref{tab:confusionMatrix} and \ref{tab:performanceMetrics} show a comparison between the model performance with the tuned hyperparameters and the default hyperparameters.
+
 \begin{table}[H]
-\caption{This is a wide table.\label{tab2}}
-	\begin{adjustwidth}{-\extralength}{0cm}
+    \caption{Confusion Matrix Components Comparison.}\label{tab:confusionMatrix}
     \newcolumntype{C}{>{\centering\arraybackslash}X}
-		\begin{tabularx}{\fulllength}{CCCC}
+    \begin{tabularx}{\textwidth}{CCC}
     \toprule
-			\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}     & \textbf{Title 4}\\
+    \textbf{Metric} & \textbf{Tuned Isolation Forest} & \textbf{Default Isolation Forest} \\
     \midrule
-\multirow[m]{3}{*}{Entry 1 *}	& Data			& Data			& Data\\
-			  	                   & Data			& Data			& Data\\
-			             	      & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 2}    & Data			& Data			& Data\\
-			  	                  & Data			& Data			& Data\\
-			             	     & Data			& Data			& Data\\
-                   \midrule
-\multirow[m]{3}{*}{Entry 3}    & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
-                  \midrule
-\multirow[m]{3}{*}{Entry 4}   & Data			& Data			& Data\\
-			  	                 & Data			& Data			& Data\\
-			             	    & Data			& Data			& Data\\
+    \textbf{TP} & 1997 & 2000 \\
+    \textbf{FP} & 1565 & 1993 \\
+    \textbf{TN} & 18435 & 18007 \\
+    \textbf{FN} & 3 & 0 \\
     \bottomrule
     \end{tabularx}
-	\end{adjustwidth}
-	\noindent{\footnotesize{* Tables may have a footer.}}
 \end{table}
 
-%\begin{listing}[H]
-%\caption{Title of the listing}
-%\rule{\columnwidth}{1pt}
-%\raggedright Text of the listing. In font size footnotesize, small, or normalsize. Preferred format: left aligned and single spaced. Preferred border format: top border line and bottom border line.
-%\rule{\columnwidth}{1pt}
-%\end{listing}
+\begin{table}[H]
+    \caption{Performance Metrics Comparison.}\label{tab:performanceMetrics}
+    \newcolumntype{C}{>{\centering\arraybackslash}X}
+    \begin{tabularx}{\textwidth}{CCC}
+    \toprule
+    \textbf{Metric} & \textbf{Tuned Isolation Forest} & \textbf{Default Isolation Forest} \\
+    \midrule
+    \textbf{Accuracy} & 0.929 & 0.909 \\
+    \textbf{Precision} & 0.561 & 0.501 \\
+    \textbf{Recall} & 0.999 & 1.000 \\
+    \textbf{F1 Score} & 0.718 & 0.667 \\
+    \bottomrule
+    \end{tabularx}
+\end{table}
 
-Text.
+The tuning phase proved effective in improving the model's performance compared to the default hyperparameters.
+Still, despite reaching a very high Recall score in both scenarios, the model is still too prone to false positives, as indicated by the value of the Precision metric.
+This is most likely due to the nature of the normal traffic signal.
+As we see from figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the ones of the jamming attack samples, leading the model to falsely classify them as anomalies.
+This is most likely because of how the dataset was created, as the normal traffic samples were taken from a real-world scenario where the RSS values would be effected by external noise.
 
-Text.
+Instead of seeing this as a setback, we see this as a positive.
+The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving trough different environments and thus be subject to environmental noise.
 
-\subsection{Formatting of Mathematical Components}
+\subsubsection{Majority rule model testing} \label{sec:majorityRuleModelTesting}
 
-This is the example 1 of equation:
-\begin{linenomath}
-\begin{equation}
-a = 1,
-\end{equation}
-\end{linenomath}
-the text following an equation need not be a new paragraph. Please punctuate equations as regular text.
-%% If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct line numbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
+Having understood the nature of the problem, we decided to implement a majority rule system to reduce the number of false positives.
+The improved model would use the Tuned Isolation Forest model's results and then pass them to a Majority Rule module, as shown in figure \ref{fig:MajorityRuleDiagram}.
 
-This is the example 2 of equation:
+\begin{figure}[H]
+	\includegraphics[width=12.5 cm]{img/ModulesStructure.jpg}
+	\caption{Majority Rule system diagram. The Tuned Isolation Forest model results are passed to the Majority Rule module, that then provides the final classification.}
+	\label{fig:MajorityRuleDiagram}
+	\end{figure}   
+\unskip
+
+The mechanism of the Majority Rule module is simple.
+When a data point is passed to the Majority rule module, its classification class is inserted into a sliding window.
+If the datapoint is classified by the Tuned Isolation forest as an anomaly, the Majority Rule module checks the contents of the sliding window.
+If the
+majority of the datapoints in the window are classified as anomalies, the data point is classified as an anomaly.
+If the majority of the datapoints in the window are classified as normal, the data point is classified as normal.
+
+\begin{algorithm}
+	\caption{Majority Rule Algorithm}
+	\begin{algorithmic}[1]
+		\State \hspace{1em} $\text{window} \leftarrow []$
+
+		\For{each index in range(len(classification))}
+			\If{length of window equals predefined window size}
+				\State \hspace{1em} $\text{window.pop}(0)$
+			\EndIf
+
+			\State \hspace{1em} $\text{window.append}(\text{classification}[index])$
+
+			\If{current classification is OUTLIER and the count of OUTLIERS in the window 
+		 \State is less than or equal to half the window size}
+				\State \hspace{1em} $\text{classification}[index] \leftarrow \text{INLIERS}$
+			\EndIf
+		\EndFor
+
+		\State \hspace{1em} $\text{return classification}$
+	\end{algorithmic}
+\end{algorithm}
+
+To determine the optimal value for the \textit{window\_size} parameter, we tested the model in the same way as we did for the hyperparameters tuning phase.
+This time, the model parameters were set to the best performing values from the tuning phase (table \ref{tab:best_hyperparameters}).
+Table \ref{tab:window_size_tuning} shows the tuning values for the \textit{window\_size} parameter.
+
+\begin{table}[H]
+	\caption{window\_size tuning values.}\label{tab:window_size_tuning}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CC}
+	\toprule
+	\textbf{window\_size} & \textbf{Values} \\
+	\midrule
+	Minimum & 1 \\
+	Maximum & 100 \\
+	Step & 1 \\
+	\bottomrule
+\end{tabularx}
+\end{table}
+
+From figure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance.
+The optimal value for the \textit{window\_size} parameter was found to be \textbf{window\_size = 39}.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5cm]{img/WindowSizeTuning.png}
+	\caption{window\_size tuning results.}\label{fig:window_size_tuning}
+\end{figure}
+
+After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (figure \ref{fig:InputSignal}).
+The results of the model classification are shown in figure \ref{fig:majorityRuleIsolationResults}.
+
+\begin{figure}[H]
 	\begin{adjustwidth}{-\extralength}{0cm}
-\begin{equation}
-a = b + c + d + e + f + g + h + i + j + k + l + m + n + o + p + q + r + s + t + u + v + w + x + y + z
-\end{equation}
+	\centering
+	\includegraphics[width=19.5cm]{img/MajorityRuleIsolatioForestClassification.png}
+	\caption{Classification results from the Majority Rule Isolation Forest model}\label{fig:majorityRuleIsolationResults}
 	\end{adjustwidth}
+\end{figure}
 
-% Example of a page in landscape format (with table and table footnote).
-%\startlandscape
-%\begin{table}[H] %% Table in wide page
-%\caption{This is a very wide table.\label{tab3}}
-%	\begin{tabularx}{\textwidth}{CCCC}
-%		\toprule
-%		\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}	& \textbf{Title 4}\\
-%		\midrule
-%		Entry 1		& Data			& Data			& This cell has some longer content that runs over two lines.\\
-%		Entry 2		& Data			& Data			& Data\textsuperscript{1}\\
-%		\bottomrule
-%	\end{tabularx}
-%	\begin{adjustwidth}{+\extralength}{0cm}
-%		\noindent\footnotesize{\textsuperscript{1} This is a table footnote.}
-%	\end{adjustwidth}
-%\end{table}
-%\finishlandscape
+In table \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
 
-Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows:
-%% Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+\begin{table}[H]
+    \caption{Confusion Matrix Components Comparison.}\label{tab:majority_rule_confusionMatrix}
+    \newcolumntype{C}{>{\centering\arraybackslash}X}
+    \begin{tabularx}{\textwidth}{CCC}
+    \toprule
+    \textbf{Metric} & \textbf{Tuned Isolation Forest} & \textbf{Majority Rule Isolation Forest} \\
+    \midrule
+    \textbf{TP}  & 1997  & 1982 \\
+    \textbf{FN}  & 3     & 18   \\
+    \textbf{FP}  & 1565  & 27   \\
+    \textbf{TN}  & 18435 & 19973 \\
+    \bottomrule
+    \end{tabularx}
+\end{table}
 
-The text continues here. Proofs must be formatted as follows:
+\begin{table}[H]
+    \caption{Performance Metrics Comparison.}\label{tab:majority_rule_performanceMetrics}
+    \newcolumntype{C}{>{\centering\arraybackslash}X}
+    \begin{tabularx}{\textwidth}{CCC}
+    \toprule
+    \textbf{Metric} & \textbf{Tuned Isolation Forest} & \textbf{Majority Rule Isolation Forest} \\
+    \midrule
+    \textbf{Accuracy}  & 0.929 & 0.998 \\
+    \textbf{Precision} & 0.561 & 0.987 \\
+    \textbf{Recall}    & 0.999 & 0.991 \\
+    \textbf{F1 Score}  & 0.718 & 0.989 \\
+    \bottomrule
+    \end{tabularx}
+\end{table}
 
-%% Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase ``of Theorem 1'' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+The results show that the Majority Rule Model proved effective in mitigating the high number of false positives that was present in the first version of the model. 
+Given the resource constrained nature of the scenario, we decided to test the computational impact of the Majority Rule module against the standard tuned model. 
+Classification times and training times were measured for both models and the results are shown in figure pair \ref{fig:majority_rule_time_comparison}.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/classificationTimeComparison.png}
+		\caption{Classification time comparison.}
+		\label{fig:majority_rule_classification_time}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/trainingTimeComparison.png}
+		\caption{Training time comparison.}
+		\label{fig:majority_rule_training_time}
+	\end{subfigure}
+	\caption{Comparison of the standard tuned model and the Majority Rule model training and classification times.}
+	\label{fig:majority_rule_time_comparison}
+\end{figure}
+
+Graph \ref{fig:majority_rule_classification_time} shows that there is indeed a difference in classification time, with the standard model being faster.
+Figure \ref{fig:majority_rule_training_time} on the other hand shows that, as expected, training time is not affected by the Majority Rule module.
+
+\subsubsection{Comparison against existing solution}\label{sec:comparisonAgainstExistingSolution}
+
+As mentioned in section \ref{sec:DatasetChoice}, this work is based on the work of \cite{JammingDetectionIoT-Hussain}, where the authors proposed a solution for jamming attack detection based on CNNs.
+In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as a non reliable classification of normal traffic.
+We decided to compare our solution against the solution of the authors of the dataset we used. 
+The results show two significant figures as the results provided in the compared paper were in this format.
+Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics.
+Table \ref{tab:periodic_jamming_comparison} shows the comparison between the two models in the case of periodic jamming and table \ref{tab:normal_traffic_comparison} shows the comparison between the two models in classification of normal traffic.
+
+\begin{table}[H]
+	\caption{Comparison between the proposed approach and the approach of \cite{JammingDetectionIoT-Hussain} in the case of periodic jamming.}\label{tab:periodic_jamming_comparison}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CCC}
+	\toprule
+	\textbf{Metric} & \textbf{Proposed Approach} & \textbf{CNN Approach} \\
+	\midrule
+	\textbf{Accuracy}  & 0.98 & N.D \\
+	\textbf{Precision} & 0.99 & 0.73 \\
+	\textbf{Recall}    & 0.95 & 0.83 \\
+	\textbf{F1 Score}  & 0.97 & 0.78 \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+\begin{table}[H]
+	\caption{Comparison between the proposed approach and the approach of \cite{JammingDetectionIoT-Hussain} in the case of normal traffic classification.}\label{tab:normal_traffic_comparison}
+	\newcolumntype{C}{>{\centering\arraybackslash}X}
+	\begin{tabularx}{\textwidth}{CCC}
+	\toprule
+	\textbf{Metric} & \textbf{Proposed Approach} & \textbf{CNN Approach} \\
+	\midrule
+	\textbf{Accuracy}  & 1.00 & N.D \\
+	\textbf{Precision} & 1.00 & 0.80 \\
+	\textbf{Recall}    & 1.00 & 0.70 \\
+	\textbf{F1 Score}  & 1.00 & 0.75 \\
+	\bottomrule
+	\end{tabularx}
+\end{table}
+
+In figures \ref{fig:periodicJammingClassification} and \ref{fig:normalTrafficClassification} we can see the classification results of our proposed solution in the case of a testing sample size of $10000$ samples.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/OnlyPeriodicJamming.png}
+		\caption{Periodic Jamming classification.}
+		\label{fig:periodicJammingClassification}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.45\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/OnlyNormalTraffic.png}
+		\caption{Normal Traffic classification.}
+		\label{fig:normalTrafficClassification}
+	\end{subfigure}
+	\caption{Classification results of the proposed solution.}
+	\label{fig:proposedSolutionClassification}
+\end{figure}
 
@@
 
-Authors should discuss the results and how they can be interpreted from the perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+In this article we analyzed wether it was possible to employ an Isolation Forest model to detect jamming attacks in a 6G drone scenario.
+We tuned the hyperparameters of the model and tested it against the default Isolation Forest model.
+We achieved a considerable improvement in performance thanks to the tuning process (section \ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model suffered too much from a high number of false positives, caused by the inherent noise of the dataset.
+To mitigate this issue, we proposed the integration of the Isolation Forest model with a Majority Rule module (section \ref{sec:majorityRuleModelTesting}).
+The \textit{window\_size} parameter of the Majority Rule module was tuned to provide the best performance.
+The addition of the Majority Rule module proved extremely effective in reducing the number of false positives, greatly improving the model's precision.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Integration of the Majority Rule module also impacted total classification time as shown in figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the isolation forest model was preserved, meaning that the classification time complexity was kept at $O(n)$.
+In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
+The linear time complexity of the classification means that the algorithm is suitable for a resource constrained environment such as the proposed 6G drone scenario.
+
+As shown in section \ref{sec:comparisonAgainstExistingSolution}, the proposed solution outperformed the solution proposed by \cite{JammingDetectionIoT-Hussain} in both the detection of periodic jamming and the classification of normal traffic, while achieving the same performance against constant jamming attacks.
+We believe that the importance of correct classification of normal traffic is often underestimated, as a high number of false positives can lead to the activation of resource intensive countermeasures, even at times when they are not needed.
+
 \section{Conclusions}
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+\subsection{Real world integration}
+
+In a real world scenario, a 6G drone integrating the proposed solution would periodically run the tuning phase of the algorithm, selecting the best hyperparameters for the current environment.
+This could happen periodically or whenever there is a change in the environment caused by the drone moving to a different location.
+After tuning of the model, the drone would periodically sample incoming signals and classify them using the Majority Rule module.
+If the model detects a jamming attack, the drone could activate built in countermeasures like frequency hopping or DSSS to mitigate the effects of the attack.
+
+\subsection{Future Work}
+
+Future research could test the model against a wider range of jamming attacks types, as well as analyze the impact of real world noise on the model performance.
+Mounting the model on an actual drone would be the best way to achieve a real-world test and would provide valuable insights into how to improve the model further.
+
+As discussed in section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
+Future research could leverage these additional metrics to improve the model's performance.
+Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more features, such as the RSV metric proposed in \cite{JammingDetectionIoT-Hussain}.
 
@@
 DOS & Denial Of Service \\
+SNR & Signal to Noise Ratio \\
+RSSI & Received Signal Strength Indicator \\
+PDR & Packet Delivery Ratio \\
+CIA & Confidentiality, Integrity, Availability \\
+IoT & Internet of Things \\
+AI & Artificial Intelligence \\
+DSSS & Direct Sequence Spread Spectrum \\
+FHSS & Frequency Hopping Spread Spectrum \\
+OSI & Open Systems Interconnection \\
+dBm & Decibel-milliwatts \\
+CNN & Convolutional Neural Network \\
+RSV & Relative Speed Variation \\
 
-MDPI & Multidisciplinary Digital Publishing Institute\\
-DOAJ & Directory of open access journals\\
-TLA & Three letter acronym\\
-LD & Linear dichroism
 \end{tabular}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional
-\appendixtitles{no} % Leave argument "no" if all appendix headings stay EMPTY (then no dot is printed after "Appendix A"). If the appendix sections contain a heading then change the argument to "yes".
-\appendixstart
-\appendix
-\section[\appendixname~\thesection]{}
-\subsection[\appendixname~\thesubsection]{}
-The appendix is an optional section that can contain details and data supplemental to the main text---for example, explanations of experimental details that would disrupt the flow of the main text but nonetheless remain crucial to understanding and reproducing the research shown; figures of replicates for experiments of which representative data are shown in the main text can be added here if brief, or as Supplementary Data.
-Mathematical proofs of results not central to the paper can be added as an appendix.
-
-\begin{table}[H] 
-\caption{This is a table caption.\label{tab5}}
-\newcolumntype{C}{>{\centering\arraybackslash}X}
-\begin{tabularx}{\textwidth}{CCC}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-Entry 1		& Data			& Data\\
-Entry 2		& Data			& Data\\
-\bottomrule
-\end{tabularx}
-\end{table}
-
-\section[\appendixname~\thesection]{}
-All appendix sections must be cited in the main text. In the appendices, Figures, Tables, etc. should be labeled, starting with ``A''---e.g., Figure A1, Figure A2, etc.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{adjustwidth}{-\extralength}{0cm}
@@
 \reftitle{References}
-
-% Please provide either the correct journal abbreviation (e.g.
-according to the “List of Title Word Abbreviations” http://www.issn.org/services/online-services/access-to-the-ltwa/) or the full name of the journal.
-% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.
-
-%=====================================
-% References, variant A: external bibliography
-%=====================================
-%\bibliography{your_external_BibTeX_file}
 
@@
 
+\bibitem[Chorti et al.(2022)]{6GSecurity-Chorti}
+Chorti, A.; Hollanti, C.; Koorapaty, H.; Poor, H.V.
+Context-Aware Security for 6G Wireless: The Role of Physical Layer Security.
+{\em IEEE Communications Standards Magazine} {\bf 2022}, {\em 6}, 102--108.
+https://doi.org/10.1109/MCOMSTD.0001.2000082.
+
+\bibitem[Sciancalepore et al.(2023)]{JammingDetection-Sciancalepore}
+Sciancalepore, S.; Kusters, F.; Abdelhadi, N.K.; Oligeri, G.
+Jamming Detection in Low-BER Mobile Indoor Scenarios via Deep Learning.
+{\em arXiv} {\bf 2023}, eprint: 2306.10912.
+Available online: \url{https://arxiv.org/abs/2306.10912}.
+
+\bibitem[Boualouache and Engel(2023)]{MLMisbehavior5GBoualouache}
+Boualouache, A.; Engel, T.
+A Survey on Machine Learning-Based Misbehavior Detection Systems for 5G and Beyond Vehicular Networks.
+{\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
+https://doi.org/10.1109/COMST.2023.3236448.
+
+\bibitem[Hussain et al.(2023)]{JammingDetectionIoT-Hussain}
+Hussain, A.; Zhang, M.; Bhatia, S.; Cheng, L.
+Jamming Detection in IoT Wireless Networks: An Edge-AI Based Approach.
+In Proceedings of the 12th International Conference on the Internet of Things, IoT ’22; Association for Computing Machinery: Delft, Netherlands, 2023; pp.
+57--64.
+ISBN: 9781450396653.
+https://doi.org/10.1145/3567445.3567456.
+
+\bibitem[Sobot(2012)]{WirelessCommSobot}
+Sobot, R. \textit{Wireless Communication Electronics: Introduction to RF Circuits and Design}; Springer: 2012; p. 252. ISBN 9783030486303.
+
+\bibitem[Liu et al.(2008)]{IsolationForestLiu}
+Liu, F.T.; Ting, K.M.; Zhou, Z.-H.
+Isolation Forest.
+In Proceedings of the 2008 Eighth IEEE International Conference on Data Mining, Pisa, Italy, 2008; pp.
+413--422.
+https://doi.org/10.1109/ICDM.2008.17.
+
+\bibitem[Scikit-learn(2024)]{IsolationForestScikitLearn}
+Scikit-learn: Isolation Forest. Available online: \url{https://scikit-learn.org/stable/modules/generated/sklearn.ensemble.IsolationForest.html} (accessed on 14 September 2024).
+
+\bibitem[RaspberryPi(2024)]{RaspberryPi3ModelB}
+Raspberry Pi 3 Model B. Available online: \url{https://www.raspberrypi.com/products/raspberry-pi-3-model-b/} (accessed on 14 September 2024).
+
+\bibitem[Karagiannis and Argyriou(2018)]{JammingDetection-Karagiannis}
+Karagiannis, D.; Argyriou, A.
+Jamming attack detection in a pair of RF communicating vehicles using unsupervised machine learning.
+{\em Vehicular Communications} {\bf 2018}, {\em 13}, 56--63.
+https://doi.org/10.1016/j.vehcom.2018.05.001.
+Available online: \url{https://www.sciencedirect.com/science/article/pii/S221420961730222X}.
+
+\bibitem[Hong et al.(2023)]{HybridJammingDetection-Hong}
+Hong, S.; Kim, K.; Lee, S.-H.
+A Hybrid Jamming Detection Algorithm for Wireless Communications: Simultaneous Classification of Known Attacks and Detection of Unknown Attacks.
+{\em IEEE Communications Letters} {\bf 2023}, {\em 27}, 1769--1773.
+https://doi.org/10.1109/LCOMM.2023.3275694.
+
+\bibitem[Zuo et al.(2021)]{GPSSpoofingDetection-Zuo}
+Zuo, S.; Liu, Y.; Zhang, D.; Xin, P.; Liu, T.
+Detection of GPS Spoofing Attacks Based on Isolation Forest.
+In Proceedings of the 2021 IEEE 9th International Conference on Information, Communication and Networks (ICICN), Xi'an, China, 2021; pp.
+357--361.
+https://doi.org/10.1109/ICICN52636.2021.9673863.
+
 \end{thebibliography}

### 2024-09-26 article.tex
Finished the abstract

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{}
+\abstract{Drones are integral to various industries and their future integration with 6G network will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation.
+However, drone networks are particularly vulnerable to Jamming attacks, a type of Availability attack that can disrupt network operation and hinder drone functionality.
+In this paper, we propose an unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
+The base model was tuned to best fit the proposed scenario, but faced challenges related to environmental noise in the dataset.
+To address this, we introduced a Majority Rule module that significantly reduced the number of false positives, while still achieving high accuracy and precision.
+Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while reducing the occurrence of false positives in normal traffic.
+Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight solution for improved security against jamming attacks.
+}
 

### 2024-09-26 article.tex
Finished the abstract and keywords
Proofreading 4

@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Drones are integral to various industries and their future integration with 6G network will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation.
+\abstract{Drones are integral to various industries and their future integration with 6G networks will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation.
 However, drone networks are particularly vulnerable to Jamming attacks, a type of Availability attack that can disrupt network operation and hinder drone functionality.
@@
 To address this, we introduced a Majority Rule module that significantly reduced the number of false positives, while still achieving high accuracy and precision.
-Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while reducing the occurrence of false positives in normal traffic.
+Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while at the same time correctly identifying normal traffic.
 Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight solution for improved security against jamming attacks.
@@
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (List three to ten pertinent keywords specific to the article; yet reasonably common within the subject discipline.)}
+\keyword{Jamming attacks, Drones, 6G Networks, Isolation Forest, Machine Learning, Edge AI, IoT Security}
 
@@
 
-6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency but this in turn 
-will also bring forth new security challenges, specific to those applications.
+6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency, but this in turn 
+will also bring forth new security challenges specific to those applications.
 
@@
 
-This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors propose a machine learning based approach for the detection of jamming attacks in IoT networks. 
+This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a machine learning based approach for the detection of jamming attacks. 
 The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in a IoT drone scenario.
@@
 Everything) communication services. Among these use cases, the report identifies vehicle platooning, advanced and remote driving end extended situational awareness as some of the main benefits
-of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence 
+of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence, 
 would allow the drones to act autonomously in a coordinated manner.
@@
 it is able to overwhelm the legitimate signal, effectively blocking the communication between the devices \cite{DroneCommHassija}. 
-Since the ability to communicate is affected, Jamming attacks falls under the umbrella of attacks that target the \textit{Availability} of the service in the CIA triad classification \cite{DataIntegrityCawthra}.
+Since the ability to communicate is affected, Jamming attacks falls under the umbrella of attacks that target the \textit{Availability} of the service in the CIA triad \cite{DataIntegrityCawthra}. 
 Jamming attacks can be classified into 5 main categories, based on the attack pattern of the jammer:
@@
     \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, jamming each transmitted packet with a probability 
-    \(p\) based on the attack pattern\cite{VANETsAI-Lyamin}. 
+    \(p\) based on a random pattern\cite{VANETsAI-Lyamin}. 
     \item \textbf{Reactive Jamming:} A reactive jammer starts transmitting its jamming signal only when it senses energy in the communication channel, 
@@
 Also, as jamming attacks degrade or sometimes completely block the communication between the device and the base station, a centralized approach might not be feasible in this case.
-An lightweight edge approach on the other hand, while not as powerful as a centralized approach, would to provide real-time results to the device and would be able to operate even when the communication is disrupted, which is crucial in a jamming situation.
+A lightweight edge approach on the other hand, while not as powerful as a centralized approach, would to provide real-time results to the device and would be able to operate even when the communication is disrupted, which is crucial in a jamming situation.
 
@@
 The use of an AI model for jamming detection is particularly suitable for a 6G network, as the improved sensing capabilities would allow the model to train on a wide variety of diagnostic data, improving the detection rate and accuracy of the model.
-Furthermore, as the network is expected to be integrated with AI from the ground up, its highly likely that in the future drones will be integrated with AI-specific chips for a more efficient execution of AI models.
+Furthermore, as the network is expected to be integrated with AI from the ground up, its highly likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
 
@@
 The drone implements a simple unsupervised machine learning algorithm module, trained on nominal traffic RSS values.
-The module takes the sampled RSS values and classifies them as either normal or anomalous.
+The module takes the sampled RSS values and classifies them as either normal or anomalous (figure \ref{fig:moduleStructure}).
 Thanks to this classification module, the drone is able to determine wether or not a jamming attack is taking place.
+
+\begin{figure}[H]
+	\includegraphics[width=10.5 cm]{img/Simple module.jpg}
+	\caption{Proposed jamming detection module. The module takes the RSS values sampled by the drone and classifies them as either normal or anomalous.}
+	\label{fig:moduleStructure}
+\end{figure}   
+\unskip
 
@@
 open source software \textit{GNU Radio}.
-A second SDR radio was connected to a Raspberry Pi 3 and was chosen to receive the jamming signal.
+A second SDR radio was connected to a Raspberry Pi 3, designated to receive the jamming signal.
 The jamming radio operates at a frequency of $2.412 GHz$ with a Bandwidth of $40MHz$, while the Raspberry Pi 3 was programmed to sample the RSS values with a frequency of $32K$ samples per second.
@@
 The process is repeated recursively until all the data points are isolated.
-The height of a node, meaning the number of splits that were required to isolate it, is used to determine the anomaly score of the data point.
-The higher the number of splits, the more likely the data point is to be an anomaly.
+The height of a node, meaning the number of splits required to isolate it, is used to determine the anomaly score of the data point.
+The greater the number of splits, the more likely the data point is to be an anomaly.
 Isolation Forest is an \textit{ensamble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
@@
 
-During the tuning phase, the untested hyperparameters were set to their default values of the \textit{Scikit-learn} implementation of the Isolation Forest (\ref{tab:isolation_forest_parameters}).
+During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (table \ref{tab:isolation_forest_parameters}).
 
@@
 The proposed results, unless otherwise specified, are based on the input signal shown in figure \ref{fig:InputSignal}, which employs constant jamming.
-Periodic jamming always showed comparable trends as constant jamming in all the tests performed.
+Periodic jamming always showed comparable trends as constant jamming in all the performed tests.
 
@@
 We decided to choose \textbf{n\_estimators = 15}, as it provided a good balance between model performance and computational resources required.
-The model metrics keep slowly improving up until 45 estimators, but the minimal performance increase was not worth such a large increase in training and classification time, especially considering the resource-constrained nature of the scenario.
+The model metrics keep slowly improving up until $45$ estimators, but the minimal performance increase was not worth such a large increase in training and classification time, especially considering the resource-constrained nature of the scenario.
 
@@
 
-Instead of seeing this as a setback, we see this as a positive.
+Instead of seeing this as a setback, we see this an improvement opportunity.
 The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving trough different environments and thus be subject to environmental noise.
@@
 In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
-The linear time complexity of the classification means that the algorithm is suitable for a resource constrained environment such as the proposed 6G drone scenario.
+The linear time complexity of the classification and low memory usage make the proposed solution suitable for a resource constrained environment such as the analyzed 6G drone scenario.
 
@@
 Future research could test the model against a wider range of jamming attacks types, as well as analyze the impact of real world noise on the model performance.
-Mounting the model on an actual drone would be the best way to achieve a real-world test and would provide valuable insights into how to improve the model further.
+Mounting the model on an actual drone would be the best way to achieve a real-world test and would provide valuable insights into how to further improve its performance.
 
 As discussed in section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
-Future research could leverage these additional metrics to improve the model's performance.
-Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more features, such as the RSV metric proposed in \cite{JammingDetectionIoT-Hussain}.
+Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more classification features, such as the RSV metric proposed in \cite{JammingDetectionIoT-Hussain}.
 

### 2024-10-06 article.tex
Revisions pt.1

@@
 % Full title of the paper (Capitalized)
-\Title{AI-Based Detection of Jamming Attacks In 6G Drone Networks}
+\Title{A Lightweight Edge AI-based Jamming Detection Scheme for 6G Drone Networks}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{AI-Based Detection of Jamming Attacks in 6G Drone Networks}
+\TitleCitation{A Lightweight Edge AI-based Jamming Detection Scheme for 6G Drone Networks}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\) 
-\abstract{Drones are integral to various industries and their future integration with 6G networks will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation.
+\abstract{The future integration of drones in 6G networks will significantly enhance their capabilities, enabling a wide range of new applications based on autonomous operation.
 However, drone networks are particularly vulnerable to Jamming attacks, a type of Availability attack that can disrupt network operation and hinder drone functionality.
 In this paper, we propose an unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
-The base model was tuned to best fit the proposed scenario, but faced challenges related to environmental noise in the dataset.
-To address this, we introduced a Majority Rule module that significantly reduced the number of false positives, while still achieving high accuracy and precision.
-Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while at the same time correctly identifying normal traffic.
-Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight solution for improved security against jamming attacks.
+The base model has been tuned to best fit the proposed scenario, but faced challenges related to environmental noise in the dataset.
+To address this, we introduced a Majority Rule module which significantly reduced the number of false positives, achieving high accuracy and precision.
+Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while still correctly identifying normal traffic.
+Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight edge-based solution for enhancing security against jamming attacks.
 }
@@
 % Keywords
-\keyword{Jamming attacks, Drones, 6G Networks, Isolation Forest, Machine Learning, Edge AI, IoT Security}
+\keyword{Jamming attacks, 6G Drone Networks, Isolation Forest, Machine Learning, Edge AI, IoT Security}
 
@@
 
-The shift from 4G to 5G has been a generational leap has revolutionized connectivity around the world. 
+The shift from 4G to 5G has been a generational leap has revolutionized connectivity. 
 Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
@@
 
-In this paper we will focus on a specific aspect of the security of 6G networks, namely we will provide a machine learning based approach 
+In this paper we will focus on a specific aspect of the security of 6G networks, namely we will provide a lightweight edge-based machine learning approach 
 for the detection of jamming attacks in networks of drones.
@@
 \begin{enumerate}
-	\item \textbf{Topic overview:} In this section we will make a general overview of how drones can benefit from integration in 6G network, analyze jamming attacks, their types, mitigation and detection.
-Finally we will discuss the advantages of an edge AI approach for jamming detection.
-	\item \textbf{Materials and methods:} In this section we will define the scenario that we decided to analyze as well as the dataset, algorithm and evaluation metrics we chose for our tests. 
-	\item \textbf{Numerical Results:} In this section we will present the testing methodology, describe model tuning and testing phases and present the results obtained. 
-	\item \textbf{Discussion:} In this section we will comment the results obtained in the previous section and highlight the advantages of the proposed approach. 
-	\item \textbf{Conclusions:} In this section we will show how the proposed solution fits into a real world scenario and discuss possible future research directions.
+	\item \textbf{Topic overview:} General overview of the benefits of drone integration in 6G networks, analysis of jamming attacks: types, mitigation and detection.
+Discussion of the advantages provided by an edge AI approach for jamming detection.
+	\item \textbf{Materials and methods:} Description of the analyzed scenario, along with the dataset, algorithms, and evaluation metrics chosen for the tests.
+	\item \textbf{Numerical Results:} Explanation of the testing methodology, including model tuning, testing phases, and a presentation of the obtained results.
+	\item \textbf{Discussion:} Analysis of the results from the previous section, emphasizing the advantages of the proposed approach.
+	\item \textbf{Conclusions:} Overview of how the proposed solution applies to real-world scenarios, with a discussion on potential future research directions.
 \end{enumerate}
@@
 Detection of jamming attacks in wireless networks has been a topic of interest for the research community for many years.
-A wide variety of approaches have been proposed for the detection of jamming attacks
-in different types of networks, with most of the work focusing on the detection of jamming attacks in Vehicular Ad-Hoc Networks (VANETs)\cite{VANETsAI-Lyamin}.
+A wide variety of approaches have been proposed for different types of networks, with most of the work focusing on the detection of jamming attacks in Vehicular Ad-Hoc Networks (VANETs)\cite{VANETsAI-Lyamin}.
 
@@
 We also focused on the tuning of the model's hyperparameters to fit our specific scenario and compared it
-against the default model. In the tuning phase, the resource constrained nature of the scenario was taken into a count for the selection of the more appropriate hyperparameters.
+against the default model. In the tuning phase, the resource constrained nature of the scenario was a key deciding factor in the selection of the more appropriate hyperparameters.
 
@@
 
-\subsection{Drones in 6G Networks}
+\subsection{6G Drone Networks}
 
@@
 
-In report 22.886 \cite{5GV2XSultan} 3GPP, the organ responsible for the development and maintenance of the 5G standard, identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
-Everything) communication services. Among these use cases, the report identifies vehicle platooning, advanced and remote driving end extended situational awareness as some of the main benefits
+In report 22.886 \cite{5GV2XSultan} 3GPP identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
+Everything) communication services. Among these use cases, advanced and remote driving, vehicle platooning and extended situational awareness are identified as some of the main benefits
 of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence, 
@@
 
-Jamming attacks are a type of Denial of Service (DoS) attack that aims at disrupting the communication between two or more devices. 
-This is achieved by transmitting a powerful signal on the same frequency as the one used by the devices to communicate. If the jamming signal is strong enough, 
+Jamming attacks are a type of Denial of Service (DoS) attack that aims at disrupting the physical communication between two or more devices. 
+This is achieved by transmitting a signal on the same frequency as the one used by the devices to communicate. If the jamming signal power level is high enough, 
 it is able to overwhelm the legitimate signal, effectively blocking the communication between the devices \cite{DroneCommHassija}. 
@@
     \item \textbf{Periodic Jamming:} The jammer transmits a strong signal for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\).
-This pattern is repeated until the attack is stopped.
+This cycle is repeated until the attack is stopped.
     \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, jamming each transmitted packet with a probability 
@@
     \item \textbf{Smart Jamming:} A smart jammer is a more sophisticated type of jammer that is able to adapt its jamming signal to 
-    maximize the disruption of the communication between the devices. Smart jammers are able to modify their attack pattern based on the 
-    transmission specifics of the devices they are targeting and are able to adapt to changes in the communication channel\cite{AntiJammingV2V-Feng}.
+    maximize the disruption of the communication between the devices. Smart jammers employ a traffic analysis module, meaning they are able to modify their attack pattern based on the 
+    transmission specifics of the devices they are targeting and adapt to changes in the communication channel\cite{AntiJammingV2V-Feng}.
 \end{itemize}
-
-An effective Jamming detection AI model should achieve a high detection score against all the different types of jamming attacks.
 
@@
 If a jammer were able to completely block the communication between the drone and the base station, the drone would be left without any indication on how to behave and would need to activate an internal failsafe mechanism.
-This usually comes in the form of either a return to base procedure, a landing procedure or a hover in place procedure.
-All of these procedures leave the drone in a vulnerable position, as a bad actor could potentially capture the drone and use it for malicious purposes.
+This usually comes in the form of either a return to base procedure, a hover in place procedure or a land in place procedure.
+All of these approaches leave the drone in a vulnerable position, as a bad actor could potentially capture the drone and use it for malicious purposes.
 This is especially true when jamming attacks are used in combination with other types of attacks, such as spoofing attacks.
@@
 
-When presenting a machine learning based approach in an IoT setting, the question of where the AI model should be placed often arises.
+When presenting a Machine Learning (ML) based approach in an IoT setting, the question of where the AI model should be placed often arises.
 By their nature, IoT devices, and in turn drones, are usually resource constrained,
@@
 offloads the computational burden to a central server, that returns the results of the AI model to the device.
-While this approach might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
-communication with the central server means less time to react to the attack.
+While this scheme might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
+communication with the server means less time to react to the attack.
 Also, as jamming attacks degrade or sometimes completely block the communication between the device and the base station, a centralized approach might not be feasible in this case.
-A lightweight edge approach on the other hand, while not as powerful as a centralized approach, would to provide real-time results to the device and would be able to operate even when the communication is disrupted, which is crucial in a jamming situation.
+A lightweight edge approach on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted in a jamming situation.
 
@@
 
-When attempting to mitigate jamming attacks, the first step is always to detect that an attack is taking place. This can be done by monitoring the communication channel for signs of jamming. 
-The state of the art approaches involve the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The state of the art approaches for jamming detection involve the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
 The simplest approach when
@@
 While this approach is easy to implement and might be effective in some cases, it is not able to adapt to changes in the communication channel and might be prone to false positives.
-Implementing a machine learning based approach for jamming detection would allow the system to adapt to the changes in the communication channel and would be able to provide a more accurate detection of jamming attacks \cite{VANETsAI-Lyamin}.
+Implementing a ML based approach for jamming detection would allow the system to adapt to the changes in the communication channel and would be able to provide a more accurate detection of jamming attacks \cite{VANETsAI-Lyamin}.
 This is especially useful in mobile scenarios like
@@
 The use of an AI model for jamming detection is particularly suitable for a 6G network, as the improved sensing capabilities would allow the model to train on a wide variety of diagnostic data, improving the detection rate and accuracy of the model.
-Furthermore, as the network is expected to be integrated with AI from the ground up, its highly likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
+Furthermore, as the network is expected to be integrated with AI from the ground up, its likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
 
@@
 The drone implements a simple unsupervised machine learning algorithm module, trained on nominal traffic RSS values.
-The module takes the sampled RSS values and classifies them as either normal or anomalous (figure \ref{fig:moduleStructure}).
-Thanks to this classification module, the drone is able to determine wether or not a jamming attack is taking place.
-
-\begin{figure}[H]
-	\includegraphics[width=10.5 cm]{img/Simple module.jpg}
-	\caption{Proposed jamming detection module. The module takes the RSS values sampled by the drone and classifies them as either normal or anomalous.}
-	\label{fig:moduleStructure}
-\end{figure}   
-\unskip
-
-We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain point in time by transmitting a strong signal on the same frequency as the one used by the drone to communicate with the ground station.
+The module takes the sampled RSS values and classifies them as either normal or anomalous, making the drone able to determine wether or not a jamming attack is taking place.
+
+We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain instant by transmitting a high power signal on the same frequency as the one used by the drone to communicate with the ground station.
 We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning the drone has to rely on its internal classification algorithm to determine if a jamming attack is taking place and react accordingly.
@@
 The constant jamming attack could be caused by a ground jammer, as maintaining a constant jamming signal requires a large power source, while
-the periodic jamming attack could be caused by a drone jammer, as drones are usually battery powered and can only jam for a limited amount of time. 
-Employing a periodic jamming attack could help the malicious drone conserve energy and reduce the chances of being detected.
+the periodic jamming attack could be caused by a mobile jammer, for example a drone, as drones are usually battery powered and can only jam for a limited amount of time. 
+Employing a periodic jamming attack could help the malicious drone preserve energy and reduce the chances of being detected.
 
@@
 
-As 6G network traffic is not yet available, we chose an open-source dataset \cite{JammingDetectionIoT-Hussain} that analyses the RSS values 
+As 6G network traffic is not yet widely available, we chose an open-source dataset \cite{JammingDetectionIoT-Hussain} that analyses the RSS values 
 received by a Raspberry Pi 3 that is subject to periodic and constant jamming attacks.
 
-The dataset was created using a software-defined radio (SDR) connected to a laptop that was programmed to transmit a jamming signal using the 
+The dataset in \cite{JammingDetectionIoT-Hussain} was created using a software-defined radio (SDR) connected to a laptop that was programmed to transmit a jamming signal using the 
 open source software \textit{GNU Radio}.
@@
 The first file contains the RSS values sampled during a constant jamming attack, the second file contains the RSS values sampled during a periodic jamming attack and the third file contains the RSS values sampled during normal network operation.
-The samples are stored in a single column, with each row representing a single sample.
-The samples us the \textit{dBm (decibel-milliwatts)} unit of measurement, a logarithmic scale that measures the power of a signal in relation to 1 milliwatt.
-Conversion can be done using the formula \cite{WirelessCommSobot} shown in equation \ref{eq:dbm_to_mw}:
-
-\begin{linenomath}
-	\begin{equation}
-		P_{dBm} = 10 \cdot \log_{10} \left( \frac{P_{mW}}{1mW} \right)
-		\label{eq:dbm_to_mw}
-	\end{equation}
-\end{linenomath}
-
-Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack.
-
-\begin{figure}[H]
-	\includegraphics[width=10.5 cm]{img/ConstantJammingSignal.png}
+The samples are stored in a single column, with each row representing a single sampled RSS value, represented using the \textit{dBm (decibel-milliwatts)} unit of measurement.
+
+Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack, while figure \ref{fig:normalSignal} shows the RSS values sampled during normal network operation.
+
+\begin{figure}[H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+	\centering
+	\includegraphics[width=19.5cm]{img/ConstantJammingSignal.png}
+	\label{fig:ConstantJammingSignal}
+	\end{adjustwidth}
 	\caption{Constant jamming attack RSS values}
-	\label{fig:ConstantJammingSignal}
 \end{figure}  
@@
 \begin{figure}[H]
-	\includegraphics[width=10.5 cm]{img/PeriodicJammingSignal.png}
+	\begin{adjustwidth}{-\extralength}{0cm}
+	\centering
+	\includegraphics[width=19.5cm]{img/PeriodicJammingSignal.png}
+	\label{fig:PeriodicJammingSignal}
+	\end{adjustwidth}
 	\caption{Periodic jamming attack RSS values}
-	\label{fig:PeriodicJammingSignal}
 \end{figure}  
@@
 
-\subsection {Algorithm Choice}
-
-When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm had to meet.
+\begin{figure} [H]
+	\begin{adjustwidth}{-\extralength}{0cm}
+	\centering
+	\includegraphics[width=19.5cm]{img/NormalSignal.png}
+	\label{fig:normalSignal}
+	\end{adjustwidth}
+	\caption{Normal network operation RSS values}
+\end{figure}
+\unskip
+
+\subsection {Detection Algorithm}
+
+When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm is required to meet.
 The algorithm has to be able to classify anomalous samples with a high detection rate (Recall), while at the same time
-being lightweight enough to be run on a resource constrained device like a drone.
-The training phase should also be fast, as this would allow the drone to redetermine the normal transmission RSS values in a constantly changing environment.
-If the model didn't periodically redefine normal RSS values,
-it would be prone to false positives caused by the mobile nature of drones. 
+being lightweight enough in terms of memory usage and computational power to be run on a resource constrained device like a drone.
+The training phase should also be fast, as this would allow the drone to quickly determine the normal transmission RSS values in a constantly changing environment.
+A periodical redefinition of normal RSS values would
+limit the number of false positives caused by the drone mobility. 
 The model should be also required a small amount of storage to run effectively, as drones are usually very limited in internal memory.
@@
 The algorithm that best fit these requirements was the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
-The Isolation Forest algorithm is a state-of-the-art unsupervised machine learning algorithm for anomaly detection, introduced by Liu et al.
+The Isolation Forest (IF) algorithm is a state-of-the-art unsupervised machine learning algorithm for anomaly detection, introduced by Liu et al.
 in 2008.
-Unlike traditional anomaly detection algorithms, which require the definition of a normal class, Isolation Forest is able to detect anomalies without explicitly defining its characteristics.
-This is achieved by leveraging the properties of anomalies themselves, i.e being few and separated from the majority of the data points.
+Unlike traditional anomaly detection algorithms, which require the definition of a normal class, IF is able to detect anomalies without explicitly defining its characteristics.
+This is achieved by leveraging the properties of anomalies themselves, i.e being rare and separated from the majority of the data points.
 
@@
 left and right branches of the tree.
-The process is repeated recursively until all the data points are isolated.
+The process is repeated recursively until all the data points are isolated, as shown in figure \ref{fig:IsolationForest}.
 The height of a node, meaning the number of splits required to isolate it, is used to determine the anomaly score of the data point.
 The greater the number of splits, the more likely the data point is to be an anomaly.
-Isolation Forest is an \textit{ensamble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
+IF is an \textit{ensamble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
 More trees mean more accuracy but also more computational power required.
@@
 
-The chosen implementation for isolation forest is the one provided by the \textit{Scikit-learn} library \cite{IsolationForestScikitLearn} for Python 3. 
+The chosen implementation for IF is the one provided by the \textit{Scikit-learn} library \cite{IsolationForestScikitLearn} for Python 3. 
 The algorithm was tested on a Desktop PC with an Intel i7-6700 CPU and 16GB of RAM as well as on a Raspberry Pi 3 with a Quad Core 1.2GHz CPU and 1GB of RAM \cite{RaspberryPi3ModelB}.
@@
 
-The performance of the model was evaluated using the state-of-the-art evaluation metrics for machine learning classification algorithms.
+The performance of the model was evaluated using the state-of-the-art evaluation metrics for ML classification algorithms.
 The metrics are all based on the number of true positives, false positives, true negatives and false negatives.
-A true positive is an anomalous data point that is correctly classified as such, while a false positive is a normal data point that is incorrectly classified as an anomaly.
-A true negative on the other hand is a normal data point that is correctly classified as a normal data point, while a false negative is an anomalous data point which is incorrectly classified as a normal data point.
-The evaluation metrics that we chose to use are the following:
+The chosen evaluation metrics are the following:
 
 \begin{itemize}
-	\item \textbf{Accuracy:} The accuracy is the ratio of correctly classified data points to the total number of data points (equation \ref{eq:accuracy}).
+	\item \textbf{Accuracy:} the ratio of correctly classified data points to the total number of data points.
 	\begin{equation}
@@
 	\end{equation}
-	\item \textbf{Precision:} The precision is the ratio of correctly classified anomalies to the total number of data points classified as anomalies (equation \ref{eq:precision}).
+	\item \textbf{Precision:} the ratio of correctly classified anomalies to the total number of data points classified as anomalies.
 	\begin{equation}
@@
 	\end{equation}
-	\item \textbf{Recall:} The recall is the ratio of correctly classified anomalies to the total number of anomalies (equation \ref{eq:recall}).
+	\item \textbf{Recall:} the ratio of correctly classified anomalies to the total number of anomalies.
 	\begin{equation}
@@
 	\end{equation}
-	\item \textbf{F1 Score:} The F1 score is the harmonic mean of the precision and recall (equation \ref{eq:f1}).
+	\item \textbf{F1 Score:} the harmonic mean of the precision and recall.
 	\begin{equation}
@@
 
-The combination of these metrics gives us an important insight into the model's performance.
+The combination of these metrics gives us an important insight into the performance of the model.
 
@@
 The first phase in our testing methodology was the tuning of the model's hyperparameters.
-The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in section \ref{EvaluationMetrics}) and then choosing the best performing parameter value.
-From the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, the parameters we decided to tune were the following:
+The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in section \ref{EvaluationMetrics}) and then choosing the best values.
+From the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune were the following:
 
 \begin{itemize}
-	\item \textbf{n\_estimators:} The number of base estimators in the ensamble, i.e the number of isolation trees used to compute the anomaly score of each datapoint. 
-	\item \textbf{max\_samples:} The max number of samples to draw from the dataset to train each tree.
-	\item \textbf{contamination:} The amount of outliers present in the training dataset.  
+	\item \textbf{n\_estimators:} the number of base estimators in the ensamble, i.e the number of isolation trees used to compute the anomaly score of each datapoint. 
+	\item \textbf{max\_samples:} the max number of samples to draw from the dataset to train each tree.
+	\item \textbf{contamination:} the amount of outliers present in the training dataset.  
 \end{itemize}
@@
 The model was evaluated using as input normal traffic samples concatenated with jamming attack samples (see code snippet \ref{alg:dataset_concatenation}). 
-This was done to simulate a real-world scenario where the model has to be able to classify correctly anomalous samples but also reduce the number of false positives during normal operation.
+This was done to simulate a real-world scenario where the model has to be able to correctly classify anomalous samples but also reduce the number of false positives during normal operation.
 
@@
 
-The dataset is purposefully unbalanced between normal data points and anomalous points, as jamming attacks are usually rare events compared to normal network operation.
+The dataset is intentionally unbalanced between normal data points and anomalous points, as jamming attacks are usually rare events compared to normal network operation.
 
@@
         \includegraphics[width=19.5cm]{img/InputSignal.png}
-	\caption{Input signal in the case of Constant Jamming. The normal traffic signal is concatenated with the jamming signal.}\label{fig:InputSignal}
     \end{adjustwidth}
+    \caption{Input signal in the case of Constant Jamming. The normal traffic signal is concatenated with the jamming signal.}
+    \label{fig:InputSignal}
 \end{figure}
@@
 
-As we can see from the graph, a growing number of estimators initially correlates with a better model performance, but after a certain point the performance stabilizes. 
+As we can see from the graph, performance increases as the estimators increase, while converging to a stable value. 
 In graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} is shown that the time required both for training and classification increases linearly with the number of estimators.
@@
     \centering
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.49\textwidth}
         \centering
@@
     \hfill
-    \begin{subfigure}{0.45\textwidth}
+    \begin{subfigure}{0.49\textwidth}
         \centering
@@
 
-We decided to choose \textbf{n\_estimators = 15}, as it provided a good balance between model performance and computational resources required.
-The model metrics keep slowly improving up until $45$ estimators, but the minimal performance increase was not worth such a large increase in training and classification time, especially considering the resource-constrained nature of the scenario.
+We accordingly selected \textbf{n\_estimators = 15}, as it provided a good balance between model performance and computational resources required.
+The model metrics keep slowly improving until $45$ estimators, but the performance increase is minimal, making it not worth such a large increase in training and classification time, especially considering the resource-constrained nature of the scenario under consideration.
 
@@
 From figure \ref{fig:max_samples_tuning} we can see that the model performance is not greatly affected by the \textit{max\_samples} parameter.
-This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a small training set.
+This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a limited training set.
 
@@
 
-Still, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in figure \ref{fig:max_samples_time_comparison}.
+However, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in figure \ref{fig:max_samples_time_comparison}.
 Given the minimal performance differences but the impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
@@
 	\centering
-	\begin{subfigure}{0.45\textwidth}
+	\begin{subfigure}{0.49\textwidth}
 		\centering
@@
 	\hfill
-	\begin{subfigure}{0.45\textwidth}
+	\begin{subfigure}{0.49\textwidth}
 		\centering
@@
 
-The contamination parameter was by far the one that had the most impact on the model performance, as shown in figure \ref{fig:contamination_tuning}.
-As recall was the metric that we wanted to prioritize as it highlights the number of detections, we chose the value of \textbf{contamination = 0.09}.
+The contamination parameter is by far the one that has the most impact on the model performance, as shown in figure \ref{fig:contamination_tuning}.
+Since recall is the metric that we want to prioritize as it highlights the number of detections, we chose the value of \textbf{contamination = 0.09}.
 
@@
 
-Our testing showed that, as expected, tuning of the contamination parameter had minimal impact on the training and classification time.
+Our testing showed that, as expected, tuning of the contamination parameter has minimal impact on the training and classification time.
 
@@
 
-After the tuning phase, we tested the model using the best performing hyperparameters, recapped in table \ref{tab:best_hyperparameters} and compared against the default parameters.
+After the tuning phase, we tested the model using the best performing hyperparameters, detailed in table \ref{tab:best_hyperparameters} and compared against the default parameters.
 
@@
 	\includegraphics[width=19.5cm]{img/StandardIsolationForestClassification.png}
+	\end{adjustwidth}
 	\caption{Classification results from the tuned Isolation Forest model}\label{fig:standardIsolationResults}
-\end{adjustwidth}
-\end{figure}
-
-Table \ref{tab:confusionMatrix} and \ref{tab:performanceMetrics} show a comparison between the model performance with the tuned hyperparameters and the default hyperparameters.
+\end{figure}
+
+Table \ref{tab:confusionMatrix} and \ref{tab:performanceMetrics} show a comparison between the model performance with the tuned and the default hyperparameters.
 
@@
 
-The tuning phase proved effective in improving the model's performance compared to the default hyperparameters.
-Still, despite reaching a very high Recall score in both scenarios, the model is still too prone to false positives, as indicated by the value of the Precision metric.
+The tuning phase proved effective in improving the model's performance compared to the default hyperparameters,with an increase of $2.20\%$ in accuracy, $11.98\%$ in precision, and $7.64\%$ in the F1 score, while maintaining a nearly identical recall ($0.1\%$ drop).
+However, despite reaching a very high Recall score in both scenarios, the model is still too prone to false positives, as indicated by the value of the Precision metric.
 This is most likely due to the nature of the normal traffic signal.
-As we see from figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the ones of the jamming attack samples, leading the model to falsely classify them as anomalies.
-This is most likely because of how the dataset was created, as the normal traffic samples were taken from a real-world scenario where the RSS values would be effected by external noise.
-
-Instead of seeing this as a setback, we see this an improvement opportunity.
+As we see from figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the jamming attack samples, leading the model to classify them as anomalies.
+This is most likely because of how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be effected by external noise.
+
+Instead of a impairment, we see this an improvement opportunity.
 The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving trough different environments and thus be subject to environmental noise.
@@
 3GPP & 3rd Generation Partnership Project \\
+ML & Machine Learning \\
 V2X & Vehicle to Everything \\
@@
 dBm & Decibel-milliwatts \\
+IF & Isolation Forest \\
 CNN & Convolutional Neural Network \\

### 2024-10-06 article.tex
Revisions pt.2

@@
 
-Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack, while figure \ref{fig:normalSignal} shows the RSS values sampled during normal network operation.
+Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack, while Figure \ref{fig:normalSignal} shows the RSS values sampled during normal network operation.
 
@@
 left and right branches of the tree.
-The process is repeated recursively until all the data points are isolated, as shown in figure \ref{fig:IsolationForest}.
+The process is repeated recursively until all the data points are isolated, as shown in Figure \ref{fig:IsolationForest}.
 The height of a node, meaning the number of splits required to isolate it, is used to determine the anomaly score of the data point.
@@
 The first phase in our testing methodology was the tuning of the model's hyperparameters.
-The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in section \ref{EvaluationMetrics}) and then choosing the best values.
+The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in Section \ref{EvaluationMetrics}) and then choosing the best values.
 From the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune were the following:
@@
 
-The values whe chose for \textit{normal\_traffic\_size} and \textit{jamming\_size} are shown in table \ref{tab:dataset_sizes}.
+The values whe chose for \textit{normal\_traffic\_size} and \textit{jamming\_size} are shown in Table \ref{tab:dataset_sizes}.
 
@@
 
-In figure \ref{fig:InputSignal} we can see a representation of the input signal in the case of a constant jamming attack.
-The proposed results, unless otherwise specified, are based on the input signal shown in figure \ref{fig:InputSignal}, which employs constant jamming.
+In Figure \ref{fig:InputSignal} we can see a representation of the input signal in the case of a constant jamming attack.
+The proposed results, unless otherwise specified, are based on the input signal shown in Figure \ref{fig:InputSignal}, which employs constant jamming.
 Periodic jamming always showed comparable trends as constant jamming in all the performed tests.
@@
 
-The first parameter that we decided to tune was the \textit{n\_estimators} parameter. The tuning values are shown in table \ref{tab:n_estimators_tuning}.
+The first parameter that we decided to tune was the \textit{n\_estimators} parameter. The tuning values are shown in Table \ref{tab:n_estimators_tuning}.
 
@@
 
-The effect on the evaluation metrics of the model is shown in figure \ref{fig:n_estimators_tuning}.
+The effect on the evaluation metrics of the model is shown in Figure \ref{fig:n_estimators_tuning}.
 
@@
 
-The second parameter that we decided to tune was the \textit{max\_samples} parameter. The tuning values are shown in table \ref{tab:max_samples_tuning}.
+The second parameter that we decided to tune was the \textit{max\_samples} parameter. The tuning values are shown in Table \ref{tab:max_samples_tuning}.
 
@@
 	\caption{max\_samples tuning values.}\label{tab:max_samples_tuning}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
 	\begin{tabularx}{\textwidth}{CC}
@@
 
-From figure \ref{fig:max_samples_tuning} we can see that the model performance is not greatly affected by the \textit{max\_samples} parameter.
+From Figure \ref{fig:max_samples_tuning} we can see that the model performance is not greatly affected by the \textit{max\_samples} parameter.
 This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a limited training set.
@@
 
-However, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in figure \ref{fig:max_samples_time_comparison}.
+However, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in Figure \ref{fig:max_samples_time_comparison}.
 Given the minimal performance differences but the impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
@@
 
-The final parameter we focused on is the \textit{contamination} parameter. The tuning values are shown in table \ref{tab:contamination_tuning}.
+The final parameter we focused on is the \textit{contamination} parameter. The tuning values are shown in Table \ref{tab:contamination_tuning}.
 
@@
 	\caption{contamination tuning values.}\label{tab:contamination_tuning}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
 	\begin{tabularx}{\textwidth}{CC}
@@
 
-The contamination parameter is by far the one that has the most impact on the model performance, as shown in figure \ref{fig:contamination_tuning}.
+The contamination parameter is by far the one that has the most impact on the model performance, as shown in Figure \ref{fig:contamination_tuning}.
 Since recall is the metric that we want to prioritize as it highlights the number of detections, we chose the value of \textbf{contamination = 0.09}.
@@
 
-After the tuning phase, we tested the model using the best performing hyperparameters, detailed in table \ref{tab:best_hyperparameters} and compared against the default parameters.
+After the tuning phase, we tested the model using the best performing hyperparameters, detailed in Table \ref{tab:best_hyperparameters} and compared against the default parameters.
 
@@
 
-The model was tested against the input signal shown in figure \ref{fig:InputSignal}.
-In figure \ref{fig:standardIsolationResults} we can see the results of the model classification of the input signal with the tuned hyperparameters.
+The model was tested against the input signal shown in Figure \ref{fig:InputSignal}.
+In Figure \ref{fig:standardIsolationResults} we can see the results of the model classification of the input signal with the tuned hyperparameters.
 
@@
 This is most likely due to the nature of the normal traffic signal.
-As we see from figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the jamming attack samples, leading the model to classify them as anomalies.
+As we see from Figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the jamming attack samples, leading the model to classify them as anomalies.
 This is most likely because of how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be effected by external noise.
@@
 Having understood the nature of the problem, we decided to implement a majority rule system to reduce the number of false positives.
-The improved model would use the Tuned Isolation Forest model's results and then pass them to a Majority Rule module, as shown in figure \ref{fig:MajorityRuleDiagram}.
+The improved model would use the Tuned Isolation Forest model's results and then pass them to a Majority Rule module, as shown in Figure \ref{fig:MajorityRuleDiagram}.
 
@@
 
-The mechanism of the Majority Rule module is simple.
-When a data point is passed to the Majority rule module, its classification class is inserted into a sliding window.
-If the datapoint is classified by the Tuned Isolation forest as an anomaly, the Majority Rule module checks the contents of the sliding window.
+The logic behind the Majority Rule module is simple.
+The Majority Rule takes as input the classification results of the IF model and inserts them into a sliding window.
+If the datapoint is classified by the Tuned IF as an anomaly, the Majority Rule module checks the contents of the sliding window.
 If the
 majority of the datapoints in the window are classified as anomalies, the data point is classified as an anomaly.
-If the majority of the datapoints in the window are classified as normal, the data point is classified as normal.
+If the majority of the datapoints in the window are classified as normal, the data point is classified as normal (see code snipped \ref{alg:majority_rule}).
 
 \begin{algorithm}
-	\caption{Majority Rule Algorithm}
+	\caption{Majority Rule Algorithm}\label{alg:majority_rule}
 	\begin{algorithmic}[1]
@@
 
-To determine the optimal value for the \textit{window\_size} parameter, we tested the model in the same way as we did for the hyperparameters tuning phase.
-This time, the model parameters were set to the best performing values from the tuning phase (table \ref{tab:best_hyperparameters}).
+To determine the optimal value for the \textit{window\_size} parameter, we test the model in the same way as in the hyperparameters tuning phase.
+The model parameters were set to the best performing values from the tuning phase (table \ref{tab:best_hyperparameters}).
 Table \ref{tab:window_size_tuning} shows the tuning values for the \textit{window\_size} parameter.
@@
 	\caption{window\_size tuning values.}\label{tab:window_size_tuning}
-	\newcolumntype{C}{>{\centering\arraybackslash}X}
 	\begin{tabularx}{\textwidth}{CC}
@@
 
-From figure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance.
+FromFigure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance.
 The optimal value for the \textit{window\_size} parameter was found to be \textbf{window\_size = 39}.
@@
 After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (figure \ref{fig:InputSignal}).
-The results of the model classification are shown in figure \ref{fig:majorityRuleIsolationResults}.
+The results of the model classification are shown in Figure \ref{fig:majorityRuleIsolationResults}.
 
@@
 
-In table \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
+In Table \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
 
@@
     \caption{Confusion Matrix Components Comparison.}\label{tab:majority_rule_confusionMatrix}
-    \newcolumntype{C}{>{\centering\arraybackslash}X}
     \begin{tabularx}{\textwidth}{CCC}
@@
     \caption{Performance Metrics Comparison.}\label{tab:majority_rule_performanceMetrics}
-    \newcolumntype{C}{>{\centering\arraybackslash}X}
     \begin{tabularx}{\textwidth}{CCC}
@@
 
-The results show that the Majority Rule Model proved effective in mitigating the high number of false positives that was present in the first version of the model. 
+The results show that the Majority Rule Model is effective in mitigating the high number of false positives that were present in the first version of the model. 
 Given the resource constrained nature of the scenario, we decided to test the computational impact of the Majority Rule module against the standard tuned model. 
-Classification times and training times were measured for both models and the results are shown in figure pair \ref{fig:majority_rule_time_comparison}.
+Classification times and training times were measured for both models and the results are shown in Figures \ref{fig:majority_rule_classification_time} and \ref{fig:majority_rule_training_time}.
 
@@
 Graph \ref{fig:majority_rule_classification_time} shows that there is indeed a difference in classification time, with the standard model being faster.
+This is due to the additional computational complexity added by the Majority Rule module, which requires updating and checking of the sliding window for each classified datapoint.
 Figure \ref{fig:majority_rule_training_time} on the other hand shows that, as expected, training time is not affected by the Majority Rule module.
@@
 
-As mentioned in section \ref{sec:DatasetChoice}, this work is based on the work of \cite{JammingDetectionIoT-Hussain}, where the authors proposed a solution for jamming attack detection based on CNNs.
+As mentioned in Section \ref{sec:DatasetChoice}, this work is based on the work of \cite{JammingDetectionIoT-Hussain}, where the authors proposed a solution for jamming attack detection based on CNNs.
 In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as a non reliable classification of normal traffic.
 We decided to compare our solution against the solution of the authors of the dataset we used. 
-The results show two significant figures as the results provided in the compared paper were in this format.
+The results show two significant Figures as the results provided in the compared paper were in this format.
 Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics.
-Table \ref{tab:periodic_jamming_comparison} shows the comparison between the two models in the case of periodic jamming and table \ref{tab:normal_traffic_comparison} shows the comparison between the two models in classification of normal traffic.
+Table \ref{tab:periodic_jamming_comparison} shows the comparison between the two models in the case of periodic jamming and Table \ref{tab:normal_traffic_comparison} shows the comparison between the two models in classification of normal traffic.
 
@@
 
-In figures \ref{fig:periodicJammingClassification} and \ref{fig:normalTrafficClassification} we can see the classification results of our proposed solution in the case of a testing sample size of $10000$ samples.
+In Figures \ref{fig:periodicJammingClassification} and \ref{fig:normalTrafficClassification} we can see the classification results of our proposed solution in the case of a testing sample size of $10000$ samples.
 
@@
 
-Integration of the Majority Rule module also impacted total classification time as shown in figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the isolation forest model was preserved, meaning that the classification time complexity was kept at $O(n)$.
+Integration of the Majority Rule module also impacted total classification time as shown in Figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the isolation forest model was preserved, meaning that the classification time complexity was kept at $O(n)$.
 In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
@@
 
-As shown in section \ref{sec:comparisonAgainstExistingSolution}, the proposed solution outperformed the solution proposed by \cite{JammingDetectionIoT-Hussain} in both the detection of periodic jamming and the classification of normal traffic, while achieving the same performance against constant jamming attacks.
+As shown in Section \ref{sec:comparisonAgainstExistingSolution}, the proposed solution outperformed the solution proposed by \cite{JammingDetectionIoT-Hussain} in both the detection of periodic jamming and the classification of normal traffic, while achieving the same performance against constant jamming attacks.
 We believe that the importance of correct classification of normal traffic is often underestimated, as a high number of false positives can lead to the activation of resource intensive countermeasures, even at times when they are not needed.
@@
 \section{Conclusions}
-
-\subsection{Real world integration}
 
@@
 
-\subsection{Future Work}
-
 Future research could test the model against a wider range of jamming attacks types, as well as analyze the impact of real world noise on the model performance.
@@
 
-As discussed in section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
+As discussed in Section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
 Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more classification features, such as the RSV metric proposed in \cite{JammingDetectionIoT-Hussain}.
@@
 
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+This Section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 

### 2024-10-09 article.tex
Fixed some figures labels

@@
 % Full title of the paper (Capitalized)
-\Title{A Lightweight Edge AI-based Jamming Detection Scheme for 6G Drone Networks}
+\Title{A Lightweight AI-based Jamming Detection for Drone Networks}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{A Lightweight Edge AI-based Jamming Detection Scheme for 6G Drone Networks}
+\TitleCitation{A Lightweight AI-based Jamming Detection for Drone Networks}
 
@@
 
+We conceptualize a scenario where a drone is subject to constant and periodic jamming and has to rely on an internal AI model to detect the attack and apply the appropriate countermeasures.
+IoT devices in 6G networks
+will be equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
+This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
+Our solution is designed to run on a resource constrained device like a drone, and is able to detect both constant and periodic jamming attacks with a high degree of accuracy.
+
 The paper is divided in 5 sections: 
@@
 Discussion of the advantages provided by an edge AI approach for jamming detection.
-	\item \textbf{Materials and methods:} Description of the analyzed scenario, along with the dataset, algorithms, and evaluation metrics chosen for the tests.
+	\item \textbf{System Model:} Description of the analyzed scenario, along with the dataset, algorithms, and evaluation metrics chosen for the tests.
 	\item \textbf{Numerical Results:} Explanation of the testing methodology, including model tuning, testing phases, and a presentation of the obtained results.
@@
 
-We apply a similar solution to the one proposed in \cite{HybridJammingDetection-Hong} to the scenario of a 6G drone network, testing the model against the dataset proposed in \cite{JammingDetectionIoT-Hussain}.
+Our solution also leverages the Isolation Forest algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset proposed in \cite{JammingDetectionIoT-Hussain}.
+We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve the resistance of the model to environmental noise.
 Our approach reached a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
@@
 
-In report 22.886 \cite{5GV2XSultan} 3GPP identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
+In technical report 22.886 \cite{5GV2XSultan} 3GPP identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
 Everything) communication services. Among these use cases, advanced and remote driving, vehicle platooning and extended situational awareness are identified as some of the main benefits
@@
 
-The state of the art approaches for jamming detection involve the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
 The simplest approach when
@@
 
-\section{Materials and Methods}
+\section{System Model}
 
@@
 	\includegraphics[width=19.5cm]{img/ConstantJammingSignal.png}
-	\label{fig:ConstantJammingSignal}
 	\end{adjustwidth}
-	\caption{Constant jamming attack RSS values}
+	\caption{Constant jamming attack RSS values}\label{fig:ConstantJammingSignal}
 \end{figure}  
@@
 	\includegraphics[width=19.5cm]{img/PeriodicJammingSignal.png}
-	\label{fig:PeriodicJammingSignal}
 	\end{adjustwidth}
-	\caption{Periodic jamming attack RSS values}
+	\caption{Periodic jamming attack RSS values}\label{fig:PeriodicJammingSignal}
 \end{figure}  
@@
 	\includegraphics[width=19.5cm]{img/NormalSignal.png}
-	\label{fig:normalSignal}
 	\end{adjustwidth}
-	\caption{Normal network operation RSS values}
+	\caption{Normal network operation RSS values}\label{fig:normalSignal}
 \end{figure}

### 2024-10-09 article.tex
Revisions pt.3

@@
 % Full title of the paper (Capitalized)
-\Title{A Lightweight AI-based Jamming Detection for Drone Networks}
+\Title{A Lightweight AI-based  Approach For Drone Jamming Detection}
 
 % MDPI internal command: Title for citation in the left column
-\TitleCitation{A Lightweight AI-based Jamming Detection for Drone Networks}
+\TitleCitation{A Lightweight AI-based  Approach For Drone Jamming Detection}
 
@@
 % MDPI internal command: Authors, for citation in the left column
-\AuthorCitation{Cibecchini, S.; Chiti, F.; Lastname, F.}
+\AuthorCitation{Cibecchini, S.; Chiti, F.; Pierucci, L.}
 % If this is a Chicago style journal: Lastname, Firstname, Firstname Lastname, and Firstname Lastname.
@@
 This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
-Our solution is designed to run on a resource constrained device like a drone, and is able to detect both constant and periodic jamming attacks with a high degree of accuracy.
+
+Our solution is designed to run on a resource constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
+Despite the low resources requirements, the proposed approach is able to detect both constant and periodic jamming attacks with a high degree of accuracy, as well as correctly classify normal traffic.
 
@@
 	\item \textbf{System Model:} Description of the analyzed scenario, along with the dataset, algorithms, and evaluation metrics chosen for the tests.
-	\item \textbf{Numerical Results:} Explanation of the testing methodology, including model tuning, testing phases, and a presentation of the obtained results.
+	\item \textbf{Model Performance:} Explanation of the testing methodology, including model tuning, testing phases, and a presentation of the obtained results.
 	\item \textbf{Discussion:} Analysis of the results from the previous section, emphasizing the advantages of the proposed approach.
@@
 
-Our solution also leverages the Isolation Forest algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset proposed in \cite{JammingDetectionIoT-Hussain}.
+Our solution also leverages the Isolation Forest algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset created by \cite{JammingDetectionIoT-Hussain}.
 We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve the resistance of the model to environmental noise.
 Our approach reached a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
-We also focused on the tuning of the model's hyperparameters to fit our specific scenario and compared it
+We also detailed the tuning of the model's hyperparameters to fit our specific scenario and compared it
 against the default model. In the tuning phase, the resource constrained nature of the scenario was a key deciding factor in the selection of the more appropriate hyperparameters.
@@
 
-In the military sector, the effectiveness of drones is widely recognized, both for high and low end models. For example, in the Ukraine war even cheap FPV drones 
-mounted with explosives were successfully used to destroy much more expensive equipment \cite{DroneCombatUkraine}.
+In the military sector, the effectiveness of drones is widely recognized, both for high and low end models and are being used in a variety of roles, from more passive roles like surveillance and intelligence gathering, to more active roles like
+delivery of explosives and targeted strikes.
 
@@
 Also, as jamming attacks degrade or sometimes completely block the communication between the device and the base station, a centralized approach might not be feasible in this case.
-A lightweight edge approach on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted in a jamming situation.
+A collaborative edge approach would suffer from the same problems, as there is a high likelihood that the communication between the devices would be disrupted by the attack. 
+Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted in a jamming situation.
 
@@
 	\centering
-	\includegraphics[width=19.5cm]{img/ConstantJammingSignal.png}
+	\includegraphics[width=21cm]{img/ConstantJammingSignal.png}
 	\end{adjustwidth}
@@
 	\centering
-	\includegraphics[width=19.5cm]{img/PeriodicJammingSignal.png}
+	\includegraphics[width=21cm]{img/PeriodicJammingSignal.png}
 	\end{adjustwidth}
@@
 	\centering
-	\includegraphics[width=19.5cm]{img/NormalSignal.png}
+	\includegraphics[width=21cm]{img/NormalSignal.png}
 	\end{adjustwidth}
@@
 The chosen implementation for IF is the one provided by the \textit{Scikit-learn} library \cite{IsolationForestScikitLearn} for Python 3.
-The algorithm was tested on a Desktop PC with an Intel i7-6700 CPU and 16GB of RAM as well as on a Raspberry Pi 3 with a Quad Core 1.2GHz CPU and 1GB of RAM \cite{RaspberryPi3ModelB}.
-The graphs shown are the ones obtained on the Desktop PC for convenience.
-The ability of the algorithm to run effectively on a resource constrained device like the Raspberry Pi 3, that has hardware comparable to the one found in high-end commercial drones, was confirmed.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
+\section{Model Performance }
 
@@
         \centering
-        \includegraphics[width=19.5cm]{img/InputSignal.png}
+        \includegraphics[width=21cm]{img/InputSignal.png}
     \end{adjustwidth}
@@
 	\centering
-	\includegraphics[width=19.5cm]{img/StandardIsolationForestClassification.png}
+	\includegraphics[width=21cm]{img/StandardIsolationForestClassification.png}
 	\end{adjustwidth}
@@
 \end{table}
+
+Figures \ref{fig:ConfusionMatrixStandardIF} and \ref{fig:ConfusionMatrixTunedIF} show, respectively, the confusion matrix for the default and the tuned Isolation Forest model.
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/ConfusionMatrixStandardIF.png}
+		\caption{}
+		\label{fig:ConfusionMatrixStandardIF}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/ConfusionMatrixTunedIF.png}
+		\caption{}
+		\label{fig:ConfusionMatrixTunedIF}
+	\end{subfigure}
+	\caption{Confusion Matrix for the default Isolation Forest model \textbf{(a)} and the tuned Isolation Forest model \textbf{(b)}.}
+	\label{fig:ConfusionMatrixStandardTunedIF}
+\end{figure}
 
@@
 	\centering
-	\includegraphics[width=19.5cm]{img/MajorityRuleIsolatioForestClassification.png}
+	\includegraphics[width=21cm]{img/MajorityRuleIsolatioForestClassification.png}
 	\caption{Classification results from the Majority Rule Isolation Forest model}\label{fig:majorityRuleIsolationResults}
@@
 \end{table}
+
+\begin{figure}[H]
+	\centering
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/ConfusionMatrixTunedIF.png}
+		\caption{}
+		\label{fig:ConfusionMatrixStandardTunedIF1}
+	\end{subfigure}
+	\hfill
+	\begin{subfigure}{0.49\textwidth}
+		\centering
+		\includegraphics[width=\textwidth]{img/ConfusionMatrixMajorityIF.png}
+		\caption{}
+		\label{fig:ConfusionMatrixMajorityIF}
+	\end{subfigure}
+	\caption{Confusion Matrix for the tuned Isolation Forest model \textbf{(a)} and the Majority Rule Isolation Forest model \textbf{(b)}.}
+	\label{fig:ConfusionMatrixTunedMajorityIF}
+\end{figure}
 
@@
 
-\bibitem[Rao et al.(2024)]{DroneCombatUkraine}
-Rao, A.; Zafra, M.; Hunder, M.; Kiyada, S.
-How drone combat in Ukraine is changing warfare.
-Available online: \url{https://www.reuters.com/graphics/UKRAINE-CRISIS/DRONES/dwpkeyjwkpm/} (accessed on 13 September 2024).
-
 \bibitem[Cawthra(2020)]{DataIntegrityCawthra}

### 2024-10-09 article.tex
Revisions pt.4

@@
 A collaborative edge approach would suffer from the same problems, as there is a high likelihood that the communication between the devices would be disrupted by the attack. 
-Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted in a jamming situation.
+Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted, as in a jamming situation.
 
@@
 
-FromFigure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance.
+From Figure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance.
 The optimal value for the \textit{window\_size} parameter was found to be \textbf{window\_size = 39}.
@@
 
-After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (figure \ref{fig:InputSignal}).
+After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (Figure\ref{fig:InputSignal}).
 The results of the model classification are shown in Figure \ref{fig:majorityRuleIsolationResults}.
@@
 
-In Table \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
+In Tables \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
 
@@
 
+Our solution is able to achieve considerably better results in the classification of normal traffic and periodic jamming, while maintaining the same level of performance in the case of constant jamming.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Conclusions}
+
+In this article we analyzed the use of the Isolation Forest unsupervised machine learning algorithm for the detection of jamming attacks.
+We compared the performance of the base Isolation Forest model against a version specifically tuned to detect jamming attacks.
+In the tuning phase, we paid particular attention to the computational added by each parameter and tried to find the balance between performance and efficiency.
+We then proposed the integration of a Majority Rule module to reduce the number of false positives caused by the inherent noise of the dataset.
+The Majority Rule module was tuned to provide the best performance and proved effective in mitigating the problem of false positives, while still maintaining a linear complexity in classification time.
+We tested the model against a dataset that included normal traffic, constant jamming, and periodic jamming attacks, with an unbalanced number of normal traffic samples and jamming attack samples to better reflect a real-world scenario.
+We compared the performance of the proposed solution against the solution proposed by \cite{JammingDetectionIoT-Hussain} and found that our solution outperformed the existing solution in both the detection of periodic jamming and the classification of normal traffic, while retaining the same performance against constant jamming attacks.
 

### 2024-10-09 article.tex
Contributions etc

@@
 % Author Orchid ID: enter ID or remove command
-\newcommand{\orcidauthorA}{0000-0000-0000-000X} % Add \orcidA{} behind the author's name
-%\newcommand{\orcidauthorB}{0000-0000-0000-000X} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorA}{0009-0001-6239-0572} % Add \orcidA{} behind the author's name
+\newcommand{\orcidauthorB}{0000-0002-0267-4733} % Add \orcidB{} behind the author's name
+\newcommand{\orcidauthorC}{0000-0001-6271-7988}
 
 % Authors, for the paper (add full first names)
-\Author{Sergio Cibecchini $^{1,\dagger}$\orcidA{}, Francesco Chiti $^{2}$ and Laura Pierucci$^{2,}$*}
+\Author{Sergio Cibecchini*\orcidA{}, Francesco Chiti $^{1}$\orcidB{} and Laura Pierucci$^{1}$\orcidC{}}
 
@@
 \address{%
-$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
-$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}
+$^{1}$ \quad Associate Professor at Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Firenze, Italy; francesco.chiti@unifi.it, laura.pierucci@unifi.it
+}
 
 % Contact information of the corresponding author
-\corres{Correspondence: sergio.cibecchini@gmail.com; Tel.: (optional; include country code; if there are multiple corresponding authors, add author initials) +xx-xxxx-xxx-xxxx (F.L.)}
+\corres{Correspondence: sergio.cibecchini@gmail.com}
 
 % Current address and/or shared authorship
-\firstnote{Current address: Affiliation.}  % Current address should not be the same as any items in the Affiliation section.
-\secondnote{These authors contributed equally to this work.}
+%\firstnote{Current address: Affiliation.}  % Current address should not be the same as any items in the Affiliation section.
+%\secondnote{These authors contributed equally to this work.}
 % The commands \thirdnote{} till \eighthnote{} are available for further notes
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Patents}
-
-This Section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+%\section{Patents}
+
+%This Section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.
-The following statements should be used ``Conceptualization, X.X.
-and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y.
-and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing---original draft preparation, X.X.; writing---review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y.
-All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation.
-Authorship must be limited to those who have contributed substantially to the work~reported.}
-
-\funding{Please add: ``This research received no external funding'' or ``This research was funded by NAME OF FUNDER grant number XXX.'' and  and ``The APC was funded by XXX''.
-Check carefully that the details given are accurate and use the standard spelling of funding agency names at \url{https://search.crossref.org/funding}, any errors may affect your future funding.}
-
-\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
+\authorcontributions{Conceptualization, Francesco Chiti and Sergio Cibecchini; methodology, Sergio Cibecchini; software, Sergio Cibecchini; validation, Francesco Chiti and Laura Pierucci; formal analysis, Sergio Cibecchini; investigation, Sergio Cibecchini; resources, Francesco Chiti and Laura Pierucci; data curation, Sergio Cibecchini; writing—original draft preparation, Sergio Cibecchini; writing—review and editing, Francesco Chiti and Laura Pierucci; visualization, Sergio Cibecchini; supervision, Francesco Chiti and Laura Pierucci.
+All authors have read and agreed to the published version of the manuscript.}
+
+\funding{This research received no external funding.}
+
+%\institutionalreview{In this section, you should add the Institutional Review Board Statement and approval number, if relevant to your study.
 You might choose to exclude this statement if the study did not require ethical approval.
@@
 
-\informedconsent{Any research article describing a study involving humans should contain this statement.
+%\informedconsent{Any research article describing a study involving humans should contain this statement.
 Please add ``Informed consent was obtained from all subjects involved in the study.'' OR ``Patient consent was waived due to REASON (please provide a detailed justification).'' OR ``Not applicable'' for studies not involving humans.
@@
 
-Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
+%Written informed consent for publication must be obtained from participating patients who can be identified (including by the patients themselves).
 Please state ``Written informed consent has been obtained from the patient(s) to publish this paper'' if applicable.}
 
-\dataavailability{We encourage all authors of articles published in MDPI journals to share their research data.
-In this section, please provide details regarding where data supporting reported results can be found, including links to publicly archived datasets analyzed or generated during the study.
-Where no new data were created, or where data is unavailable due to privacy or ethical restrictions, a statement is still required.
-Suggested Data Availability Statements are available in section ``MDPI Research Data Policies'' at \url{https://www.mdpi.com/ethics}.}
-
-% Only for journal Nursing Reports
-%\publicinvolvement{Please describe how the public (patients, consumers, carers) were involved in the research.
-Consider reporting against the GRIPP2 (Guidance for Reporting Involvement of Patients and the Public) checklist.
-If the public were not involved in any aspect of the research add: ``No public involvement in any aspect of this research''.}
-
-% Only for journal Nursing Reports
-%\guidelinesstandards{Please add a statement indicating which reporting guideline was used when drafting the report.
-For example, ``This manuscript was drafted against the XXX (the full name of reporting guidelines and citation) for XXX (type of research) research''.
-A complete list of reporting guidelines can be accessed via the equator network: \url{https://www.equator-network.org/}.}
-
-% Only for journal Nursing Reports
-%\useofartificialintelligence{Please describe in detail any and all uses of artificial intelligence (AI) or AI-assisted tools used in the preparation of the manuscript.
-This may include, but is not limited to, language translation, language editing and grammar, or generating text.
-Alternatively, please state that “AI or AI-assisted tools were not used in drafting any aspect of this manuscript”.}
-
-\acknowledgments{In this section you can acknowledge any support given which is not covered by the author contribution or funding sections.
-This may include administrative and technical support, or donations in kind (e.g., materials used for experiments).}
-
-\conflictsofinterest{Declare conflicts of interest or state ``The authors declare no conflicts of interest.'' Authors must identify and declare any personal circumstances or interest that may be perceived as inappropriately influencing the representation or interpretation of reported research results.
-Any role of the funders in the design of the study; in the collection, analyses or interpretation of data; in the writing of the manuscript; or in the decision to publish the results must be declared in this section.
-If there is no role, please state ``The funders had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript; or in the decision to publish the results''.}
+\dataavailability{The dataset used in this study is openly available and provided by the authors of \cite{JammingDetectionIoT-Hussain} at the following URL: \url{https://github.com/AMHD/Jamming-Detection-in-IoT-Wireless-Networks-An-Edge-AI-Based-Approach}.
+The code for the tests and the jamming detection model developed in this study is available in the following repository: \url{https://github.com/cibecs/JammingAttacksAnomalyDetection.git}.}
+
+\acknowledgments{This work was partially supported by the European Union under the Italian National Recovery and Resilience Plan (NRRP) of NextGenerationEU, in partnership with the project “Telecommunications of the Future” (PE00000001—program “RESTART”).
+Additionally, this article publication is based upon work from COST Action CA22168 for "Physical Layer Security for Trustworthy and Resilient 6G Systems (6G-PHYSEC)," supported by COST (European Cooperation in Science and Technology).}
+
+\conflictsofinterest{The authors declare no conflicts of interest.}
 

### 2024-10-10 article.tex
Revisions pt.5

@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{%
-$^{1}$ \quad Associate Professor at Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Firenze, Italy; francesco.chiti@unifi.it, laura.pierucci@unifi.it
+\address{
+$^{1}$ \quad Associate Professor at Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Florence, Italy; francesco.chiti@unifi.it, laura.pierucci@unifi.it
 }
@@
 In this paper, we propose an unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
-The base model has been tuned to best fit the proposed scenario, but faced challenges related to environmental noise in the dataset.
-To address this, we introduced a Majority Rule module which significantly reduced the number of false positives, achieving high accuracy and precision.
+We detail the tuning of the base model as well as the intregration with a Majority Rule module which significantly reduced the number of false positives caused by environmental noise, achieving high accuracy and precision.
 Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while still correctly identifying normal traffic.
@@
 
-One of the main differences between 5G and 6G technology will be a much deeper integration with AI.
+One of the main differences between 5G and 6G technology will be a much deeper integration with Artificial Intelligence (AI).
 While Software Defined Networks (SDN) have played a key role in improving the efficiency and security
-of 5G networks, 6G is expected to take this a step further, by designing the networks to be integrated with artificial intelligence from the ground up.
-This is what the authors of \cite{6GRoadmapLetaief} define as
+of 5G networks, 6G is expected to take this a step further, by designing the networks to be integrated with AI from the ground up. This is what the authors of \cite{6GRoadmapLetaief} define as 
 the shift from \textit{Softwarization} to \textit{Intelligentization}.
@@
 We conceptualize a scenario where a drone is subject to constant and periodic jamming and has to rely on an internal AI model to detect the attack and apply the appropriate countermeasures.
-IoT devices in 6G networks
-will be equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
+
+In the future, IoT devices will be equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
 This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
@@
 	\item \textbf{System Model:} Description of the analyzed scenario, along with the dataset, algorithms, and evaluation metrics chosen for the tests.
-	\item \textbf{Model Performance:} Explanation of the testing methodology, including model tuning, testing phases, and a presentation of the obtained results.
+	\item \textbf{Model Performance:} Explanation of the testing methodology, including model tuning, testing phases, and detailed description of the performance of the model.
 	\item \textbf{Discussion:} Analysis of the results from the previous section, emphasizing the advantages of the proposed approach.
@@
 The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in a IoT drone scenario.
-The authors show that the CNN model is able to achieve a high detection rate against constant jamming attacks, but it
+The authors \cite{JammingDetectionIoT-Hussain} show that their CNN model is able to achieve a high detection rate against constant jamming attacks, but
 struggles in the classification of periodic jamming and normal traffic.
@@
 
-Security against Jamming attacks is crucial in all these applications, especially in a safety critical environment.
+Securing the communication channel against Jamming attacks is crucial in all these applications, especially in a safety critical environment.
 
@@
     \item \textbf{Periodic Jamming:} The jammer transmits a strong signal for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\).
-This cycle is repeated until the attack is stopped.
+This cycle is repeated until the attack ends.
     \item \textbf{Random Jamming:} In random jamming, the jammer is active at random intervals, jamming each transmitted packet with a probability 
-    \(p\) based on a random pattern\cite{VANETsAI-Lyamin}. 
+    \(p\) based on a random pattern \cite{VANETsAI-Lyamin}. 
     \item \textbf{Reactive Jamming:} A reactive jammer starts transmitting its jamming signal only when it senses energy in the communication channel, 
     indicating that a legitimate transmission is taking place. This type of jamming attack is more power efficient compared to other 
-    attack patterns, as it only transmits its signal when it know that it can actually disrupt the communication\cite{MLMisbehavior5GBoualouache}.
+    attack patterns, as it only transmits its signal when it know that it can actually disrupt the communication \cite{MLMisbehavior5GBoualouache}.
     \item \textbf{Smart Jamming:} A smart jammer is a more sophisticated type of jammer that is able to adapt its jamming signal to 
     maximize the disruption of the communication between the devices. Smart jammers employ a traffic analysis module, meaning they are able to modify their attack pattern based on the 
-    transmission specifics of the devices they are targeting and adapt to changes in the communication channel\cite{AntiJammingV2V-Feng}.
+    transmission specifics of the devices they are targeting and adapt to changes in the communication channel \cite{AntiJammingV2V-Feng}.
 \end{itemize}
@@
 If a jammer were able to completely block the communication between the drone and the base station, the drone would be left without any indication on how to behave and would need to activate an internal failsafe mechanism.
-This usually comes in the form of either a return to base procedure, a hover in place procedure or a land in place procedure.
+This usually comes in the form of either a \textit{return to base} procedure, a \textit{hover in place} procedure or a \textit{land in place} procedure.
 All of these approaches leave the drone in a vulnerable position, as a bad actor could potentially capture the drone and use it for malicious purposes.
 This is especially true when jamming attacks are used in combination with other types of attacks, such as spoofing attacks.
-
-One real world example is the capture of an American drone by Iran in 2011. 
-In December 2011 a Lockheed Martin \textit{RQ-170} Sentinel drone operated by the United States Air Force was flying over Iran when its operators lost control of the vehicle.
-The US government initially claimed that the drone had crashed due to a technical malfunction, but later reports revealed that the drone had been captured by the Iranian military.
-Iranian electronic warfare specialists claimed to have brought it down using a Jamming attack, that forced the drone into a return to base procedure, in combination with a  GPS spoofing attack, that made the drone land into a designated area \cite{RQ170DroneOwano}.
-After successfully capturing the drone, the Iranian government managed to reverse-engineer the drone and produce a working replica, which was then used in their military operations \cite{IranianUAVGross}.
+A jamming attack can be initiated against a drone, making it lose connection with the central server.
+The drone would be forced to start a failsafe procedure, like \textit{return to base}.
+The attacker could than employ a GPS spoofing attack to make the drone believe that the base station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
 
@@
 A collaborative edge approach would suffer from the same problems, as there is a high likelihood that the communication between the devices would be disrupted by the attack. 
-Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted, as in a jamming situation.
+Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted, as is the case in a jamming situation.
 
@@
 
-The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) and the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) or the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
 The simplest approach when
@@
 	\end{figure}
-	\unskip
-
-In our scenario, the drone will be subject to two types of jamming attacks, a constant jamming attack and a periodic jamming attack.
+
+In our scenario, the drone will be subject to two types of jamming attacks, a constant and a periodic jamming attack.
 These types of attacks can be attributed to different types of jammers.
@@
 
-When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm is required to meet.
+When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm has to meet.
 The algorithm has to be able to classify anomalous samples with a high detection rate (Recall), while at the same time
@@
 in 2008.
-Unlike traditional anomaly detection algorithms, which require the definition of a normal class, IF is able to detect anomalies without explicitly defining its characteristics.
+Unlike traditional anomaly detection algorithms, which require the definition of a normal class, IF is able to detect anomalies without explicitly defining their characteristics.
 This is achieved by leveraging the properties of anomalies themselves, i.e being rare and separated from the majority of the data points.
@@
 	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
-	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal datapoint \textbf{x1}\cite{IsolationForestLiu}.}
+	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal datapoint \textbf{x1} \cite{IsolationForestLiu}.}
 	\label{fig:IsolationForest}
@@
 
-The combination of these metrics gives us an important insight into the performance of the model.
+The combination of these metrics gives us concrete insight into the performance of the model.
 
@@
 The first phase in our testing methodology was the tuning of the model's hyperparameters.
-The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (depicted in Section \ref{EvaluationMetrics}) and then choosing the best values.
-From the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune were the following:
+The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
+Among the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune the following:
 
@@
 
-As we can see from the graph, performance increases as the estimators increase, while converging to a stable value. 
+As we can see from the graph, performance increases as the estimators increase, converging to a stable value. 
 In graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} is shown that the time required both for training and classification increases linearly with the number of estimators.
@@
 
-The tuning phase proved effective in improving the model's performance compared to the default hyperparameters,with an increase of $2.20\%$ in accuracy, $11.98\%$ in precision, and $7.64\%$ in the F1 score, while maintaining a nearly identical recall ($0.1\%$ drop).
+The tuning phase proved effective in improving the model's performance compared to the default hyperparameters,with an increase of $2\%$ in accuracy, $6\%$ in precision, and $5.1\%$ in the F1 score, while maintaining a nearly identical recall ($0.1\%$ drop).
 However, despite reaching a very high Recall score in both scenarios, the model is still too prone to false positives, as indicated by the value of the Precision metric.
@@
 	\end{figure}
-\unskip
 
@@
 
-After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (Figure\ref{fig:InputSignal}).
+After defining the value for the \textit{window\_size} parameter, we tested the model against the same input signal used for the standard tuned model (Figure \ref{fig:InputSignal}).
 The results of the model classification are shown in Figure \ref{fig:majorityRuleIsolationResults}.
@@
 The results show that the Majority Rule Model is effective in mitigating the high number of false positives that were present in the first version of the model. 
+The Majority rule integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
 Given the resource constrained nature of the scenario, we decided to test the computational impact of the Majority Rule module against the standard tuned model. 
@@
 		\includegraphics[width=\textwidth]{img/classificationTimeComparison.png}
-		\caption{Classification time comparison.}
+		\caption{}
 		\label{fig:majority_rule_classification_time}
@@
 		\includegraphics[width=\textwidth]{img/trainingTimeComparison.png}
-		\caption{Training time comparison.}
+		\caption{}
 		\label{fig:majority_rule_training_time}
 	\end{subfigure}
-	\caption{Comparison of the standard tuned model and the Majority Rule model training and classification times.}
+	\caption{Comparison of the standard tuned model and the Majority Rule in terms of classification time \textbf{(a)} and training time \textbf{(b)}.}
 	\label{fig:majority_rule_time_comparison}
@@
 The results show two significant Figures as the results provided in the compared paper were in this format.
-Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics.
+Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics and are thus not shown.
+
 Table \ref{tab:periodic_jamming_comparison} shows the comparison between the two models in the case of periodic jamming and Table \ref{tab:normal_traffic_comparison} shows the comparison between the two models in classification of normal traffic.
@@
 We compared the performance of the base Isolation Forest model against a version specifically tuned to detect jamming attacks.
-In the tuning phase, we paid particular attention to the computational added by each parameter and tried to find the balance between performance and efficiency.
+In the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the balance between performance and efficiency.
 We then proposed the integration of a Majority Rule module to reduce the number of false positives caused by the inherent noise of the dataset.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{Conceptualization, Francesco Chiti and Sergio Cibecchini; methodology, Sergio Cibecchini; software, Sergio Cibecchini; validation, Francesco Chiti and Laura Pierucci; formal analysis, Sergio Cibecchini; investigation, Sergio Cibecchini; resources, Francesco Chiti and Laura Pierucci; data curation, Sergio Cibecchini; writing—original draft preparation, Sergio Cibecchini; writing—review and editing, Francesco Chiti and Laura Pierucci; visualization, Sergio Cibecchini; supervision, Francesco Chiti and Laura Pierucci.
+\authorcontributions{Conceptualization, Francesco Chiti and Sergio Cibecchini; methodology, Sergio Cibecchini; software, Sergio Cibecchini; validation, Francesco Chiti and Laura Pierucci; writing—original draft preparation, Sergio Cibecchini; writing—review and editing, Francesco Chiti and Laura Pierucci; visualization, Sergio Cibecchini; supervision, Francesco Chiti and Laura Pierucci.
 All authors have read and agreed to the published version of the manuscript.}
@@
 
-\bibitem[Gross and TOI Staff(2024)]{IranianUAVGross}
-Gross, J.A.; TOI Staff.
-Iranian UAV that entered Israeli airspace seems to be American stealth knock-off.
-Available online: \url{https://www.timesofisrael.com/iranian-uav-that-enteredisraeli-airspace-seems-to-be-american-stealth-knock-off} (accessed on 16 May 2024).
-
 \bibitem[Chorti et al.(2022)]{6GSecurity-Chorti}

### 2024-10-13 article.tex
Revisions pt.6

@@
 However, drone networks are particularly vulnerable to Jamming attacks, a type of Availability attack that can disrupt network operation and hinder drone functionality.
-In this paper, we propose an unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
+In this paper, we propose a low complexity unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
 We detail the tuning of the base model as well as the intregration with a Majority Rule module which significantly reduced the number of false positives caused by environmental noise, achieving high accuracy and precision.
-Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while still correctly identifying normal traffic.
+Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while still correctly identifying nominal traffic.
 Finally, we discuss the potential integration of the proposed solution in 6G-enabled drone networks, as a lightweight edge-based solution for enhancing security against jamming attacks.
@@
 % Keywords
-\keyword{Jamming attacks, 6G Drone Networks, Isolation Forest, Machine Learning, Edge AI, IoT Security}
+\keyword{Jamming attacks, 6G Drone Networks, Isolation Forest, Edge AI, IoT Security}
 
@@
 Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
-
-6G technology is expected to enable a wide variety of new use cases, thanks to the increases in both data rates and latency, but this in turn 
-will also bring forth new security challenges specific to those applications.
+6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as increases in both data rates and latency.
+All of these advancements will in turn bring forth new security challenges specific to those applications.
 
@@
 of 5G networks, 6G is expected to take this a step further, by designing the networks to be integrated with AI from the ground up. This is what the authors of \cite{6GRoadmapLetaief} define as 
-the shift from \textit{Softwarization} to \textit{Intelligentization}.
-
-AI integration in 6G networks will greatly strengthen the security of the network against potential threats. 
+the shift from \textit{Softwarization} to \textit{Intelligentization}.AI integration in 6G networks will greatly strengthen the security of the network against potential threats. 
 By leveraging Diagnostic Analytics, a collection of insights into the status of the networks, security teams 
@@
 
-In this paper we will focus on a specific aspect of the security of 6G networks, namely we will provide a lightweight edge-based machine learning approach 
+In this paper we focus on a specific aspect of the security of 6G networks, namely we provide a lightweight edge-based Machine Learning approach 
 for the detection of jamming attacks in networks of drones.
-
 We conceptualize a scenario where a drone is subject to constant and periodic jamming and has to rely on an internal AI model to detect the attack and apply the appropriate countermeasures.
 
-In the future, IoT devices will be equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
+In the future, IoT devices are expected to come equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
 This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
-
 Our solution is designed to run on a resource constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
@@
 
-The paper is divided in 5 sections: 
+The paper is organized in 5 Sections: 
 \begin{enumerate}
@@
 
-This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a machine learning based approach for the detection of jamming attacks. 
+This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks. 
 The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in a IoT drone scenario.
@@
 In the military sector, the effectiveness of drones is widely recognized, both for high and low end models and are being used in a variety of roles, from more passive roles like surveillance and intelligence gathering, to more active roles like
-delivery of explosives and targeted strikes.
-
-Securing the communication channel against Jamming attacks is crucial in all these applications, especially in a safety critical environment.
+delivery of explosives and targeted strikes. Securing the communication channel against jamming attacks is crucial in all these applications, especially in a safety critical environment.
 
@@
 it is able to overwhelm the legitimate signal, effectively blocking the communication between the devices \cite{DroneCommHassija}. 
-Since the ability to communicate is affected, Jamming attacks falls under the umbrella of attacks that target the \textit{Availability} of the service in the CIA triad \cite{DataIntegrityCawthra}. 
+Since the ability to communicate is affected, jamming attacks falls under the umbrella of attacks that target the \textit{Availability} of the service in the CIA triad \cite{DataIntegrityCawthra}. 
 Jamming attacks can be classified into 5 main categories, based on the attack pattern of the jammer:
@@
     \item \textbf{Constant Jamming:} The jammer continuously transmits a strong signal on the same frequency used by the devices it wants to disrupt to communicate. 
-    \item \textbf{Periodic Jamming:} The jammer transmits a strong signal for a certain period of time \(t_a\), then stops transmitting for another period of time \(t_b\).
+    \item \textbf{Periodic Jamming:} The jammer transmits a strong signal for a certain period of time \(t_{on}\), then stops transmitting for another period of time \(t_{off}\).
 This cycle is repeated until the attack ends.
@@
     attack patterns, as it only transmits its signal when it know that it can actually disrupt the communication \cite{MLMisbehavior5GBoualouache}.
-    \item \textbf{Smart Jamming:} A smart jammer is a more sophisticated type of jammer that is able to adapt its jamming signal to 
+    \item \textbf{Smart Jamming:} A smart jammer is a more advanced and computationally intensive type of jammer that is able to adapt its jamming signal to 
     maximize the disruption of the communication between the devices. Smart jammers employ a traffic analysis module, meaning they are able to modify their attack pattern based on the 
@@
 Jamming attacks are particularly effective against drone networks, as drones usually rely on external input to navigate and operate correctly.
-If a jammer were able to completely block the communication between the drone and the base station, the drone would be left without any indication on how to behave and would need to activate an internal failsafe mechanism.
+If a jammer were able to completely block the communication between the drone and the Base Station (BS), the drone would be left without any indication on how to behave and would need to activate an internal failsafe mechanism.
 This usually comes in the form of either a \textit{return to base} procedure, a \textit{hover in place} procedure or a \textit{land in place} procedure.
@@
 The drone would be forced to start a failsafe procedure, like \textit{return to base}.
-The attacker could than employ a GPS spoofing attack to make the drone believe that the base station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
+The attacker could than employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
 
@@
 
-When presenting a Machine Learning (ML) based approach in an IoT setting, the question of where the AI model should be placed often arises.
+When presenting a ML based approach in an IoT setting, the question of where the AI model should be placed often arises.
 By their nature, IoT devices, and in turn drones, are usually resource constrained,
@@
 A centralized approach
-offloads the computational burden to a central server, that returns the results of the AI model to the device.
+offloads the computational burden to a remote central server, that returns the results of the AI model to the device.
 While this scheme might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
-communication with the server means less time to react to the attack.
-Also, as jamming attacks degrade or sometimes completely block the communication between the device and the base station, a centralized approach might not be feasible in this case.
+communication with the server reduces the time to react to the attack.
+Also, as jamming attacks degrade or sometimes completely block the communication between the device and the BS, a centralized approach might not be feasible in this case.
 A collaborative edge approach would suffer from the same problems, as there is a high likelihood that the communication between the devices would be disrupted by the attack. 
@@
 
-In the proposed scenario we have a flying drone that is subject to a jamming attack.
+In the proposed scenario (Figure \ref{fig:CombinedJammingscenariosDiagram}) we have a flying drone that is subject to a jamming attack.
 The drone communicates with a ground station and periodically samples the Received Signal Strength (RSS) of the signal it receives.
@@
 We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain instant by transmitting a high power signal on the same frequency as the one used by the drone to communicate with the ground station.
-We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning the drone has to rely on its internal classification algorithm to determine if a jamming attack is taking place and react accordingly.
+We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning that the drone has to rely on its internal classification algorithm to determine if a jamming attack is taking place and react accordingly.
 We assume that the jammer type is unknown to the drone.
 
-Figure \ref{fig:CombinedJammingscenariosDiagram} shows a diagram of the proposed scenario.
-
 \begin{figure}[H]
 	\includegraphics[width=10.5 cm]{img/CombinedJammingscenariosDiagram.jpg}
+	\centering
 	\caption{Proposed jamming scenario.
-The Drone communicates with the 6G base station and receives information about how to behave.
-The fixed jammer \textbf{(1)} and the mobile jammer \textbf{(2)} target the communication between the drone and the base station.
+The Drone communicates with the 6G BS and receives information about how to behave.
+The fixed jammer \textbf{(1)} and the mobile jammer \textbf{(2)} target the communication between the drone and the Base Station.
 The drone has an internal classification module that is able to detect jamming attacks.}
@@
 
-In our scenario, the drone will be subject to two types of jamming attacks, a constant and a periodic jamming attack.
-These types of attacks can be attributed to different types of jammers.
-The constant jamming attack could be caused by a ground jammer, as maintaining a constant jamming signal requires a large power source, while
+In our scenario, the drone is subject to two types of jamming attacks, a constant and a periodic jamming attack that can be attributed to two different types of jammers.
+The constant jamming attack could be caused by a fixed ground jammer, as maintaining a constant jamming signal requires a large power source, while
 the periodic jamming attack could be caused by a mobile jammer, for example a drone, as drones are usually battery powered and can only jam for a limited amount of time. 
@@
 
-Table \ref{tab:attacker_classification} shows the attacker classification in the proposed scenario \cite{MLMisbehavior5GBoualouache}:
+The attacker classification \cite{MLMisbehavior5GBoualouache} of the proposed scenario is detailed in Table \ref{tab:attacker_classification}:
 
@@
 The first file contains the RSS values sampled during a constant jamming attack, the second file contains the RSS values sampled during a periodic jamming attack and the third file contains the RSS values sampled during normal network operation.
-The samples are stored in a single column, with each row representing a single sampled RSS value, represented using the \textit{dBm (decibel-milliwatts)} unit of measurement.
+The samples are stored in a single column, with each row representing a single sampled RSS value, expressed in \textit{dBm (decibel-milliwatts)}.
 
@@
 
-When choosing the algorithm for the classification module, we first had to define the requirements that the algorithm has to meet.
-The algorithm has to be able to classify anomalous samples with a high detection rate (Recall), while at the same time
+When choosing the algorithm for the classification module, we first had to define the requirements that the it is required to meet.
+The algorithm has to have the ability to classify anomalous samples with a high detection rate (Recall), while at the same time
 being lightweight enough in terms of memory usage and computational power to be run on a resource constrained device like a drone.
@@
 
-The algorithm that best fit these requirements was the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
-The Isolation Forest (IF) algorithm is a state-of-the-art unsupervised machine learning algorithm for anomaly detection, introduced by Liu et al.
+The algorithm that we deemed the best fit for these requirements is the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
+The Isolation Forest (IF) algorithm is a state-of-the-art unsupervised ML algorithm for anomaly detection, introduced by Liu et al.
 in 2008.
@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
@@
 \end{itemize}
-
 The combination of these metrics gives us concrete insight into the performance of the model.
@@
 
-The first phase in our testing methodology was the tuning of the model's hyperparameters.
-The tuning was performed by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
+The first phase in our testing methodology is the tuning of the model's hyperparameters by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
 Among the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune the following:
@@
 \end{itemize} 
-
 During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (table \ref{tab:isolation_forest_parameters}).
@@
 
-The values whe chose for \textit{normal\_traffic\_size} and \textit{jamming\_size} are shown in Table \ref{tab:dataset_sizes}.
+The selected values for \textit{normal\_traffic\_size} and \textit{jamming\_size} are shown in Table \ref{tab:dataset_sizes}.
 
@@
 The dataset is intentionally unbalanced between normal data points and anomalous points, as jamming attacks are usually rare events compared to normal network operation. 
-
 In Figure \ref{fig:InputSignal} we can see a representation of the input signal in the case of a constant jamming attack.
 The proposed results, unless otherwise specified, are based on the input signal shown in Figure \ref{fig:InputSignal}, which employs constant jamming.
-Periodic jamming always showed comparable trends as constant jamming in all the performed tests.
+Periodic jamming always shown comparable trends as constant jamming in all the performed tests.
 
@@
     \end{adjustwidth}
-    \caption{Input signal in the case of Constant Jamming. The normal traffic signal is concatenated with the jamming signal.}
+    \caption{Input signal in the case of Constant jamming. The normal traffic signal is concatenated with the jamming signal.}
     \label{fig:InputSignal}
@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=10.5cm]{img/nEstimatorsTuning.png}
@@
 
-From Figure \ref{fig:max_samples_tuning} we can see that the model performance is not greatly affected by the \textit{max\_samples} parameter.
+From Figure \ref{fig:max_samples_tuning} we can notice that the model performance is not greatly affected by the \textit{max\_samples} parameter.
 This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a limited training set.
@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=10.5cm]{img/maxSamplesTuning.png}
@@
 
-The final parameter we focused on is the \textit{contamination} parameter. The tuning values are shown in Table \ref{tab:contamination_tuning}.
+The last parameter we focused on is the \textit{contamination} parameter. The tuning values are shown in Table \ref{tab:contamination_tuning}.
 
@@
 \begin{figure}[H]
+	\centering
 	\includegraphics[width=10.5cm]{img/contaminationTuning.png}
@@
 
-Our testing showed that, as expected, tuning of the contamination parameter has minimal impact on the training and classification time.
+Our testing pointed out that, as expected, tuning of the contamination parameter has minimal impact on the training and classification time.
 
@@
 
-The tuning phase proved effective in improving the model's performance compared to the default hyperparameters,with an increase of $2\%$ in accuracy, $6\%$ in precision, and $5.1\%$ in the F1 score, while maintaining a nearly identical recall ($0.1\%$ drop).
+The tuning phase proved effective in improving the model's performance compared to the default hyperparameters, with an increase of $2\%$ in accuracy, $6\%$ in precision, and $5.1\%$ in the F1 score, while maintaining a nearly identical recall ($0.1\%$ drop).
 However, despite reaching a very high Recall score in both scenarios, the model is still too prone to false positives, as indicated by the value of the Precision metric.
@@
 
-\subsubsection{Majority rule model testing} \label{sec:majorityRuleModelTesting}
-
-Having understood the nature of the problem, we decided to implement a majority rule system to reduce the number of false positives.
-The improved model would use the Tuned Isolation Forest model's results and then pass them to a Majority Rule module, as shown in Figure \ref{fig:MajorityRuleDiagram}.
-
-\begin{figure}[H]
+\subsubsection{Majority Rule model testing} \label{sec:majorityRuleModelTesting}
+
+Having understood the nature of the problem, we decided to implement a Majority Rule (MR) system to reduce the number of false positives.
+The improved model would use the Tuned Isolation Forest model's results and then pass them to a MR module, as shown in Figure \ref{fig:MajorityRuleDiagram}.
+
+\begin{figure}[H]
+	\centering
 	\includegraphics[width=12.5 cm]{img/ModulesStructure.jpg}
-	\caption{Majority Rule system diagram. The Tuned Isolation Forest model results are passed to the Majority Rule module, that then provides the final classification.}
+	\caption{Majority Rule system diagram. The Tuned Isolation Forest model results are passed to the MR module, that then provides the final classification.}
 	\label{fig:MajorityRuleDiagram}
@@
 The logic behind the Majority Rule module is simple.
-The Majority Rule takes as input the classification results of the IF model and inserts them into a sliding window.
-If the datapoint is classified by the Tuned IF as an anomaly, the Majority Rule module checks the contents of the sliding window.
+The MR takes as input the classification results of the IF model and inserts them into a sliding window.
+If the datapoint is classified by the Tuned IF as an anomaly, the MR module checks the contents of the sliding window.
 If the
@@
 \begin{table}[H]
+	\centering
 	\caption{window\_size tuning values.}\label{tab:window_size_tuning}
@@
 	\includegraphics[width=21cm]{img/MajorityRuleIsolatioForestClassification.png}
-	\caption{Classification results from the Majority Rule Isolation Forest model}\label{fig:majorityRuleIsolationResults}
+	\caption{Classification results from the MR Isolation Forest model}\label{fig:majorityRuleIsolationResults}
 	\end{adjustwidth}
@@
 
-In Tables \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the Majority Rule model.
+In Tables \ref{tab:majority_rule_confusionMatrix} and \ref{tab:majority_rule_performanceMetrics} we can see a comparison between the tuned model and the MR model.
 
@@
 The results show that the Majority Rule Model is effective in mitigating the high number of false positives that were present in the first version of the model. 
-The Majority rule integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
-Given the resource constrained nature of the scenario, we decided to test the computational impact of the Majority Rule module against the standard tuned model. 
+The MR integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
+Given the resource constrained nature of the scenario, we decided to test the computational impact of the MR module against the standard tuned model. 
 Classification times and training times were measured for both models and the results are shown in Figures \ref{fig:majority_rule_classification_time} and \ref{fig:majority_rule_training_time}.
@@
 	\end{subfigure}
-	\caption{Comparison of the standard tuned model and the Majority Rule in terms of classification time \textbf{(a)} and training time \textbf{(b)}.}
+	\caption{Comparison of the standard tuned model and the MR in terms of classification time \textbf{(a)} and training time \textbf{(b)}.}
 	\label{fig:majority_rule_time_comparison}
@@
 This is due to the additional computational complexity added by the Majority Rule module, which requires updating and checking of the sliding window for each classified datapoint.
-Figure \ref{fig:majority_rule_training_time} on the other hand shows that, as expected, training time is not affected by the Majority Rule module.
+Figure \ref{fig:majority_rule_training_time} on the other hand shows that, as expected, training time is not affected by the MR module.
 
@@
 In this article we analyzed wether it was possible to employ an Isolation Forest model to detect jamming attacks in a 6G drone scenario.
-We tuned the hyperparameters of the model and tested it against the default Isolation Forest model.
+We tuned the hyperparameters of the model and tested it against the default IF model.
 We achieved a considerable improvement in performance thanks to the tuning process (section \ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model suffered too much from a high number of false positives, caused by the inherent noise of the dataset.
-To mitigate this issue, we proposed the integration of the Isolation Forest model with a Majority Rule module (section \ref{sec:majorityRuleModelTesting}).
-The \textit{window\_size} parameter of the Majority Rule module was tuned to provide the best performance.
-The addition of the Majority Rule module proved extremely effective in reducing the number of false positives, greatly improving the model's precision.
-
-Integration of the Majority Rule module also impacted total classification time as shown in Figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the isolation forest model was preserved, meaning that the classification time complexity was kept at $O(n)$.
+To mitigate this issue, we proposed the integration of the IF model with a Majority Rule module (section \ref{sec:majorityRuleModelTesting}).
+The \textit{window\_size} parameter of the MR module was tuned to provide the best performance.
+The addition of the MR module proved extremely effective in reducing the number of false positives, greatly improving the model's precision.
+
+Integration of the MR module also impacted total classification time as shown in Figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the IF model was preserved, meaning that the classification time complexity was kept at $O(n)$.
 In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
@@
 In this article we analyzed the use of the Isolation Forest unsupervised machine learning algorithm for the detection of jamming attacks.
-We compared the performance of the base Isolation Forest model against a version specifically tuned to detect jamming attacks.
+We compared the performance of the base IF model against a version specifically tuned to detect jamming attacks.
 In the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the balance between performance and efficiency.
 We then proposed the integration of a Majority Rule module to reduce the number of false positives caused by the inherent noise of the dataset.
-The Majority Rule module was tuned to provide the best performance and proved effective in mitigating the problem of false positives, while still maintaining a linear complexity in classification time.
+The MR module was tuned to provide the best performance and proved effective in mitigating the problem of false positives, while still maintaining a linear complexity in classification time.
 We tested the model against a dataset that included normal traffic, constant jamming, and periodic jamming attacks, with an unbalanced number of normal traffic samples and jamming attack samples to better reflect a real-world scenario.
@@
 This could happen periodically or whenever there is a change in the environment caused by the drone moving to a different location.
-After tuning of the model, the drone would periodically sample incoming signals and classify them using the Majority Rule module.
-If the model detects a jamming attack, the drone could activate built in countermeasures like frequency hopping or DSSS to mitigate the effects of the attack.
+After tuning of the model, the drone would periodically sample incoming signals and classify them using the MR module.
+If the model detects a jamming attack, the drone could activate built in countermeasures like Frequency Hopping or Direct Sequence Spread Spectrum  to mitigate the effects of the attack.
 
@@
 As discussed in Section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
-Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more classification features, such as the RSV metric proposed in \cite{JammingDetectionIoT-Hussain}.
+Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more classification features, such as the RSV metric proposed in \cite{JammingDetection-Karagiannis}.
 
@@
 FPV & First Person View \\
+BS & Base Station \\
+MR & Majority Rule \\
 DOS & Denial Of Service \\
@@
 
-\bibitem[EuropeanCommission(2024)]{DronesEC}
-Unmanned aircraft (drones). Available online: \url{https://transport.ec.europa.eu/transport-modes/air/aviation-safety/unmanned-aircraft-drones_en} (accessed on 13 September 2024).
-
-\bibitem[Laricchia(2024)]{DronesStatisticsLaricchia}
-Laricchia, F. Consumer and commercial drones - statistics and facts. Available online: \url{https://www.statista.com/topics/7939/drones/\#topicOverview} (accessed on 13 September 2024).
-
-\bibitem[Sultan(2018)]{5GV2XSultan}
-Sultan, A. Study on enhancement of 3GPP support for 5G V2X services. Tech. Rep. {\em 3GPP}, 2018.
-
-\bibitem[Hassija et al.(2021)]{DroneCommHassija}
-Hassija, V.; Kumar, R.; Gupta, H.; Singh, S.; Sharma, P.
-Fast, Reliable, and Secure Drone Communication: A Comprehensive Survey.
-{\em IEEE Communications Surveys and Tutorials} {\bf 2021}, {\em 23}, 2802--2832.
-\url{https://doi.org/10.1109/COMST.2021.3097916}.
-
-\bibitem[Cawthra(2020)]{DataIntegrityCawthra}
-Cawthra, J. Data Integrity: Detecting and Responding to Ransomware and Other Destructive Events. {\em NIST Special Publication} {\bf 2020}, {\em 1800-26A}.
-
 \bibitem[Lyamin et al.(2018)]{VANETsAI-Lyamin}
@@
 \url{https://doi.org/10.1109/MNET.2018.1800074}.
-
-\bibitem[Boualouache and Engel(2023)]{MLMisbehavior5GBoualouache}
-Boualouache, A.; Engel, T.
-A Survey on Machine Learning-Based Misbehavior Detection Systems for 5G and Beyond Vehicular Networks.
-{\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
-\url{https://doi.org/10.1109/COMST.2023.3236448}.
-
-\bibitem[Feng and Haykin(2019)]{AntiJammingV2V-Feng}
-Feng, S.; Haykin, S.
-Cognitive Risk Control for Anti-Jamming V2V Communications in Autonomous Vehicle Networks.
-{\em IEEE Transactions on Vehicular Technology} {\bf 2019}, {\em 68}, 9920--9934.
-\url{https://doi.org/10.1109/TVT.2019.2935999}.
-
-\bibitem[Owano(2024)]{RQ170DroneOwano}
-Owano, N. RQ-170 drone's ambush facts spilled by Iranian engineer. Available online: \url{https://phys.org/news/2011-12-rq-drone-ambush-facts-iranian.html} (accessed on 14 September 2024).
-
-\bibitem[Chorti et al.(2022)]{6GSecurity-Chorti}
-Chorti, A.; Hollanti, C.; Koorapaty, H.; Poor, H.V.
-Context-Aware Security for 6G Wireless: The Role of Physical Layer Security.
-{\em IEEE Communications Standards Magazine} {\bf 2022}, {\em 6}, 102--108.
-https://doi.org/10.1109/MCOMSTD.0001.2000082.
-
-\bibitem[Sciancalepore et al.(2023)]{JammingDetection-Sciancalepore}
-Sciancalepore, S.; Kusters, F.; Abdelhadi, N.K.; Oligeri, G.
-Jamming Detection in Low-BER Mobile Indoor Scenarios via Deep Learning.
-{\em arXiv} {\bf 2023}, eprint: 2306.10912.
-Available online: \url{https://arxiv.org/abs/2306.10912}.
-
-\bibitem[Boualouache and Engel(2023)]{MLMisbehavior5GBoualouache}
-Boualouache, A.; Engel, T.
-A Survey on Machine Learning-Based Misbehavior Detection Systems for 5G and Beyond Vehicular Networks.
-{\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
-https://doi.org/10.1109/COMST.2023.3236448.
 
@@
 
-\bibitem[Sobot(2012)]{WirelessCommSobot}
-Sobot, R. \textit{Wireless Communication Electronics: Introduction to RF Circuits and Design}; Springer: 2012; p. 252. ISBN 9783030486303.
+\bibitem[Zuo et al.(2021)]{GPSSpoofingDetection-Zuo}
+Zuo, S.; Liu, Y.; Zhang, D.; Xin, P.; Liu, T.
+Detection of GPS Spoofing Attacks Based on Isolation Forest.
+In Proceedings of the 2021 IEEE 9th International Conference on Information, Communication and Networks (ICICN), Xi'an, China, 2021; pp.
+357--361.
+https://doi.org/10.1109/ICICN52636.2021.9673863.
+
+\bibitem[Hong et al.(2023)]{HybridJammingDetection-Hong}
+Hong, S.; Kim, K.; Lee, S.-H.
+A Hybrid Jamming Detection Algorithm for Wireless Communications: Simultaneous Classification of Known Attacks and Detection of Unknown Attacks.
+{\em IEEE Communications Letters} {\bf 2023}, {\em 27}, 1769--1773.
+https://doi.org/10.1109/LCOMM.2023.3275694.
+
+\bibitem[EuropeanCommission(2024)]{DronesEC}
+Unmanned aircraft (drones). Available online: \url{https://transport.ec.europa.eu/transport-modes/air/aviation-safety/unmanned-aircraft-drones_en} (accessed on 13 September 2024).
+
+\bibitem[Laricchia(2024)]{DronesStatisticsLaricchia}
+Laricchia, F. Consumer and commercial drones - statistics and facts. Available online: \url{https://www.statista.com/topics/7939/drones/\#topicOverview} (accessed on 13 September 2024).
+
+\bibitem[Sultan(2018)]{5GV2XSultan}
+Sultan, A. Study on enhancement of 3GPP support for 5G V2X services. Tech. Rep. {\em 3GPP}, 2018.
+
+\bibitem[Hassija et al.(2021)]{DroneCommHassija}
+Hassija, V.; Kumar, R.; Gupta, H.; Singh, S.; Sharma, P.
+Fast, Reliable, and Secure Drone Communication: A Comprehensive Survey.
+{\em IEEE Communications Surveys and Tutorials} {\bf 2021}, {\em 23}, 2802--2832.
+\url{https://doi.org/10.1109/COMST.2021.3097916}.
+
+\bibitem[Cawthra(2020)]{DataIntegrityCawthra}
+Cawthra, J. Data Integrity: Detecting and Responding to Ransomware and Other Destructive Events. {\em NIST Special Publication} {\bf 2020}, {\em 1800-26A}.
+
+\bibitem[Boualouache and Engel(2023)]{MLMisbehavior5GBoualouache}
+Boualouache, A.; Engel, T.
+A Survey on Machine Learning-Based Misbehavior Detection Systems for 5G and Beyond Vehicular Networks.
+{\em IEEE Communications Surveys and Tutorials} {\bf 2023}, {\em 25}, 1128--1172.
+\url{https://doi.org/10.1109/COMST.2023.3236448}.
+
+\bibitem[Feng and Haykin(2019)]{AntiJammingV2V-Feng}
+Feng, S.; Haykin, S.
+Cognitive Risk Control for Anti-Jamming V2V Communications in Autonomous Vehicle Networks.
+{\em IEEE Transactions on Vehicular Technology} {\bf 2019}, {\em 68}, 9920--9934.
+\url{https://doi.org/10.1109/TVT.2019.2935999}.
+
+\bibitem[Owano(2024)]{RQ170DroneOwano}
+Owano, N. RQ-170 drone's ambush facts spilled by Iranian engineer. Available online: \url{https://phys.org/news/2011-12-rq-drone-ambush-facts-iranian.html} (accessed on 14 September 2024).
+
+\bibitem[Chorti et al.(2022)]{6GSecurity-Chorti}
+Chorti, A.; Hollanti, C.; Koorapaty, H.; Poor, H.V.
+Context-Aware Security for 6G Wireless: The Role of Physical Layer Security.
+{\em IEEE Communications Standards Magazine} {\bf 2022}, {\em 6}, 102--108.
+https://doi.org/10.1109/MCOMSTD.0001.2000082.
+
+\bibitem[Sciancalepore et al.(2023)]{JammingDetection-Sciancalepore}
+Sciancalepore, S.; Kusters, F.; Abdelhadi, N.K.; Oligeri, G.
+Jamming Detection in Low-BER Mobile Indoor Scenarios via Deep Learning.
+{\em arXiv} {\bf 2023}, eprint: 2306.10912.
+Available online: \url{https://arxiv.org/abs/2306.10912}.
 
@@
 
-\bibitem[RaspberryPi(2024)]{RaspberryPi3ModelB}
-Raspberry Pi 3 Model B. Available online: \url{https://www.raspberrypi.com/products/raspberry-pi-3-model-b/} (accessed on 14 September 2024).
-
 \bibitem[Karagiannis and Argyriou(2018)]{JammingDetection-Karagiannis}
@@
 Available online: \url{https://www.sciencedirect.com/science/article/pii/S221420961730222X}.
-
-\bibitem[Hong et al.(2023)]{HybridJammingDetection-Hong}
-Hong, S.; Kim, K.; Lee, S.-H.
-A Hybrid Jamming Detection Algorithm for Wireless Communications: Simultaneous Classification of Known Attacks and Detection of Unknown Attacks.
-{\em IEEE Communications Letters} {\bf 2023}, {\em 27}, 1769--1773.
-https://doi.org/10.1109/LCOMM.2023.3275694.
-
-\bibitem[Zuo et al.(2021)]{GPSSpoofingDetection-Zuo}
-Zuo, S.; Liu, Y.; Zhang, D.; Xin, P.; Liu, T.
-Detection of GPS Spoofing Attacks Based on Isolation Forest.
-In Proceedings of the 2021 IEEE 9th International Conference on Information, Communication and Networks (ICICN), Xi'an, China, 2021; pp.
-357--361.
-https://doi.org/10.1109/ICICN52636.2021.9673863.
 

### 2024-10-16 article.tex
Revisions pt.7

@@
 % Authors, for the paper (add full first names)
-\Author{Sergio Cibecchini*\orcidA{}, Francesco Chiti $^{1}$\orcidB{} and Laura Pierucci$^{1}$\orcidC{}}
+\Author{Sergio Cibecchini*\orcidA{}, Francesco Chiti $^{1}$\orcidB{} and Laura Pierucci$^{2}$\orcidC{}}
 
@@
 % Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
-\address{
-$^{1}$ \quad Associate Professor at Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Florence, Italy; francesco.chiti@unifi.it, laura.pierucci@unifi.it
+\address {
+$^{1}$ \quad Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Florence, Italy; francesco.chiti@unifi.it\\
+$^{2}$ \quad Dipartimento di Ingegneria dell'Informazione, Università degli Studi di Firenze, Florence, Italy; laura.pierucci@unifi.it\\
 }
@@
 
-The shift from 4G to 5G has been a generational leap has revolutionized connectivity. 
+The shift from 4G to 5G has been a generational leap and has revolutionized connectivity. 
 Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
-6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as increases in both data rates and latency.
+6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as improvements in both data rates and latency.
 All of these advancements will in turn bring forth new security challenges specific to those applications.
@@
 While Software Defined Networks (SDN) have played a key role in improving the efficiency and security
-of 5G networks, 6G is expected to take this a step further, by designing the networks to be integrated with AI from the ground up. This is what the authors of \cite{6GRoadmapLetaief} define as 
-the shift from \textit{Softwarization} to \textit{Intelligentization}.AI integration in 6G networks will greatly strengthen the security of the network against potential threats. 
-By leveraging Diagnostic Analytics, a collection of insights into the status of the networks, security teams 
+of 5G networks, 6G is expected to take this a step further, with the networks being designed to be AI native from the ground up. This is what the authors of \cite{6GRoadmapLetaief} define as 
+the shift from \textit{Softwarization} to \textit{Intelligentization}.
+
+AI integration in 6G networks will greatly strengthen the security of the network against potential threats. 
+By leveraging Diagnostic Analytics, a collection of insights into the status of the network, security teams 
 will be able to train specific AI models to detect and respond to security threats in real-time.
@@
 	\item \textbf{Model Performance:} Explanation of the testing methodology, including model tuning, testing phases, and detailed description of the performance of the model.
-	\item \textbf{Discussion:} Analysis of the results from the previous section, emphasizing the advantages of the proposed approach.
+	\item \textbf{Discussion:} Analysis of the results from the previous section and the advantages of the proposed approach.
 	\item \textbf{Conclusions:} Overview of how the proposed solution applies to real-world scenarios, with a discussion on potential future research directions.
@@
 This means that complex AI models and algorithms are usually not feasible to be run on the device itself.
-A centralized approach
-offloads the computational burden to a remote central server, that returns the results of the AI model to the device.
+
+A centralized approach offloads the computational burden to a remote central server, that returns the results of the AI model to the device.
 While this scheme might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
@@
 We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain instant by transmitting a high power signal on the same frequency as the one used by the drone to communicate with the ground station.
-We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning that the drone has to rely on its internal classification algorithm to determine if a jamming attack is taking place and react accordingly.
+We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning that the drone has to rely on its internal resources to determine if a jamming attack is taking place and react accordingly.
 We assume that the jammer type is unknown to the drone.
@@
 
-When choosing the algorithm for the classification module, we first had to define the requirements that the it is required to meet.
+When choosing the algorithm for the classification module, we first had to define the requirements that it has to meet.
 The algorithm has to have the ability to classify anomalous samples with a high detection rate (Recall), while at the same time
@@
 A periodical redefinition of normal RSS values would
-limit the number of false positives caused by the drone mobility. 
+limit the number of false positives caused by drone mobility. 
 The model should be also required a small amount of storage to run effectively, as drones are usually very limited in internal memory.
@@
 In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
-The linear time complexity of the classification and low memory usage make the proposed solution suitable for a resource constrained environment such as the analyzed 6G drone scenario.
+The linear time complexity and low memory usage make the proposed solution suitable for a resource constrained environment such as the analyzed 6G drone scenario.
 

### 2024-10-17 article.tex
Revisions pt.8

@@
 In this paper, we propose a low complexity unsupervised machine learning approach for the detection of constant and periodic jamming attacks, using the Isolation Forest algorithm.
-We detail the tuning of the base model as well as the intregration with a Majority Rule module which significantly reduced the number of false positives caused by environmental noise, achieving high accuracy and precision.
+We detail the tuning of the base model as well as the integration with a Majority Rule module which significantly reduced the number of false positives caused by environmental noise, achieving high accuracy and precision.
 Our approach outperforms the standard Isolation Forest model in the detection of both constant and periodic jamming attacks, while still correctly identifying nominal traffic.
@@
 The shift from 4G to 5G has been a generational leap and has revolutionized connectivity. 
-Despite 5G being still in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
+Despite 5G still being in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
 6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as improvements in both data rates and latency.
@@
 Our solution is designed to run on a resource constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
-Despite the low resources requirements, the proposed approach is able to detect both constant and periodic jamming attacks with a high degree of accuracy, as well as correctly classify normal traffic.
+Despite the low resource requirements, the proposed approach is able to detect both constant and periodic jamming attacks with a high degree of accuracy, as well as correctly classify normal traffic.
 
@@
 
-This work build upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks. 
-The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in a IoT drone scenario.
+This work builds upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks. 
+The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in an IoT drone scenario.
 The authors \cite{JammingDetectionIoT-Hussain} show that their CNN model is able to achieve a high detection rate against constant jamming attacks, but
@@
 Everything) communication services. Among these use cases, advanced and remote driving, vehicle platooning and extended situational awareness are identified as some of the main benefits
-of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that, with the integration of artificial intelligence, 
+of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that with the integration of artificial intelligence, 
 would allow the drones to act autonomously in a coordinated manner.
@@
 This would prove useful in a variety of fields: from autonomous irrigation as well as soil and crop health assessment in agriculture, 
-delivery of life saving supplies and identification of survivors in disaster response, in the delivery sector as a more eco friendly alternative to traditional 
-delivery options and possibly in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.
-
-In the military sector, the effectiveness of drones is widely recognized, both for high and low end models and are being used in a variety of roles, from more passive roles like surveillance and intelligence gathering, to more active roles like
+delivery of life saving supplies and identification of survivors in disaster response, in the delivery sector as a more eco-friendly alternative to traditional 
+delivery options, and potentially in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.
+
+In the military sector, the effectiveness of drones is widely recognized, with both high and low end models being used in a variety of roles, from more passive roles like surveillance and intelligence gathering, to more active roles like
 delivery of explosives and targeted strikes. Securing the communication channel against jamming attacks is crucial in all these applications, especially in a safety critical environment.
@@
     indicating that a legitimate transmission is taking place. This type of jamming attack is more power efficient compared to other 
-    attack patterns, as it only transmits its signal when it know that it can actually disrupt the communication \cite{MLMisbehavior5GBoualouache}.
+    attack patterns, as it only transmits its signal when it knows that it can actually disrupt the communication \cite{MLMisbehavior5GBoualouache}.
     \item \textbf{Smart Jamming:} A smart jammer is a more advanced and computationally intensive type of jammer that is able to adapt its jamming signal to 
@@
 The drone would be forced to start a failsafe procedure, like \textit{return to base}.
-The attacker could than employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
+The attacker could then employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
 
@@
 By their nature, IoT devices, and in turn drones, are usually resource constrained,
-both in terms of computational power but also in terms of internal storage and battery capacity \cite{6GSecurity-Chorti}.
+both in terms of computational power and also in terms of internal storage and battery capacity \cite{6GSecurity-Chorti}.
 This means that complex AI models and algorithms are usually not feasible to be run on the device itself.
@@
 Also, as jamming attacks degrade or sometimes completely block the communication between the device and the BS, a centralized approach might not be feasible in this case.
-A collaborative edge approach would suffer from the same problems, as there is a high likelihood that the communication between the devices would be disrupted by the attack. 
+A collaborative edge approach faces similar issues, as the communication between the devices would likely be disrupted by the attack. 
 Implementing a lightweight on-device edge approach, on the other hand, while not as precise as a centralized approach, would provide real-time results and would be able to operate even when the communication is disrupted, as is the case in a jamming situation.
@@
 
-The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ration (SNR), the Received Signal Strength (RSS) or the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ratio (SNR), the Received Signal Strength (RSS) or the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
 The simplest approach when
@@
 The use of an AI model for jamming detection is particularly suitable for a 6G network, as the improved sensing capabilities would allow the model to train on a wide variety of diagnostic data, improving the detection rate and accuracy of the model.
-Furthermore, as the network is expected to be integrated with AI from the ground up, its likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
+Furthermore, as the network is expected to be integrated with AI from the ground up, it's likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
 
@@
 The drone communicates with a ground station and periodically samples the Received Signal Strength (RSS) of the signal it receives.
-The drone implements a simple unsupervised machine learning algorithm module, trained on nominal traffic RSS values.
-The module takes the sampled RSS values and classifies them as either normal or anomalous, making the drone able to determine wether or not a jamming attack is taking place.
+The drone implements a simple unsupervised machine learning module, trained on nominal traffic RSS values.
+The module takes the sampled RSS values and classifies them as either normal or anomalous, making the drone able to determine whether or not a jamming attack is taking place.
 
@@
 the periodic jamming attack could be caused by a mobile jammer, for example a drone, as drones are usually battery powered and can only jam for a limited amount of time. 
-Employing a periodic jamming attack could help the malicious drone preserve energy and reduce the chances of being detected.
+Employing a periodic jamming attack allows the malicious drone to preserve energy and lowers the chances of detection.
 
@@
 limit the number of false positives caused by drone mobility. 
-The model should be also required a small amount of storage to run effectively, as drones are usually very limited in internal memory.
-
-The algorithm that we deemed the best fit for these requirements is the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
+The model should also require a small amount of storage to run effectively, as drones are usually very limited in internal memory.
+
+The algorithm that we found to be the best fit for these requirements is the \textit{Isolation Forest} algorithm \cite{IsolationForestLiu}.
 The Isolation Forest (IF) algorithm is a state-of-the-art unsupervised ML algorithm for anomaly detection, introduced by Liu et al.
@@
 Unlike traditional anomaly detection algorithms, which require the definition of a normal class, IF is able to detect anomalies without explicitly defining their characteristics.
-This is achieved by leveraging the properties of anomalies themselves, i.e being rare and separated from the majority of the data points.
+This is achieved by leveraging the properties of anomalies themselves, i.e., being rare and separated from the majority of the data points.
 
@@
 The greater the number of splits, the more likely the data point is to be an anomaly.
-IF is an \textit{ensamble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
+IF is an \textit{ensemble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
 More trees mean more accuracy but also more computational power required.
@@
 	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
-	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal datapoint \textbf{x1} \cite{IsolationForestLiu}.}
+	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal data point \textbf{x1} \cite{IsolationForestLiu}.}
 	\label{fig:IsolationForest}
@@
 
-The first phase in our testing methodology is the tuning of the model's hyperparameters by making the parameters vary between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
+The first phase in our testing methodology involves tuning the model's hyperparameters by varying them between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
 Among the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune the following:
@@
 \begin{itemize}
-	\item \textbf{n\_estimators:} the number of base estimators in the ensamble, i.e the number of isolation trees used to compute the anomaly score of each datapoint. 
+	\item \textbf{n\_estimators:} the number of base estimators in the ensemble, i.e. the number of isolation trees used to compute the anomaly score of each data point. 
 	\item \textbf{max\_samples:} the max number of samples to draw from the dataset to train each tree.
@@
 
-The model was evaluated using as input normal traffic samples concatenated with jamming attack samples (see code snippet \ref{alg:dataset_concatenation}). 
+The model was evaluated using input composed of normal traffic samples concatenated with jamming attack samples (see code snippet \ref{alg:dataset_concatenation}). 
 This was done to simulate a real-world scenario where the model has to be able to correctly classify anomalous samples but also reduce the number of false positives during normal operation.
@@
 As we can see from the graph, performance increases as the estimators increase, converging to a stable value. 
-In graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} is shown that the time required both for training and classification increases linearly with the number of estimators.
+Graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} show that the time required both for training and classification increases linearly with the number of estimators.
 This means that choosing an appropriate number of estimators is crucial, as it can greatly affect the model performance.
@@
 
-However, as the model has to build bigger trees, the \textit{max\_samples} parameters has considerable influence on the training and classification time, as shown in Figure \ref{fig:max_samples_time_comparison}.
+However, as the model has to build bigger trees, the \textit{max\_samples} parameter has considerable influence on the training and classification time, as shown in Figure \ref{fig:max_samples_time_comparison}.
 Given the minimal performance differences but the impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
@@
 
-The contamination parameter is by far the one that has the most impact on the model performance, as shown in Figure \ref{fig:contamination_tuning}.
+The contamination parameter is by far the one that has the greatest impact on the model performance, as shown in Figure \ref{fig:contamination_tuning}.
 Since recall is the metric that we want to prioritize as it highlights the number of detections, we chose the value of \textbf{contamination = 0.09}.
@@
 As we see from Figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the jamming attack samples, leading the model to classify them as anomalies.
-This is most likely because of how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be effected by external noise.
-
-Instead of a impairment, we see this an improvement opportunity.
+This is most likely because of how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be affected by external noise.
+
+Instead of seeing this as an impairment, we view it as an improvement opportunity.
 The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving trough different environments and thus be subject to environmental noise.
@@
 The MR takes as input the classification results of the IF model and inserts them into a sliding window.
-If the datapoint is classified by the Tuned IF as an anomaly, the MR module checks the contents of the sliding window.
+If the data point is classified by the Tuned IF as an anomaly, the MR module checks the contents of the sliding window.
 If the
-majority of the datapoints in the window are classified as anomalies, the data point is classified as an anomaly.
-If the majority of the datapoints in the window are classified as normal, the data point is classified as normal (see code snipped \ref{alg:majority_rule}).
+majority of the data points in the window are classified as anomalies, the data point is classified as an anomaly.
+If the majority of the data points in the window are classified as normal, the data point is classified as normal (see code snipped \ref{alg:majority_rule}).
 
@@
 The results show that the Majority Rule Model is effective in mitigating the high number of false positives that were present in the first version of the model. 
-The MR integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
+The MR integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
 Given the resource constrained nature of the scenario, we decided to test the computational impact of the MR module against the standard tuned model. 
@@
 
-Graph \ref{fig:majority_rule_classification_time} shows that there is indeed a difference in classification time, with the standard model being faster.
-This is due to the additional computational complexity added by the Majority Rule module, which requires updating and checking of the sliding window for each classified datapoint.
+Figure \ref{fig:majority_rule_classification_time} shows that there is indeed a difference in classification time, with the standard model being faster.
+This is due to the additional computational complexity added by the Majority Rule module, which requires updating and checking of the sliding window for each classified data point.
 Figure \ref{fig:majority_rule_training_time} on the other hand shows that, as expected, training time is not affected by the MR module.
@@
 As mentioned in Section \ref{sec:DatasetChoice}, this work is based on the work of \cite{JammingDetectionIoT-Hussain}, where the authors proposed a solution for jamming attack detection based on CNNs.
-In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as a non reliable classification of normal traffic.
+In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as a unreliable classification of normal traffic.
 We decided to compare our solution against the solution of the authors of the dataset we used. 
 The results show two significant Figures as the results provided in the compared paper were in this format.
-Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics and are thus not shown.
+Results in the case of constant jamming were very similar, with both models scoring $1.0$ in all the metrics and are therefore not shown.
 
@@
 
-In this article we analyzed wether it was possible to employ an Isolation Forest model to detect jamming attacks in a 6G drone scenario.
+In this article we analyzed whether it was possible to employ an Isolation Forest model to detect jamming attacks in a 6G drone scenario.
 We tuned the hyperparameters of the model and tested it against the default IF model.
@@
 This could happen periodically or whenever there is a change in the environment caused by the drone moving to a different location.
-After tuning of the model, the drone would periodically sample incoming signals and classify them using the MR module.
+After tuning, the drone would periodically sample incoming signals and classify them using the MR module.
 If the model detects a jamming attack, the drone could activate built in countermeasures like Frequency Hopping or Direct Sequence Spread Spectrum  to mitigate the effects of the attack.
 
-Future research could test the model against a wider range of jamming attacks types, as well as analyze the impact of real world noise on the model performance.
-Mounting the model on an actual drone would be the best way to achieve a real-world test and would provide valuable insights into how to further improve its performance.
+Future research could explore the model's performance against a broader range of jamming attacks types and evaluate the impact of real world noise on its accuracy.
+Deploying the model on a real drone would offer opportunity for real-world tests and would provide valuable insights for further refinement.
 

### 2024-10-17 article.tex
Revisions pt.9

@@
 The shift from 4G to 5G has been a generational leap and has revolutionized connectivity. 
-Despite 5G still being in its early adoption rate at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
+Despite 5G still being in its early stages of adoption at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
 6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as improvements in both data rates and latency.
@@
 This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
-Our solution is designed to run on a resource constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
+Our solution is designed to run on a resource-constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
 Despite the low resource requirements, the proposed approach is able to detect both constant and periodic jamming attacks with a high degree of accuracy, as well as correctly classify normal traffic.
@@
 
-The authors of \cite{GPSSpoofingDetection-Zuo} propose an Isolation Forest based approach for the detection of GPS spoofing attacks, while the authors of \cite{HybridJammingDetection-Hong} successfully applied a combination of decision trees and Isolation forest to classify
+The authors of \cite{GPSSpoofingDetection-Zuo} propose an Isolation Forest based approach for the detection of GPS spoofing attacks, while the authors of \cite{HybridJammingDetection-Hong} successfully applied a combination of decision trees and Isolation Forest to classify
 and detect jamming attacks in a mobile scenario.
@@
 We also detailed the tuning of the model's hyperparameters to fit our specific scenario and compared it
-against the default model. In the tuning phase, the resource constrained nature of the scenario was a key deciding factor in the selection of the more appropriate hyperparameters.
+against the default model. In the tuning phase, the resource-constrained nature of the scenario was a key deciding factor in the selection of the more appropriate hyperparameters.
 
@@
 
-Drones, also known as Unmanned Aerial Vehicles (UAVs) are defined as \textit{all aircraft designed to fly
+Drones, also known as Unmanned Aerial Vehicles (UAVs), are defined as \textit{all aircraft designed to fly
 without a pilot on board} \cite{DronesEC}. This technology has experienced rapid growth in recent years and is expected to 
-keep growing in both the consumer sector as well as the commercial and military sectors \cite{DronesStatisticsLaricchia}.
+continue growing in both the consumer sector as well as the commercial and military sectors \cite{DronesStatisticsLaricchia}.
 
@@
 Everything) communication services. Among these use cases, advanced and remote driving, vehicle platooning and extended situational awareness are identified as some of the main benefits
-of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication, that with the integration of artificial intelligence, 
+of V2V communication. All these capabilities can be leveraged by a 6G drone network to achieve fast and reliable drone-to-drone communication that, with the integration of artificial intelligence, 
 would allow the drones to act autonomously in a coordinated manner.
@@
 This would prove useful in a variety of fields: from autonomous irrigation as well as soil and crop health assessment in agriculture, 
-delivery of life saving supplies and identification of survivors in disaster response, in the delivery sector as a more eco-friendly alternative to traditional 
+delivery of life-saving supplies and identification of survivors in disaster response, in the delivery sector as a more eco-friendly alternative to traditional 
 delivery options, and potentially in the mobility sector as a complement to traditional taxis and public transportation \cite{DroneCommHassija}.
@@
     \item \textbf{Reactive Jamming:} A reactive jammer starts transmitting its jamming signal only when it senses energy in the communication channel, 
-    indicating that a legitimate transmission is taking place. This type of jamming attack is more power efficient compared to other 
+    indicating that a legitimate transmission is taking place. This type of jamming attack is more power-efficient compared to other 
     attack patterns, as it only transmits its signal when it knows that it can actually disrupt the communication \cite{MLMisbehavior5GBoualouache}.
@@
 The drone would be forced to start a failsafe procedure, like \textit{return to base}.
-The attacker could then employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}
+The attacker could then employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}.
 
@@
 When presenting a ML based approach in an IoT setting, the question of where the AI model should be placed often arises.
-By their nature, IoT devices, and in turn drones, are usually resource constrained,
+By their nature, IoT devices, and in turn drones, are usually resource-constrained,
 both in terms of computational power and also in terms of internal storage and battery capacity \cite{6GSecurity-Chorti}.
@@
 
-The state of the art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ratio (SNR), the Received Signal Strength (RSS) or the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
+The state-of-the-art approaches for jamming detection involve monitoring of the communication link and the analysis of metrics such as the Signal to Noise Ratio (SNR), the Received Signal Strength (RSS) or the Packet Delivery Ratio (PDR) \cite{JammingDetection-Sciancalepore}.
 The simplest approach when
@@
 
-Once an attack is successfully detected, state of the art jamming mitigation techniques, like Direct Sequence Spread Spectrum (DSSS), Frequency Hopping (FHSS) and advanced signal processing techniques can be put in place to mitigate the
+Once an attack is successfully detected, state-of-the-art jamming mitigation techniques, like Direct Sequence Spread Spectrum (DSSS), Frequency Hopping (FHSS) and advanced signal processing techniques can be put in place to mitigate the
 effects of the attack.
@@
 The use of an AI model for jamming detection is particularly suitable for a 6G network, as the improved sensing capabilities would allow the model to train on a wide variety of diagnostic data, improving the detection rate and accuracy of the model.
-Furthermore, as the network is expected to be integrated with AI from the ground up, it's likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
+Furthermore, as the network is expected to be integrated with AI from the ground up, it is likely that in the future drones will be equipped with AI-specific chips for a more efficient execution of AI models.
 
@@
 
-We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain instant by transmitting a high power signal on the same frequency as the one used by the drone to communicate with the ground station.
+We assume that a jammer is deployed in the network and that it starts a jamming attack at a certain instant by transmitting a high-power signal on the same frequency as the one used by the drone to communicate with the ground station.
 We assume that the jammer is able to completely block the communication between the drone and the ground station, meaning that the drone has to rely on its internal resources to determine if a jamming attack is taking place and react accordingly.
@@
 The fixed jammer \textbf{(1)} and the mobile jammer \textbf{(2)} target the communication between the drone and the Base Station.
-The drone has an internal classification module that is able to detect jamming attacks.}
+The drone has an internal classification module capable of detecting jamming attacks.}
 	\label{fig:CombinedJammingscenariosDiagram}
@@
 As 6G network traffic is not yet widely available, we chose an open-source dataset \cite{JammingDetectionIoT-Hussain} that analyses the RSS values 
-received by a Raspberry Pi 3 that is subject to periodic and constant jamming attacks.
+received by a Raspberry Pi 3 which is subject to periodic and constant jamming attacks.
 
 The dataset in \cite{JammingDetectionIoT-Hussain} was created using a software-defined radio (SDR) connected to a laptop that was programmed to transmit a jamming signal using the 
-open source software \textit{GNU Radio}.
+open-source software \textit{GNU Radio}.
 A second SDR radio was connected to a Raspberry Pi 3, designated to receive the jamming signal.
-The jamming radio operates at a frequency of $2.412 GHz$ with a Bandwidth of $40MHz$, while the Raspberry Pi 3 was programmed to sample the RSS values with a frequency of $32K$ samples per second.
-
-The dataset contains 3 different \textit{.txt} files that store the RSS values sampled by the Raspberry Pi 3.
+The jamming radio operates at a frequency of $2.412 GHz$ with a bandwidth of $40MHz$, while the Raspberry Pi 3 was programmed to sample the RSS values with a frequency of $32K$ samples per second.
+
+The dataset contains three different \textit{.txt} files that store the RSS values sampled by the Raspberry Pi 3.
 The first file contains the RSS values sampled during a constant jamming attack, the second file contains the RSS values sampled during a periodic jamming attack and the third file contains the RSS values sampled during normal network operation.
@@
 
-Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show respectively plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack, while Figure \ref{fig:normalSignal} shows the RSS values sampled during normal network operation.
+Figures \ref{fig:ConstantJammingSignal} and \ref{fig:PeriodicJammingSignal} show, respectively, plots of the RSS values sampled during a constant jamming attack and a periodic jamming attack, while Figure \ref{fig:normalSignal} shows the RSS values sampled during normal network operation.
 
@@
 The algorithm has to have the ability to classify anomalous samples with a high detection rate (Recall), while at the same time
-being lightweight enough in terms of memory usage and computational power to be run on a resource constrained device like a drone.
+being lightweight enough in terms of memory usage and computational power to be run on a resource-constrained device like a drone.
 The training phase should also be fast, as this would allow the drone to quickly determine the normal transmission RSS values in a constantly changing environment.
-A periodical redefinition of normal RSS values would
+A periodic redefinition of normal RSS values would
 limit the number of false positives caused by drone mobility. 
@@
 IF is an \textit{ensemble} algorithm, meaning that the final anomaly score is calculated by averaging the anomaly scores of all the trees in the forest.
-More trees mean more accuracy but also more computational power required.
+More trees result in greater accuracy but also more computational power required.
 
@@
 	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
-	\caption{Isolation forest in action. The anomaly \textbf{x0} is isolated in less splits compared to the normal data point \textbf{x1} \cite{IsolationForestLiu}.}
+	\caption{Isolation Forest in action. The anomaly \textbf{x0} is isolated in fewer splits compared to the normal data point \textbf{x1} \cite{IsolationForestLiu}.}
 	\label{fig:IsolationForest}
@@
 \begin{itemize}
-	\item \textbf{n\_estimators:} the number of base estimators in the ensemble, i.e. the number of isolation trees used to compute the anomaly score of each data point. 
+	\item \textbf{n\_estimators:} the number of base estimators in the ensemble, i.e., the number of isolation trees used to compute the anomaly score of each data point. 
 	\item \textbf{max\_samples:} the max number of samples to draw from the dataset to train each tree.
@@
 \end{itemize} 
-During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (table \ref{tab:isolation_forest_parameters}).
+During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (Table\ref{tab:isolation_forest_parameters}).
 
@@
 	\midrule
-	normal\_traffic\_size & 20000 \\
-	jamming\_size & 2000 \\
+	normal\_traffic\_size & 20,000 \\
+	jamming\_size & 2,000 \\
 	\bottomrule
@@
 The proposed results, unless otherwise specified, are based on the input signal shown in Figure \ref{fig:InputSignal}, which employs constant jamming.
-Periodic jamming always shown comparable trends as constant jamming in all the performed tests.
+Periodic jamming has always shown comparable trends as constant jamming in all the performed tests.
 
@@
 
-As we can see from the graph, performance increases as the estimators increase, converging to a stable value. 
+As we can see from the graph, performance increases as the number of estimators increase, converging to a stable value. 
 Graphs \ref{fig:n_estimators_training_time} and \ref{fig:n_estimators_classification_time} show that the time required both for training and classification increases linearly with the number of estimators.
@@
 From Figure \ref{fig:max_samples_tuning} we can notice that the model performance is not greatly affected by the \textit{max\_samples} parameter.
-This is most likely due to the great difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a limited training set.
+This is most likely due to the significant difference in RSS values between the normal traffic samples and the jamming attack samples, meaning the model can develop the ability to correctly classify the input even with a limited training set.
 
@@
 
-\subsubsection{Standard model testing}\label{sec:standardModelTesting}
+\subsubsection{Standard Model Testing}\label{sec:standardModelTesting}
 
@@
 As we see from Figure \ref{fig:standardIsolationResults}, many of the normal traffic samples have RSS values that are similar to the jamming attack samples, leading the model to classify them as anomalies.
-This is most likely because of how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be affected by external noise.
+This is most likely due to how the dataset has been created, as the normal traffic samples were measured in a real-world scenario where the RSS values would be affected by external noise.
 
 Instead of seeing this as an impairment, we view it as an improvement opportunity.
-The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving trough different environments and thus be subject to environmental noise.
+The fact that the dataset contains noise means it is more representative of a real-world scenario, where the drone might be moving through different environments and thus be subject to environmental noise.
 
@@
 	\includegraphics[width=12.5 cm]{img/ModulesStructure.jpg}
-	\caption{Majority Rule system diagram. The Tuned Isolation Forest model results are passed to the MR module, that then provides the final classification.}
+	\caption{Majority Rule system diagram. The Tuned Isolation Forest model results are passed to the MR module, which then provides the final classification.}
 	\label{fig:MajorityRuleDiagram}
@@
 majority of the data points in the window are classified as anomalies, the data point is classified as an anomaly.
-If the majority of the data points in the window are classified as normal, the data point is classified as normal (see code snipped \ref{alg:majority_rule}).
+If the majority of the data points in the window are classified as normal, then the data point is classified as normal (see code snipped \ref{alg:majority_rule}).
 
@@
 To determine the optimal value for the \textit{window\_size} parameter, we test the model in the same way as in the hyperparameters tuning phase.
-The model parameters were set to the best performing values from the tuning phase (table \ref{tab:best_hyperparameters}).
+The model parameters were set to the best performing values from the tuning phase (Table \ref{tab:best_hyperparameters}).
 Table \ref{tab:window_size_tuning} shows the tuning values for the \textit{window\_size} parameter.
@@
 The MR integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
-Given the resource constrained nature of the scenario, we decided to test the computational impact of the MR module against the standard tuned model. 
+Given the resource-constrained nature of the scenario, we decided to test the computational impact of the MR module against the standard tuned model. 
 Classification times and training times were measured for both models and the results are shown in Figures \ref{fig:majority_rule_classification_time} and \ref{fig:majority_rule_training_time}.
@@
 As mentioned in Section \ref{sec:DatasetChoice}, this work is based on the work of \cite{JammingDetectionIoT-Hussain}, where the authors proposed a solution for jamming attack detection based on CNNs.
-In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as a unreliable classification of normal traffic.
+In their paper, one of the drawbacks that the authors cite with their solution is the low detection rate against periodic jamming, as well as an unreliable classification of normal traffic.
 We decided to compare our solution against the solution of the authors of the dataset we used. 
@@
 
-In Figures \ref{fig:periodicJammingClassification} and \ref{fig:normalTrafficClassification} we can see the classification results of our proposed solution in the case of a testing sample size of $10000$ samples.
+In Figures \ref{fig:periodicJammingClassification} and \ref{fig:normalTrafficClassification} we can see the classification results of our proposed solution in the case of a testing sample size of $10,000$ samples.
 
@@
 We tuned the hyperparameters of the model and tested it against the default IF model.
-We achieved a considerable improvement in performance thanks to the tuning process (section \ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model suffered too much from a high number of false positives, caused by the inherent noise of the dataset.
-To mitigate this issue, we proposed the integration of the IF model with a Majority Rule module (section \ref{sec:majorityRuleModelTesting}).
+We achieved a considerable improvement in performance thanks to the tuning process (Section\ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model experienced a high number of false positives, caused by the inherent noise of the dataset.
+To mitigate this issue, we proposed the integration of the IF model with a Majority Rule module (Section\ref{sec:majorityRuleModelTesting}).
 The \textit{window\_size} parameter of the MR module was tuned to provide the best performance.
@@
 Integration of the MR module also impacted total classification time as shown in Figure \ref{fig:majority_rule_classification_time}, but the linear trend \cite{IsolationForestLiu} that we expected from the IF model was preserved, meaning that the classification time complexity was kept at $O(n)$.
-In our opinion the trade-off between the increased classification time and the improved performance is worth it, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
-The linear time complexity and low memory usage make the proposed solution suitable for a resource constrained environment such as the analyzed 6G drone scenario.
+In our opinion, the trade-off between the increased classification time and the improved performance is justified, as the model is now much more reliable in a real-world scenario, where noise from the surrounding environment is almost always present.
+The linear time complexity and low memory usage make the proposed solution suitable for a resource-constrained environment such as the analyzed 6G drone scenario.
 
 As shown in Section \ref{sec:comparisonAgainstExistingSolution}, the proposed solution outperformed the solution proposed by \cite{JammingDetectionIoT-Hussain} in both the detection of periodic jamming and the classification of normal traffic, while achieving the same performance against constant jamming attacks.
-We believe that the importance of correct classification of normal traffic is often underestimated, as a high number of false positives can lead to the activation of resource intensive countermeasures, even at times when they are not needed.
+We believe that the importance of correct classification of normal traffic is often underestimated, as a high number of false positives can lead to the activation of resource-intensive countermeasures, even at times when they are not needed.
 
@@
 We compared the performance of the base IF model against a version specifically tuned to detect jamming attacks.
-In the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the balance between performance and efficiency.
+During the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the balance between performance and efficiency.
 We then proposed the integration of a Majority Rule module to reduce the number of false positives caused by the inherent noise of the dataset.
@@
 After tuning, the drone would periodically sample incoming signals and classify them using the MR module.
-If the model detects a jamming attack, the drone could activate built in countermeasures like Frequency Hopping or Direct Sequence Spread Spectrum  to mitigate the effects of the attack.
+If the model detects a jamming attack, the drone could activate built-in countermeasures like Frequency Hopping or Direct Sequence Spread Spectrum  to mitigate the effects of the attack.
 
 Future research could explore the model's performance against a broader range of jamming attacks types and evaluate the impact of real world noise on its accuracy.
-Deploying the model on a real drone would offer opportunity for real-world tests and would provide valuable insights for further refinement.
-
-As discussed in Section \ref{sec:DetectionMitigation} devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
-Thanks to the properties of the Isolation Forest to work on high dimensional data, the model could be easily expanded to include more classification features, such as the RSV metric proposed in \cite{JammingDetection-Karagiannis}.
+Deploying the model on a real drone would provide opportunity for real-world testing and valuable insights for further refinement.
+
+As discussed in Section \ref{sec:DetectionMitigation}, devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
+Thanks to the ability of the Isolation Forest to work on high dimensional data, the model could easily be expanded to include more classification features, which would improve its situational awareness and performance.
 
@@
 
-\bibitem[Karagiannis and Argyriou(2018)]{JammingDetection-Karagiannis}
-Karagiannis, D.; Argyriou, A.
-Jamming attack detection in a pair of RF communicating vehicles using unsupervised machine learning.
-{\em Vehicular Communications} {\bf 2018}, {\em 13}, 56--63.
-https://doi.org/10.1016/j.vehcom.2018.05.001.
-Available online: \url{https://www.sciencedirect.com/science/article/pii/S221420961730222X}.
-
 \end{thebibliography}

### 2024-10-17 article.tex
Revisions pt.10

@@
 
-The paper is organized in 5 Sections: 
+The paper is organized in five Sections: 
 \begin{enumerate}
@@
 The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in an IoT drone scenario.
-The authors \cite{JammingDetectionIoT-Hussain} show that their CNN model is able to achieve a high detection rate against constant jamming attacks, but
+The authors of \cite{JammingDetectionIoT-Hussain} show that their CNN model is able to achieve a high detection rate against constant jamming attacks, but
 struggles in the classification of periodic jamming and normal traffic.
@@
 Our solution also leverages the Isolation Forest algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset created by \cite{JammingDetectionIoT-Hussain}.
-We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve the resistance of the model to environmental noise.
-Our approach reached a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
-We also detailed the tuning of the model's hyperparameters to fit our specific scenario and compared it
+We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve resistance against environmental noise.
+Our approach reaches a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
+We also detail the tuning of the model's hyperparameters to fit our specific scenario and compare it
 against the default model. In the tuning phase, the resource-constrained nature of the scenario was a key deciding factor in the selection of the more appropriate hyperparameters.
@@
 
-In technical report 22.886 \cite{5GV2XSultan} 3GPP identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
+In technical report 22.886 \cite{5GV2XSultan}, 3GPP identifies some of the envisioned use cases for 5G V2X (Vehicle-to-
 Everything) communication services. Among these use cases, advanced and remote driving, vehicle platooning and extended situational awareness are identified as some of the main benefits
@@
 The drone would be forced to start a failsafe procedure, like \textit{return to base}.
-The attacker could then employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in the spot designated by the attacker \cite{RQ170DroneOwano}.
+The attacker could then employ a GPS spoofing attack to make the drone believe that the Base Station is in a different location, leading to the drone landing in a spot designated by the attacker \cite{RQ170DroneOwano}.
 
@@
 A centralized approach offloads the computational burden to a remote central server, that returns the results of the AI model to the device.
-While this scheme might be favorable in some cases, in a real-time situation such as a jamming attack, the latency introduced by the
-communication with the server reduces the time to react to the attack.
+While this scheme might be favorable in some cases, in a real-time situation, such as a jamming attack, the latency introduced by the
+communication with the server reduces the time to react to the threat.
 Also, as jamming attacks degrade or sometimes completely block the communication between the device and the BS, a centralized approach might not be feasible in this case.
@@
 \end{itemize} 
-During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (Table\ref{tab:isolation_forest_parameters}).
+During the tuning phase, the untested hyperparameters were set to the default values of the \textit{Scikit-learn} implementation of the Isolation Forest (Table \ref{tab:isolation_forest_parameters}).
 
@@
 However, as the model has to build bigger trees, the \textit{max\_samples} parameter has considerable influence on the training and classification time, as shown in Figure \ref{fig:max_samples_time_comparison}.
-Given the minimal performance differences but the impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
+Given the minimal performance differences but substantial impact on the time metrics, we chose the value of \textbf{max\_samples = 10}.
 
@@
 We tuned the hyperparameters of the model and tested it against the default IF model.
-We achieved a considerable improvement in performance thanks to the tuning process (Section\ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model experienced a high number of false positives, caused by the inherent noise of the dataset.
-To mitigate this issue, we proposed the integration of the IF model with a Majority Rule module (Section\ref{sec:majorityRuleModelTesting}).
+We achieved a considerable improvement in performance thanks to the tuning process (Section \ref{sec:standardModelTesting}), but despite the high recall and accuracy scores, the model experienced a high number of false positives, caused by the inherent noise of the dataset.
+To mitigate this issue, we proposed the integration of the IF model with a Majority Rule module (Section \ref{sec:majorityRuleModelTesting}).
 The \textit{window\_size} parameter of the MR module was tuned to provide the best performance.
@@
 We compared the performance of the base IF model against a version specifically tuned to detect jamming attacks.
-During the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the balance between performance and efficiency.
+During the tuning phase, we paid particular attention to the computational impact of each parameter and tried to find the right balance between performance and efficiency.
 We then proposed the integration of a Majority Rule module to reduce the number of false positives caused by the inherent noise of the dataset.
@@
 This could happen periodically or whenever there is a change in the environment caused by the drone moving to a different location.
-After tuning, the drone would periodically sample incoming signals and classify them using the MR module.
+After the tuning phase, the drone would periodically sample incoming signals and classify them using the MR-integrated IF.
 If the model detects a jamming attack, the drone could activate built-in countermeasures like Frequency Hopping or Direct Sequence Spread Spectrum  to mitigate the effects of the attack.
@@
 Future research could explore the model's performance against a broader range of jamming attacks types and evaluate the impact of real world noise on its accuracy.
-Deploying the model on a real drone would provide opportunity for real-world testing and valuable insights for further refinement.
+Deploying the model on a drone would provide opportunity for real-world testing and valuable insights for further refinement.
 

### 2024-11-21 article.tex
Updated correspondence
Edited bibliography to include urls
Fixed table
Addressed Q2.3

@@
 % Contact information of the corresponding author
-\corres{Correspondence: sergio.cibecchini@gmail.com}
+\corres{Correspondence: sergio.cibecchini@edu.unifi.it}
 
@@
 From Figure \ref{fig:window_size_tuning} we can see that the \textit{window\_size} parameter has a considerable impact on the model performance. 
-The optimal value for the \textit{window\_size} parameter was found to be \textbf{window\_size = 39}.
-
 \begin{figure}[H]
@@
 \end{figure}
+
+While accuracy and precision benefit from a larger window size, we can observe a linear decrease in recall as the window size increases.
+This is due to the nature of the majority rule, as a larger window size means that a larger number of anomalous data points must be present in the window in order to classify the current data point as an anomaly.
+The optimal value for the \textit{window\_size} parameter was found to be \textbf{window\_size = 39}, as it provides high accuracy and precision while maintaining a high recall.
 
@@
 	\midrule
-	\textbf{Accuracy}  & 0.98 & N.D \\
+	\textbf{Accuracy}  & 0.98 & 0.72 \\
 	\textbf{Precision} & 0.99 & 0.73 \\
@@
 	\midrule
-	\textbf{Accuracy}  & 1.00 & N.D \\
+	\textbf{Accuracy}  & 1.00 & 0.87 \\
 	\textbf{Precision} & 1.00 & 0.80 \\
@@
 ISBN: 9781450396653.
-https://doi.org/10.1145/3567445.3567456.
+\url{https://doi.org/10.1145/3567445.3567456}.
 
@@
 357--361.
-https://doi.org/10.1109/ICICN52636.2021.9673863.
+\url{https://doi.org/10.1109/ICICN52636.2021.9673863}.
 
@@
 {\em IEEE Communications Letters} {\bf 2023}, {\em 27}, 1769--1773.
-https://doi.org/10.1109/LCOMM.2023.3275694.
+\url{https://doi.org/10.1109/LCOMM.2023.3275694}.
 
@@
 413--422.
-https://doi.org/10.1109/ICDM.2008.17.
+\url{https://doi.org/10.1109/ICDM.2008.17}.
 

### 2024-11-21 article.tex
Addressed concerns about the captions of the figures

@@
 	\includegraphics[width=10.5cm]{img/nEstimatorsTuning.png}
-	\caption{n\_estimators tuning results.}\label{fig:n_estimators_tuning}
+	\caption{n\_estimators tuning results. Performance of the model increases with an increasing number of estimators}\label{fig:n_estimators_tuning}
 \end{figure}
@@
     \end{subfigure}
-    \caption{Comparison of n\_estimators training and classification times.}
+    \caption{Comparison of n\_estimators training and classification times. Both training and classification times increase linearly with the number of estimators.}
     \label{fig:estimators_time_comparison}
@@
 	\includegraphics[width=10.5cm]{img/maxSamplesTuning.png}
-	\caption{max\_samples tuning results.}\label{fig:max_samples_tuning}
+	\caption{max\_samples tuning results.
+The max samples parameter has limited impact on the model's performance given the large difference in RSS values between normal and anomalous samples.}\label{fig:max_samples_tuning}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{Comparison of max\_samples training and classification times.}
+	\caption{Comparison of max\_samples training and classification times. Both training and classification times follow a logarithmic trend.}
 	\label{fig:max_samples_time_comparison}
@@
 	\includegraphics[width=10.5cm]{img/contaminationTuning.png}
-	\caption{contamination tuning results.}\label{fig:contamination_tuning}
+	\caption{contamination tuning results.
+While recall score benefits from a higher contamination, all the other metrics are negatively impacted by a higher contamination value.}\label{fig:contamination_tuning}
 \end{figure}
@@
 	\end{adjustwidth}
-	\caption{Classification results from the tuned Isolation Forest model}\label{fig:standardIsolationResults}
+	\caption{Classification results from the tuned Isolation Forest model.}\label{fig:standardIsolationResults}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{Confusion Matrix for the default Isolation Forest model \textbf{(a)} and the tuned Isolation Forest model \textbf{(b)}.}
+	\caption{Confusion Matrix for the default Isolation Forest model \textbf{(a)} and the tuned Isolation Forest model \textbf{(b)}.
+The tuned version reduces false positives while suffering a minimal loss in true positives.}
 	\label{fig:ConfusionMatrixStandardTunedIF}
@@
 	\includegraphics[width=10.5cm]{img/WindowSizeTuning.png}
-	\caption{window\_size tuning results.}\label{fig:window_size_tuning}
+	\caption{window\_size tuning results. Most metrics initially benefit from a larger window size except for recall that suffers a linear decrease.}\label{fig:window_size_tuning}
 \end{figure}
@@
 	\end{subfigure}
-	\caption{Confusion Matrix for the tuned Isolation Forest model \textbf{(a)} and the Majority Rule Isolation Forest model \textbf{(b)}.}
+	\caption{Confusion Matrix for the tuned Isolation Forest model \textbf{(a)} and the Majority Rule Isolation Forest model \textbf{(b)}.
+The MR model greatly reduces false positives while maintaining a rate of true positives of over 99\%.}
 	\label{fig:ConfusionMatrixTunedMajorityIF}
@@
 	\end{subfigure}
-	\caption{Classification results of the proposed solution.}
+	\caption{Classification results of the proposed solution. The model is able to correctly classify periodic jamming and normal traffic with high accuracy.}
 	\label{fig:proposedSolutionClassification}

### 2024-11-21 article.tex
Addressed Q2.4

@@
 The MR integration resulted in an improvement in Precision of $42.6\%$, in Accuracy of $6.9\%$ and in F1 Score of $27.1\%$, while suffering only a less than $1\%$ drop in Recall.
+In the original model, most of the false positives occurred due to the normal traffic samples containing a high number of isolated data points with similar RSS values to those of the jamming samples. 
+The MR module addresses this by checking if the previous points were also classified as anomalies. This approach proves to be effective, as jamming attacks are rarely composed of isolated data points.
+
 Given the resource-constrained nature of the scenario, we decided to test the computational impact of the MR module against the standard tuned model. 

### 2024-11-21 article.tex
Addressed 3.3

@@
 This could happen periodically or whenever there is a change in the environment caused by the drone moving to a different location.
+The dynamic tuning of the model would ensure that the parameters of the model are always optimized for the current environment, providing the best possible performance.
 After the tuning phase, the drone would periodically sample incoming signals and classify them using the MR-integrated IF.
@@
 
-Future research could explore the model's performance against a broader range of jamming attacks types and evaluate the impact of real world noise on its accuracy.
+Future research could explore the model's performance against a broader range of jamming attacks types, including smart, reactive and random jamming, and evaluate the impact of real world noise on its accuracy.
 Deploying the model on a drone would provide opportunity for real-world testing and valuable insights for further refinement.

### 2024-11-23 article.tex
Added further reasoning behind algorithm selection and removed copyrighted image

@@
 
+The authors of \cite{JammingDetectionML-Arjoune} analyze a wide range of supervised Machine Learning approaches for the detection of Jamming attacks, including Random Forest, Support Vector Machines and Neural Networks.
+The authors show that Random Forests were able to achieve a high detection of jamming attacks.
+The authors of \cite{JammingDetectionRF-Karagiannis} on the other hand, propose the use of an unsupervised approach in the context of VANETs and test its performance in a variety of real-world scenarios.
+
 This work builds upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks. 
@@
 
+We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve resistance against environmental noise.
+Our solution leverages the IF algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset created by \cite{JammingDetectionIoT-Hussain}.
+
+Isolation forest has been successfully applied in a variety of scenarios for the detection of anomalies.
 The authors of \cite{GPSSpoofingDetection-Zuo} propose an Isolation Forest based approach for the detection of GPS spoofing attacks, while the authors of \cite{HybridJammingDetection-Hong} successfully applied a combination of decision trees and Isolation Forest to classify
@@
 
-Our solution also leverages the Isolation Forest algorithm for jamming detection in the scenario of a 6G drone network, testing the model against the dataset created by \cite{JammingDetectionIoT-Hussain}.
-We propose a lightweight approach that integrates a specifically tuned Isolation Forest with a Majority Rule module to reduce the number of false positives and improve resistance against environmental noise.
+We decided on the Isolation Forest algorithm for its low computational and memory requirements and good performance in the detection of anomalies.
 Our approach reaches a high detection rate against both constant and periodic jamming attacks, while also being able to classify normal traffic with a high degree of accuracy.
@@
 left and right branches of the tree.
-The process is repeated recursively until all the data points are isolated, as shown in Figure \ref{fig:IsolationForest}.
+The process is repeated recursively until all the data points are isolated.
 The height of a node, meaning the number of splits required to isolate it, is used to determine the anomaly score of the data point.
@@
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=6 cm]{img/IsolationForest.jpg}
-	\caption{Isolation Forest in action. The anomaly \textbf{x0} is isolated in fewer splits compared to the normal data point \textbf{x1} \cite{IsolationForestLiu}.}
-	\label{fig:IsolationForest}
-\end{figure}   
-\unskip
+The algorithm was chosen for its simplicity, low computational requirements (both in terms of memory and computational power) and proven effectiveness in the detection of anomalies\cite{IsolationForestLiu}.
+While more complex solutions like Neural Networks or Support Vector Machines might prove more effective in certain scenarios, they are best suited in a situation where computation power is not a limiting factor.
+The unsupervised nature of the algorithm was also a determining factor in its selection, as it would allow for a periodical redefinition of the normal RSS values based on the current environment, without the need to rely on a fixed labeled dataset.
+Also, thanks to the ability to work on high dimensional data, the algorithm could potentially be scaled to work with more complex datasets in the future, if the drones were to be equipped with more advanced sensors.
 
@@
 
+\bibitem[Arjoune et al.(2020)]{JammingDetectionML-Arjoune}
+Arjoune, Y.; Salahdine, F.; Islam, M.S.; Ghribi, E.; Kaabouch, N.
+A Novel Jamming Attacks Detection Approach Based on Machine Learning for Wireless Communication.
+In Proceedings of the 2020 International Conference on Information Networking (ICOIN), Barcelona, Spain, 2020; pp.
+459--464.
+https://doi.org/10.1109/ICOIN48656.2020.9016462.
+
+\bibitem[Karagiannis and Argyriou(2018)]{JammingDetectionRF-Karagiannis}
+Karagiannis, D.; Argyriou, A.
+Jamming attack detection in a pair of RF communicating vehicles using unsupervised machine learning.
+{\em Vehicular Communications} {\bf 2018}, {\em 13}, 56--63.
+https://doi.org/10.1016/j.vehcom.2018.05.001.
+Available online: \url{https://www.sciencedirect.com/science/article/pii/S221420961730222X}.
+
 \bibitem[Hussain et al.(2023)]{JammingDetectionIoT-Hussain}

### 2024-11-23 article.tex
Edited related works sections and added comparison table

@@
 
+The authors of \cite{JammingDetectionDrones-Greco} compare the use of Multi-Layer Perceptrons (MLPs) and Decision Trees for the detection of jamming attacks in drone networks, showing that both methods are able to achieve good detection performance.
+
 This work builds upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks. 
@@
 and detect jamming attacks in a mobile scenario.
+
+Table \ref{tab:method_comparison} shows a summary of the detailed approaches for jamming detection in scientific literature.
+
+\begin{table}[H]
+    \caption{Existing approaches for jamming detection in scientific literature\label{tab:method_comparison}}
+    \newcolumntype{C}{>{\centering\arraybackslash}X}
+    \begin{tabularx}{\textwidth}{CCCC}
+    \toprule
+    \textbf{Reference} & \textbf{Data Source} & \textbf{Method} & \textbf{Metrics} \\
+    \midrule
+    \cite{JammingDetectionML-Arjoune} & Simulation & Random Forest & BPR, PDR, RSS, CCA \\
+    \cite{JammingDetectionIoT-Hussain} & Real data & CNN & RSS \\
+    \cite{JammingDetectionML-Arjoune} & Simulation & Linear SVM & BPR, PDR, RSS, CCA \\
+    \cite{HybridJammingDetection-Hong} & Real data & DT + IF & PDR, BPR, SNR, RSSI \\
+    \cite{JammingDetectionDrones-Greco} & Real + Simulated data & DT + MLP & Throughput, PDR, RSSI \\
+    Our solution & Real data & IF & RSS \\
+    \bottomrule
+    \end{tabularx}
+\end{table}
 
@@
 
+\bibitem[Greco et al.(2021)]{JammingDetectionDrones-Greco}
+Greco, C.; Pace, P.; Basagni, S.; Fortino, G.
+Jamming detection at the edge of drone networks using Multi-layer Perceptrons and Decision Trees.
+{\em Applied Soft Computing} {\bf 2021}, {\em 111}, 107806.
+https://doi.org/10.1016/j.asoc.2021.107806.
+Available online: \url{https://www.sciencedirect.com/science/article/pii/S1568494621007274}.
+
 \bibitem[Hussain et al.(2023)]{JammingDetectionIoT-Hussain}

### 2024-11-24 article.tex
edited some captions. Clarified parameter selection

@@
 
-The first phase in our testing methodology involves tuning the model's hyperparameters by varying them between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best values.
+The first phase in our testing methodology involves tuning the model's hyperparameters by varying them between a minimum and a maximum value, evaluating the impact on the performance metrics (detailed in Section \ref{EvaluationMetrics}) and then choosing the best possible values.
+In our scenario, a value is considered good if it provides a high metric value while at the same time not impacting too drastically the execution time.
+In cases where improving the value of a metric requires a significant increase in execution time, we chose the value that provides the best trade-off between the two.
+
 Among the parameters available in the \textit{Scikit-learn} implementation of the Isolation Forest, we decided to tune the following:
@@
 	\includegraphics[width=10.5cm]{img/nEstimatorsTuning.png}
-	\caption{n\_estimators tuning results. Performance of the model increases with an increasing number of estimators}\label{fig:n_estimators_tuning}
+	\caption{n\_estimators tuning results. Performance of the model in all analyzed metrics increases with an increasing number of estimators}\label{fig:n_estimators_tuning}
 \end{figure}
@@
 	\caption{Confusion Matrix for the default Isolation Forest model \textbf{(a)} and the tuned Isolation Forest model \textbf{(b)}.
-The tuned version reduces false positives while suffering a minimal loss in true positives.}
+The tuned version reduces false positives while suffering a negligible increase in false negatives compared to the default model.}
 	\label{fig:ConfusionMatrixStandardTunedIF}
@@
 	\caption{Confusion Matrix for the tuned Isolation Forest model \textbf{(a)} and the Majority Rule Isolation Forest model \textbf{(b)}.
-The MR model greatly reduces false positives while maintaining a rate of true positives of over 99\%.}
+The MR model significantly reduces false positives while maintaining a rate of true positives of over 99\%.}
 	\label{fig:ConfusionMatrixTunedMajorityIF}

### 2024-12-05 article.tex
Added information about hardware testing
Added modifications from professor

@@
 Despite 5G still being in its early stages of adoption at the time of writing \cite{5GStatisticsTaylor}, the research community is already working on the next generation of wireless communication technologies, 6G.
-6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as improvements in both data rates and latency.
+6G technology is expected to enable a wide variety of new use cases, thanks to massive coverage as well as improvements in both data rates and latency, especially for IoT domains~\cite{ChFaPi21}.
 All of these advancements will in turn bring forth new security challenges specific to those applications.
+
+Starting from Release 17, 3GPP introduces the wireless infrastructure UAV (WI UAV) to provide, thanks to its controlled  mobility, the flexibility required by a dynamic and massive access  for ubiquitous  connectivity.
+Release 18, known as ``6G and beyond drones'', enlarges this vision introducing AI to achieve fully connected sky and marine communications of drones for a global Internet of Drones (IoD).
 
@@
 In the future, IoT devices are expected to come equipped with AI-specific chips that will allow them to run AI models directly on the edge, without the need to offload computation to a central server.
-This is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
+This approach, aligning with the context-aware autonomic computing and communications paradigm~\cite{ChFaLoPu16}, is especially useful in the case of jamming attacks, where the communication between the device and the server is disrupted.
 Our solution is designed to run on a resource-constrained IoT device like a drone and to be lightweight, both in terms of memory usage and computational power.
@@
 \section{Related Works}
+In this Section, some reviews regarding the integration of terrestrial 5G/6G cellular networks with non terrestrial network (NTN), e.g., UAV/drone networks, and the relevance of AI-native solutions in T(NTN) domain are  highlighted.
+Further, the attention is focused on the jamming attacks detection in a typical drone scenario.
+The paper~\cite{BaShKiJu22} introduces the UAV wireless infrastructure to support a flying base station/ relay  or data collector /disseminator in 6G integrated terrestrial/non terrestrial networks (T/NTNs).
+The authors provide a sufficient review of various regulatory and the main standardization initiatives for integrating UAVs into the cellular network and describe several testbeds and UAV prototypes.
+Moreover, the paper (i) categorizes various advantages potentially provided, such as the increased capacity and coverage, on-demand networking, machine type communications, 3D mobility support and users tracking, (ii) addresses the issue of flexible use spectrum policy, and (iii) conducts an accurate analysis of security concerns, as GPS jamming attacks.
+
+The recent survey \cite{AQMoBaCeZoArAsMuDeIm23} first highlights the limits of ML models training to manage Big Data related to the massive number of connected devices in Cloud-based servers to deliver pervasive smart services and applications and then considers federated learning (FL) as a promising solution to distribute computation to the edge network.
+In particular, after the fundamentals of the FL principles and architecture, the review shows the use of multi-access edge computing (MEC) as a suitable environment for FL algorithms to offer low latency for real time applications in beyond 5G/6G networks as well as in regard to other FL enabled technologies, such as BlockChain and Network Slicing.
+In addition, the state of art for AI-empowered UAV is reviewed, especially considering FL  (i) for  preserving the privacy of sensed data in UAV-enabled mobile crowd-sensing, (ii) for exploiting and predict the data on air quality acquired by an UAV swarm also considering data collected by different agencies, (iii) for reducing e2e latency and overhead at the edge, and to improve consequently the battery life of UAV, (iv) for reducing the communication cost among multiple UAVs and a ground data fusion centre in the context of image classification.
+
+The authors of~\cite{WaGuGa24}  provide a review of the current trends and state of the art of Unmanned autonomous intelligent systems (UAISs) in the context of 5G/6G NTN communications.
+Initially, the NTN integration with 5G/6G systems is addressed by means of utilizing UAVs and other low-altitude aerial platforms, then it highlights the importance  of artificial intelligence (AI) as UAIS becomes a part of the future integrated T/NTN networks.
+Deep learning/reinforcement learning  algorithms, MEC and distributed computation offloading offering low latency paths are shown to enable UAIS in the development of practical applications, such as object detection/reorganization, decision-making, and autonomous navigation.
 
@@
 The authors show that Random Forests were able to achieve a high detection of jamming attacks.
+
 The authors of \cite{JammingDetectionRF-Karagiannis} on the other hand, propose the use of an unsupervised approach in the context of VANETs and test its performance in a variety of real-world scenarios.
@@
 This work builds upon the research done in \cite{JammingDetectionIoT-Hussain}, where the authors analyze a Machine Learning (ML) based approach for the detection of jamming attacks.
+
 The authors propose the use of Convolutional Neural Networks (CNNs) to detect jamming attacks in an IoT drone scenario.
@@
 struggles in the classification of periodic jamming and normal traffic.
+
+Finally, a lightweight reinforcement learning algorithm for anti-jamming in UAV communications, utilizing spectrum state abstraction to efficiently adapt to dynamic jamming environments, rather than focusing specifically on jamming detection, is presented in~\cite{LiWaDuXuHa24}.
 
@@
 
-In the proposed scenario (Figure \ref{fig:CombinedJammingscenariosDiagram}) we have a flying drone that is subject to a jamming attack.
+The reference scenario, as depicted in Figure \ref{fig:CombinedJammingscenariosDiagram}, is comprised of a  drone that is subject to a jamming attack.
 The drone communicates with a ground station and periodically samples the Received Signal Strength (RSS) of the signal it receives.
-The drone implements a simple unsupervised machine learning module, trained on nominal traffic RSS values.
+According to the edge processing and networking paradigm, the drone is equipped with jamming detection module which could be integrated as a part of a more complex security architectural framework. 
+In particular, this module implements a simple unsupervised machine learning module, trained on nominal traffic RSS values.
 The module takes the sampled RSS values and classifies them as either normal or anomalous, making the drone able to determine whether or not a jamming attack is taking place.
@@
 The chosen implementation for IF is the one provided by the \textit{Scikit-learn} library \cite{IsolationForestScikitLearn} for Python 3.
+The model was tested on both a Raspberry Pi 3 and a desktop processor, demonstrating effective performance in both environments with comparable trends.
+The presented graphs reflect results from the desktop processor, but the model's efficiency on resource-constrained devices has been validated.
 
@@
 
-As discussed in Section \ref{sec:DetectionMitigation}, devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{6GRoadmapLetaief}.
+As discussed in Section \ref{sec:DetectionMitigation}, devices integrated into 6G networks are expected to have a higher degree of sensing capabilities compared to current devices \cite{}.
 Thanks to the ability of the Isolation Forest to work on high dimensional data, the model could easily be expanded to include more classification features, which would improve its situational awareness and performance.
+This could play a crucial role in addressing interference or signal shadowing patterns.
+
+Furthermore, future work could include the investigation of the impact of adversarial settings, as this could offer insights into real-world performance as well as demonstrate adaptability to emerging 6G technologies.
 
@@
 
+\bibitem[Chiti et al.(2021)]{ChFaPi21}
+Chiti, F.
+and Fantacci, R.
+and Pierucci, L.
+A Green Routing Protocol with Wireless Power Transfer for Internet of Things.
+{\em Journal of Sensor and Actuator Networks} {\bf 2021}, {\em 10}, {\em 1}.
+\url{https://doi.org/10.3390/jsan10010006}.
+
+\bibitem[Bajracharya et al.(2022)]{BaShKiJu22}
+Bajracharya, R.; Shrestha, R.; Kim, S.; Jung, H.
+6G NR-U Based Wireless Infrastructure UAV: Standardization, Opportunities, Challenges and Future Scopes.
+{\em IEEE Access} {\bf 2022}, {\em 10}, 84--90.
+\url{https://doi.org/10.3390/jsan10010006}.
+
+\bibitem[Al-Quraan et al.(2023)]{AQMoBaCeZoArAsMuDeIm23}
+Al-Quraan, M.;  Mohjazi, L.;  Bariah, L.; Centeno, A.; Zoha, A.; Arshad, K.; Assaleh, K.; Muhaidat, S.; Debbah, M.; Imran, M.
+A.
+Edge-Native Intelligence for 6G Communications Driven by Federated Learning: A Survey of Trends and Challenges.
+{\em IEEE Transactions on Emerging Topics in Computational Intelligence} {\bf 2023}, {\em 7}, {\em 3}, 957--979.
+\url{https://doi.org/10.1109/10.1109/TETCI.2023.3251404}.
+
+\bibitem[Wang et al.(2024)]{WaGuGa24}
+Wang, X.; Guo, Y.; Gao, Y. Unmanned Autonomous Intelligent System in 6G Non-Terrestrial Network. {\em Information} {\bf 2024}, {\em 15}, {\em 1}. \url{https://doi.org/10.3390/info15010038}.
+
 \bibitem[Letaief et al.(2019)]{6GRoadmapLetaief}
@@
 \url{https://doi.org/10.1109/MCOM.2019.1900271}.
+
+\bibitem[Chiti et al.(2016)]{LoPu16}
+Chiti, F.
+and Fantacci, R.
+and Loreti, M.
+and Pugliese, R.
+Context-aware wireless mobile autonomic computing and communications: research trends and emerging applications.
+{\em IEEE Wireless Communications} {\bf 2016}, {\em 23}, {\em 2}, 86--92.
+\url{https://10.1109/MWC.2016.7462489}.
 
@@
 Available online: \url{https://www.sciencedirect.com/science/article/pii/S1568494621007274}.
+
+\bibitem[Liu et al.(2024)]{LiWaDuXuHa24}
+Liu, X.; Wang, X.; Xu, Y.; Du, Z.; Xu Y.; Han H.
+Lightweight Reinforcement Learning with State Abstraction for Dynamic Spectrum Anti-Jamming Communications {\em 2024 IEEE Wireless Communications and Networking Conference} {\bf 2024}, 1--6.
+\url{https://doi.org/10.1109/WCNC57260.2024.10571324}.
 
